### 2022-02-25 nakayama/nakayamas-lemma.tex
initial commit

\documentclass[12pt]{article}
\usepackage[top=1in, bottom=1in, left=1in, right=1in ]{geometry}
\usepackage{amsmath,amsfonts,amssymb, amsthm}
\usepackage[colorlinks, filecolor=cyan, urlcolor=niceblue]{hyperref}

\usepackage{libertinus}
\usepackage[T1]{fontenc}
\usepackage{fancyhdr}
\usepackage[shortlabels]{enumitem}
\usepackage[mathscr]{euscript}

\renewcommand{\baselinestretch}{1}
\thispagestyle{empty}

\newcommand{\NN}{\mathbb{N}}
\newcommand{\ZZ}{\mathbb{Z}}
\newcommand{\RR}{\mathbb{R}}
\newcommand{\CC}{\mathbb{C}}
\newcommand{\QQ}{\mathbb{Q}}
\newcommand{\Zm}[1]{\mathbb{Z}/{#1}\mathbb{Z}}
\newcommand{\VV}{\mathbb{V}}

\newcommand{\kay}{\mathsf{k}}

\newcommand{\WW}{\mathcal{W}}
\renewcommand{\AA}{\mathcal{A}}
\newcommand{\BB}{\mathcal{B}}

\newcommand{\HRule}{\begin{center}\rule{\linewidth}{.01cm}\end{center}}

\setlength{\parskip}{1em}

%THEOREM ENVIRONMENTS

\newtheorem{theorem}{Theorem}[section]
\newtheorem{lemma}[theorem]{Lemma}
\newtheorem{corollary}[theorem]{Corollary}
\newtheorem{proposition}[theorem]{Proposition}

%DEFINITION STYLE ENVIRONMENTS
\theoremstyle{definition}
\newtheorem{definition}[theorem]{Definition}
\newtheorem*{definition*}{Definition}
\newtheorem{definition-theorem}[theorem]{Definition/Theorem}
\newtheorem{setup}[theorem]{Setup}
\newtheorem*{notation*}{Notation}
\newtheorem{notation}[theorem]{Notation}
\newtheorem{example}[theorem]{Example}
\newtheorem{examples}[theorem]{Examples}

%REMARK STYLE ENVIRONMENTS
\theoremstyle{remark}
\newtheorem{remark}[theorem]{Remark}
\newtheorem*{convention}{Co\usepackage{tikz-cd}nvention}

% http://www.neverendingbooks.org/mumfords-treasure-map

\pagestyle{fancy}
\fancyhead[L]{{\textbf{MATH 831}}}
\fancyhead[R]{\thepage}
\fancyhead[C]{Nakayama's Lemma}

\begin{document}

\begin{center}
	{\large \textbf{Proof Object:  \emph{Nakayama's Lemma}} } \\ \vspace{.2cm} Statement and Relevant Definitions
\end{center}

\vspace{-.5cm}

\HRule

\begin{definition}[Group]
A \textbf{group} is a set $G$ with a binary operation $\ast$ on $G$ such that the following properties hold.
\begin{enumerate}[topsep=0cm,itemsep=0cm]
\item \textbf{Associativity.}  For all $a, b, c, \in G$, $(a \ast b) \ast c = a \ast (b \ast c)$.
\item \textbf{Identity.}  There exists an element $e \in G$ such that for all $a \in G$, $a \ast e = a$ and $e \ast a = a$.
\item \textbf{Inverses.}  For every $a \in G$ there exists some $b \in G$ for which $a \ast b  = e$ and $b \ast a = e$. 
\end{enumerate}
A group $G$ is called \textbf{abelian} if $a \ast b = b \ast a$ for all $a, b \in G$.
\end{definition}

%\begin{examples}
%The set of integers
%\end{examples}

\begin{definition}[Ring]
A \textbf{ring} is a set $R$ with two binary operations, denoted $+$ and $\cdot$, for which the following hold.
\begin{enumerate}[topsep=0cm,itemsep=0cm]
\item \textbf{Abelian group under addition.}  $R$ is an abelian group under $+$ with identity denoted ``$0$.''
\item \textbf{Associativity of multiplication.}  $(r \cdot s) \cdot t = r \cdot (s \cdot t)$ for all $r, s, t \in R$.
 \item \textbf{Multiplicative identity.}  There is an element  denoted ``$1$'' in $R$ for which $r \cdot 1 = r$ and $1 \cdot r = r$ for every $r \in R$. 
 \item \textbf{Distributivity.} $r \cdot (s + t) = r \cdot s + r \cdot t$ and  $(r + s) \cdot t = r \cdot t + s \cdot t$ for all $r, s, t \in R$.  
\end{enumerate}
A ring $R$ is called \textbf{commutative} if $r \cdot s = s \cdot r$ for all $r, s \in R$. 
\end{definition}

\begin{definition}[Ideal of a commutative ring]
An \textbf{ideal} of a commutative ring $R$ is a subset $I \subseteq R$ for which the following hold. 
\begin{enumerate}[topsep=0cm,itemsep=0cm]
\item \textbf{Abelian group under addition.}  $R$ is an abelian group under $+$ with identity denoted ``$0$.''
\item \textbf{Absorption.}  $r a \in I$ for all $r \in R$ and $a \in I$.
\end{enumerate}
An ideal $\mathfrak{m}$ of a ring $R$ is called \textbf{maximal} if it is  a proper ideal, i.e., $\mathfrak{m} \subsetneq R,$ and there is no other proper ideal strictly containing $\mathfrak{m}$, i.e., if $\mathfrak{m} \subseteq J \subsetneq R$ for some ideal $J$ of $R$, then $J = \mathfrak{m}$. 
\end{definition}

\begin{definition}
	A \textbf{local ring} is a ring that has a unique maximal ideal. 
\end{definition}

\begin{remark}
Assuming the axiom of choice, every ring has at least one maximal ideal since
given ideals
\[
I_1 \subsetneq I_2 \subsetneq I_3 \subsetneq \cdots R
\]
one can check that the union $\bigcup_{i=1}^\infty I_i$ is again an ideal of $R$, so the existence of a maximal ideal follows by Zorn's lemma.  In fact, any \emph{unit} of $R$--element with no multiplicative inverse--is contained in a maximal ideal. 
\end{remark}

\begin{definition}[Module over a ring]
A \textbf{module} over a ring $R$ is an abelian group $M$ under a binary operation $+$, and a function $\cdot: R \times M \to M$, satisfying the following properties for all $r, s \in R$ and $u, v \in M$.
\begin{enumerate}[topsep=0cm,itemsep=0cm]
\item  $r \cdot (u + v)  = r \cdot u + r \cdot v$.
\item $(r+s) \cdot u = r \cdot u + s \cdot u$.
\item $(rs) \cdot u = r \cdot (s \cdot u)$.
\item $1 \cdot u = u$ for all $u \in M$.
\end{enumerate}
A module is called \textbf{finitely generated} if there exist a fixed finite list $u_1, \ldots, u_n \in M$ such that any 
$w \in M$ can be written as 
$
w = r_1 u_1 + r_1 u_2 + \cdots + r_n u_n
$
for some $r_1, \ldots, r_n \in R$. 
\end{definition}

Though the following has long been traditionally called a ``lemma,'' it is a fundamental theorem in the field of commutative algebra, and could arguably called the ``Fundamental Theorem of Commutative Algebra.''

\begin{definition}
	Suppose that $R$ is a commmutative ring, $I$ is an ideal of $R$, than $M$ is an $R$-module.  Then $IM$ is the set of elements of the form 
	$a_1 u_1 + a_2 u_2 + \cdots + a_k u_k$, where $a_1, \ldots, a_2$.  
Due to the absorption property of ideals, $IM$ is an $R$-module contained in $M$. 	
\end{definition}

\begin{theorem}[Nakayama's Lemma]
	Let $M$ be a finitely generated module over a local ring $R$ that has maximal ideal $\mathfrak m$. 
	If $M = \mathfrak{m}M$, then $M=0$. 
\end{theorem}

\begin{proof}[Informal Proof]
We apply induction on the number of generators $n$ of $M$. 
For the base case $n=1$, suppose that $u$ generates $M$.	
Then every element of $M$ has the form $ru$ for some $r \in R$, and hence every element of $\mathfrak{m}M$ has the form $a(ru) = (ar)u = (ra)u$ for some $a \in    \mathfrak{m}$.  By the absorption property of ideals, $ra \in \mathfrak{m}$, and we conclude that every element of $\mathfrak{m}M$ has the form $xu$ for some $x \in \mathfrak{m}$.

Suppose that $M = \mathfrak{m} M$.  Then since $u \in M$, $u = xu$ for some $x \in \mathfrak{m}$.  Hence $(1-x) u = 0$. We claim that $1-x$ has a multiplicative inverse. If not, then it is contained in $\mathfrak{m}$, but then since $x \in m$, we have that $1 = (1-x)+x \in \mathfrak{m}$, contradicting the fact that $\mathfrak{m}$ is a proper ideal of $R$.  Hence $1-x$ has a multiplicative inverse $y$, and so \[ 0 = y \cdot 0= y((1-x)u) = (y(1-x)) u = 1 \cdot u = u. \]  This forces $M=0$, and the statement holds.

Now, inductively, for some $n \geq 1$,  assume that $M$ is generated by $u_1, \ldots, u_n \in M$.  Let $Ru_1$ denote the $R$-module generated by $u_1$, and let 
 if $N = M/R u_1$ be the $R$-module consisting of equivalence classes of elements of $M$ with respect to the equivalence relation given by $w \sim w'$ if and only if $w - w' \in R u_1$.  Then $N$ is generated by the equivalence classes of $u_2, \ldots, u_n$, $(n-1)$-many element of $N$, and $\mathfrak{m}N = N$ still holds.  
 So by the inductive hypothesis, $N=0$, which says that $M = R u_1$.  But we have already done the case where $n=1$. 
\end{proof}
\end{document}

### 2022-03-04 nakayama/nakayamas-lemma.tex
Finished informal proof description of Nakayama's Lemma

@@
-\documentclass[12pt]{article}
-\usepackage[top=1in, bottom=1in, left=1in, right=1in ]{geometry}
+\documentclass[12pt]{amsart}
+\usepackage[top=1in, bottom=1in, left=1.2in, right=1.2in ]{geometry}
 \usepackage{amsmath,amsfonts,amssymb, amsthm}
-\usepackage[colorlinks, filecolor=cyan, urlcolor=niceblue]{hyperref}
 
@@
 \usepackage[T1]{fontenc}
+
 \usepackage{fancyhdr}
-\usepackage[shortlabels]{enumitem}
-\usepackage[mathscr]{euscript}
-
-\renewcommand{\baselinestretch}{1}
+\pagestyle{fancy}
 \thispagestyle{empty}
 
-\newcommand{\NN}{\mathbb{N}}
-\newcommand{\ZZ}{\mathbb{Z}}
-\newcommand{\RR}{\mathbb{R}}
-\newcommand{\CC}{\mathbb{C}}
-\newcommand{\QQ}{\mathbb{Q}}
-\newcommand{\Zm}[1]{\mathbb{Z}/{#1}\mathbb{Z}}
-\newcommand{\VV}{\mathbb{V}}
+\fancyhead[L]{{Lambda Group Project}}
+\fancyhead[R]{\thepage}
+\fancyhead[C]{\textbf{Nakayama's Lemma}}
 
-\newcommand{\kay}{\mathsf{k}}
-
-\newcommand{\WW}{\mathcal{W}}
-\renewcommand{\AA}{\mathcal{A}}
-\newcommand{\BB}{\mathcal{B}}
+\renewcommand{\baselinestretch}{1.2}
+\parskip 0.2cm
 
@@
 
-\setlength{\parskip}{1em}
+\usepackage[shortlabels]{enumitem}
 
 %THEOREM ENVIRONMENTS
-
-\newtheorem{theorem}{Theorem}[section]
+\newtheorem{theorem}{Theorem}
 \newtheorem{lemma}[theorem]{Lemma}
@@
 \newtheorem{definition}[theorem]{Definition}
-\newtheorem*{definition*}{Definition}
-\newtheorem{definition-theorem}[theorem]{Definition/Theorem}
-\newtheorem{setup}[theorem]{Setup}
-\newtheorem*{notation*}{Notation}
 \newtheorem{notation}[theorem]{Notation}
@@
 \newtheorem{remark}[theorem]{Remark}
-\newtheorem*{convention}{Co\usepackage{tikz-cd}nvention}
-
-% http://www.neverendingbooks.org/mumfords-treasure-map
-
-\pagestyle{fancy}
-\fancyhead[L]{{\textbf{MATH 831}}}
-\fancyhead[R]{\thepage}
-\fancyhead[C]{Nakayama's Lemma}
 
@@
 \begin{enumerate}[topsep=0cm,itemsep=0cm]
-\item \textbf{Abelian group under addition.}  $R$ is an abelian group under $+$ with identity denoted ``$0$.''
+\item \textbf{Abelian group under addition.}  $R$ is an abelian group under $+$ with identity denoted $0$.
 \item \textbf{Associativity of multiplication.}  $(r \cdot s) \cdot t = r \cdot (s \cdot t)$ for all $r, s, t \in R$.
- \item \textbf{Multiplicative identity.}  There is an element  denoted ``$1$'' in $R$ for which $r \cdot 1 = r$ and $1 \cdot r = r$ for every $r \in R$. 
+ \item \textbf{Multiplicative identity.}  There is an element  denoted $1$ in $R$ for which $r \cdot 1 = r$ and $1 \cdot r = r$ for every $r \in R$. 
  \item \textbf{Distributivity.} $r \cdot (s + t) = r \cdot s + r \cdot t$ and  $(r + s) \cdot t = r \cdot t + s \cdot t$ for all $r, s, t \in R$.  
@@
 \begin{enumerate}[topsep=0cm,itemsep=0cm]
-\item \textbf{Abelian group under addition.}  $R$ is an abelian group under $+$ with identity denoted ``$0$.''
-\item \textbf{Absorption.}  $r a \in I$ for all $r \in R$ and $a \in I$.
+\item \textbf{Abelian group under addition.}  $R$ is an abelian group under $+$ with identity denoted $0$.
+\item \textbf{Absorption.} For any $r \in R$ and $a \in I$, the element $r a = a r$ is in $I$. 
 \end{enumerate}
@@
 
+\begin{remark}[Characterization of proper ideals] \label{proper-ideal: R}
+An ideal $I$ of a commutative ring $R$ satisfies $I = R$ if and only if $1 \in I$:  
+If $I=R$, then certainly $1 \in R = I$.
+On the other hand, if $1 \in I$, then by the absorption property of ideals, $r = r \cdot 1 \in R$ for any $r \in R$, i.e., $R \subseteq I$, and so $I = R.$  Hence an ideal is proper if and only if it does not contain $1$.
+\end{remark}
+
+\begin{definition}[Multiplicative inverse/unit of a ring] 
+An element $s$ of a commutative ring $R$ is a \textbf{(muliplicative) inverse}  of $r \in S$ if $rs = 1$.
+If $r\in R$ has a multiplicative inverse, we call it a \textbf{unit} of $R$. 
+\end{definition}
+
+\begin{remark}[Multiples of units are again units] \label{multiples-units: R}
+Ifotice that if $r \in R$ is not a unit, then neither is $rs$ for any $s \in R$:   If $(rs)t = 1$, then $r$ has inverse $st$ since by the associativity of multiplication in $R$,  $1 = (rs)t = r(st)$. 
+\end{remark}
+
+\begin{remark} \label{maximal-ideals-existence: R}
+Assuming the axiom of choice, every non-unit $x \in R$ is contained in some maximal ideal:
+Given a chain of proper ideals containing $x$
+\[
+I_1 \subsetneq I_2 \subsetneq I_3 \subsetneq \cdots  \subseteq R
+\]
+one can check that the union $\bigcup_{i=1}^\infty I_i$ is again an ideal of $R$ containing $x$, so the existence of a maximal ideal follows by Zorn's lemma.  
+\end{remark}
+
+\begin{lemma} \label{units-local-ring: L}
+Suppose that $R$ is a commutative local ring with maximal ideal $\mathfrak{m}$.  
+If $x \in \mathfrak{m}$, then $1-x$ is a unit.
+\end{lemma}
+
+\begin{proof}[Informal proof]
+Suppose, by way of contradiction, that $1-x$ is not a unit.
+Then by Remark \ref{maximal-ideals-existence: R}, $1-x$ is contained in the unique maximal ideal $\mathfrak{m}$.
+So then $x$ and $1-x$ are both in $\mathfrak{m}$, and since $-x \in \mathfrak{m}$ as well, $(1+x) + (-x) = 1 \in \mathfrak{m}$.
+This forces $\mathfrak{m} = R$ by Remark \ref{proper-ideal: R}, a contradiction since maximal ideals are proper. Hence $1-x$ is indeed a unit. 
+\end{proof}
+
 \begin{definition}
@@
 \end{definition}
-
-\begin{remark}
-Assuming the axiom of choice, every ring has at least one maximal ideal since
-given ideals
-\[
-I_1 \subsetneq I_2 \subsetneq I_3 \subsetneq \cdots R
-\]
-one can check that the union $\bigcup_{i=1}^\infty I_i$ is again an ideal of $R$, so the existence of a maximal ideal follows by Zorn's lemma.
-In fact, any \emph{unit} of $R$--element with no multiplicative inverse--is contained in a maximal ideal.
-\end{remark}
 
@@
 
-Though the following has long been traditionally called a ``lemma,'' it is a fundamental theorem in the field of commutative algebra, and could arguably called the ``Fundamental Theorem of Commutative Algebra.''
-
 \begin{definition}
 	Suppose that $R$ is a commmutative ring, $I$ is an ideal of $R$, than $M$ is an $R$-module.  Then $IM$ is the set of elements of the form 
-	$a_1 u_1 + a_2 u_2 + \cdots + a_k u_k$, where $a_1, \ldots, a_2$.  
-Due to the absorption property of ideals, $IM$ is an $R$-module contained in $M$. 	
+	$a_1 u_1 + a_2 u_2 + \cdots + a_k u_k$, where $a_1, \ldots, a_k \in I$ and $u_1, \ldots, u_k \in M$.  
+Notice that by the absorption property of ideals, $IM$ is an $R$-module contained in $M$. 	
 \end{definition}
 
+Though the following has long been traditionally called a ``lemma,'' it is a fundamental theorem in the field of commutative algebra, and could arguably called the ``Fundamental Theorem of Commutative Algebra.''
+Below, the notation ``$M=0$'' means that $M$ is the $R$-module consisting of only one element, $0$.
+
 \begin{theorem}[Nakayama's Lemma]
-	Let $M$ be a finitely generated module over a local ring $R$ that has maximal ideal $\mathfrak m$. 
+	Let $M$ be a finitely generated module over a commutative local ring $R$ that has maximal ideal $\mathfrak{m}$. 
 	If $M = \mathfrak{m}M$, then $M=0$. 
@@
 We apply induction on the number of generators $n$ of $M$.
+
 For the base case $n=1$, suppose that $u$ generates $M$.	
-Then every element of $M$ has the form $ru$ for some $r \in R$, and hence every element of $\mathfrak{m}M$ has the form $a(ru) = (ar)u = (ra)u$ for some $a \in    \mathfrak{m}$.
-By the absorption property of ideals, $ra \in \mathfrak{m}$, and we conclude that every element of $\mathfrak{m}M$ has the form $xu$ for some $x \in \mathfrak{m}$.
+Then every element of $M$ has the form $ru$ for some $r \in R$, and hence every element of $\mathfrak{m}M$ has the form $a(ru) $
+for some $a \in    \mathfrak{m}$. 
+By the associative  property of multiplication in $R$, $a(ru) = (ar)u$.  
+Then by the absorption property of ideals, $ar \in \mathfrak{m}$, and we conclude that every element of $\mathfrak{m}M$ has the form $xu$ for some element $x \in \mathfrak{m}$ (namely, $x = ar$).
 
-Suppose that $M = \mathfrak{m} M$.
-Then since $u \in M$, $u = xu$ for some $x \in \mathfrak{m}$.
-Hence $(1-x) u = 0$.
-We claim that $1-x$ has a multiplicative inverse.
-If not, then it is contained in $\mathfrak{m}$, but then since $x \in m$, we have that $1 = (1-x)+x \in \mathfrak{m}$, contradicting the fact that $\mathfrak{m}$ is a proper ideal of $R$.
-Hence $1-x$ has a multiplicative inverse $y$, and so \[ 0 = y \cdot 0= y((1-x)u) = (y(1-x)) u = 1 \cdot u = u.
-\]  This forces $M=0$, and the statement holds.
+Since $M = \mathfrak{m} M$ and $u \in M$, we can write $u = xu$ for some $x \in \mathfrak{m}$.  Hence $(1-x) u = 0$.
+By Lemma \ref{units-local-ring: L},  $1-x$ is a unit.  Suppose it has inverse $y$,  so \[ 0 = y \cdot 0= y((1-x)u) = (y(1-x)) u = 1 \cdot u = u. \]  Hence every element in $M$ is zero, i.e. $M=0$.
 
-Now, inductively, for some $n \geq 1$,  assume that $M$ is generated by $u_1, \ldots, u_n \in M$.  Let $Ru_1$ denote the $R$-module generated by $u_1$, and let 
- if $N = M/R u_1$ be the $R$-module consisting of equivalence classes of elements of $M$ with respect to the equivalence relation given by $w \sim w'$ if and only if $w - w' \in R u_1$.
-Then $N$ is generated by the equivalence classes of $u_2, \ldots, u_n$, $(n-1)$-many element of $N$, and $\mathfrak{m}N = N$ still holds.
- So by the inductive hypothesis, $N=0$, which says that $M = R u_1$.  But we have already done the case where $n=1$. 
+Inductively, fix  $n > 1$ and assume that the only $R$-module $N$ generated by $n-1$ elements that satisfies $N = \mathfrak{m}N$ is $N=0$.
+
+Take an $R$-module $M$ generated by $u_1, \ldots, u_n \in M$.
+
+Since $M = \mathfrak{m}M$ and $u_1 \in M$, we can write 
+\[
+u_1 = x_1 u_1 + x_2 u_2 + \cdots + x_n u_n
+\]
+for some $x_1, \ldots, x_n \in \mathfrak{m}$. 
+Then $(1-x_1)u_1 =  x_2 u_2 + \cdots + x_n u_n$, where again by Lemma \ref{units-local-ring: L}, $1-x_1$ is a unit. 
+If $z$ is its inverse, then 
+\begin{align*}
+z ((1-x_1)u_1)  &= z( x_2 u_2 + \cdots + x_n u_n ) \\
+(z (1-x_1))u_1 &= z( x_2 u_2 ) + \cdots + z (x_n u_n) \\
+u_1 &= (z x_2) u_2 + \cdots + (z x_n) u_n. 
+\end{align*}
+Hence $M$ is generated by $u_2, \ldots, u_n$, and by the inductive hypothesis, 
+$M = 0$.
 \end{proof}

### 2022-05-12 nakayama/paper.tex
Starting paper

% !TeX document-id = {34714a8d-170f-4947-a4b9-b8812e4a094a}
% !TeX TXS-program:compile = txs:///pdflatex/[--shell-escape]
\RequirePackage[l2tabu,orthodox]{nag}
\documentclass{article}
\usepackage{amssymb}
\usepackage{mathtools}
\usepackage{minted}
\begin{document}
We started by defining a semigroup class, which declares a binary operation to
be associative. From here, we build up through monoids, which introduce
identities, to groups, which introduce inverses. Note the double equals in
these definitions is notation for an arbitrary equivalence relation over the
group's carrier set.
\begin{minted}{coq}
  Infix "==" := equiv (at level 60, no associativity).
  Class Semigroup := {
    semigroup_assoc:
      forall (a b c: Carrier),
        a <o> b <o> c == a <o> (b <o> c);
  }.
  Class Monoid := {
    monoid_semigroup :> Semigroup equiv op;
    monoid_ident_l:
      forall (a: Carrier), ident <o> a == a;
    monoid_ident_r:
      forall (a: Carrier), a <o> ident == a;
  }.
  Class Group := {
    group_monoid :> Monoid equiv op ident;
    group_inv_l:
      forall (a: Carrier), inv a <o> a == ident;
    group_inv_r:
      forall (a: Carrier), a <o> inv a == ident;
  }.
\end{minted}

While we found later on that we did not need quotients, it is worth remarking
that we got quotients working rather nicely in Coq using typeclasses. An
algebraic quotient are an equivalence relation on the algebraic structure which
preserve that structure. For example, quotient groups are formed by taking a
subgroup and making every element of that subgroup equivalent to the identity.
With \(P\) being the predicate for the subgroup, there are two ways to make an
equivalence relation from this description.
\begin{minted}{coq}
  Definition left_congru (a b: Carrier) :=
    P (inv a <o> b).
  Definition right_congru (a b: Carrier) :=
    P (a <o> inv b).
\end{minted}
When these two relations coincide, then we can prove that the equivalence
relation(s) actually preserve the group structure. Subgroups which have this
property are called \emph{normal subgroups}.
\begin{minted}{coq}
  Let normal_subgroup_congru_coincide :=
    forall (a b: Carrier),
      left_congru op inv P a b <->
      right_congru op inv P a b.

  Theorem quotient_normal_subgroup_group:
    normal_subgroup_congru_coincide ->
    Group (left_congru op inv P) op ident inv.
\end{minted}

Moving onwards, we then defined structures for rings, which have two binary
operations: a commutative plus \(+\) and a non-commutative times \(\cdot\), and
structures for commutative rings, where multiplication is commutative and has
an identity. Here we define \emph{ideals} which are normal subgroups under
addition and are absorbing with regards to multiplication, i.e. \(r a\) is in
the ideal whenever \(a\) is in the ideal and \(r\) is any element of the ring.
Again, we defined quotient rings but found them unnecessary in the end. Maximal
ideals were defined next. These are ideals that are proper subsets of the ring
while having no larger ideal except for the ring itself. Below is the
definition in Coq, which uses \(P\) as the predicate for the ideal.
\begin{minted}{coq}
  Definition maximal_ideal :=
    exists (r: Carrier), (not (P r) /\
      forall (Q: Carrier -> Prop)(Q_proper: Proper (equiv ==> iff) Q)
          (Q_ideal: Ideal add zero minus mul Q),
        (forall (r: Carrier), P r -> Q r) ->
        (forall (r: Carrier), Q r) \/
          (forall (r: Carrier), Q r -> P r)).
\end{minted}
We could then define a local ring, which is a ring with a single maximal ideal.
\begin{minted}{coq}
  Definition local_ring :=
    exists (P: Carrier -> Prop)(P_proper: Proper (equiv ==> iff) P)
        (P_ideal: Ideal add zero minus mul P),
      maximal_ideal P /\
      (forall (Q: Carrier -> Prop)(Q_proper: Proper (equiv ==> iff) Q)
          (Q_ideal: Ideal add zero minus mul Q),
        maximal_ideal Q -> forall (r: Carrier), P r <-> Q r).
\end{minted}

Here we had to include an axiom that in commutative ring, any non-unit \(x\) is
contained in some maximal ideal. This was made into an axiom as the standard
mathematical argument is a proof with potentially infinitely many steps. The
standard argument goes as follows.
\begin{quote}
    Set \(I_{1}\coloneqq (x)\) to be the principal ideal for \(x\). If
    \(I_{1}\) is not maximal, then there exists a strictly larger ideal
    \(I_{2}\), i.e. \(x\in I_{1}\subsetneq I_{2}\). If \(I_{2}\) is not
    maximal, then there exists another strictly larger ideal \(I_{3}\).
    Continue these arguments infinitely many times if necessary in order to get
    an infinite chain of ideals containing \(x\).
    \[x\in I_{1}\subsetneq I_{2}\subsetneq I_{3}\subsetneq\cdots\subsetneq R\]
    It is a simple matter to show that \(\bigcup_{k=1}^{\infty} I_{k}\) is also
    an ideal containing in \(x\). So by Zorn's lemma, there exists a maximal
    ideal in \(R\) which contains \(x\).
\end{quote}

We used classical logic to prove that \(1 - x\) is a unit where \(x\) is a
non-unit in any local ring. The proof used the rule \(\neg\neg P\rightarrow
P\) in order to do a proof by contradiction.

The next structure defined were modules over rings which generalize vector
spaces over fields. We needed to capture the notion of linear combinations of
coefficients and module vectors. This was done by dependently typed vectors,
i.e. lists parameterized by their length. Because there is an overload of the
term ``vector'', we will use that term to refer to module vectors, and use the
term ``list'' to mean length parameterized lists. As we don't use the simpler
kind of lists, this avoids any name collisions. A finitely generated module is
like the vector space \(\mathbf{R}^{n}\) in that there are finitely many
vectors which can generate all other vectors, for \(\mathbf{R}^{n}\) one such
collection of generators are \(\mathbf{e}_{1} = \begin{pmatrix} 1 & 0 & 0 &
  \cdots & 0\end{pmatrix}^{T}\), \(\mathbf{e}_{2} = \begin{pmatrix} 0 & 1 & 0 &
  \cdots & 0\end{pmatrix}^{T}\), \textellipsis, \(\mathbf{e}_{n} =
  \begin{pmatrix} 0 & 0 & 0 & \cdots & 1\end{pmatrix}^{T}\). In our code, \(M\)
is the type of module elements, \(R\) is the type of ring elements which act
as coefficients, and \(t A n\) is a list whose elements are of type \(A\) and
whose length is \(n\).
\begin{minted}{coq}
  Definition finitely_generated {n: nat}(basis: t M n) :=
    forall (vector: M),
      exists (coeffs: t R n),
        vector =M= linear_combin coeffs basis.
\end{minted}
\end{document}

### 2022-06-07 nakayama/paper.tex
Small updates to paper

@@
-% !TeX document-id = {34714a8d-170f-4947-a4b9-b8812e4a094a}
-% !TeX TXS-program:compile = txs:///pdflatex/[--shell-escape]
 \RequirePackage[l2tabu,orthodox]{nag}
@@
 \begin{document}
+
+% Mention an attempt with modules
+% Formalizing algebra => crypto
+% Interesting steps of the proof
+% ssreflect still looks to only deal with finite/discrete objects
+
 We started by defining a semigroup class, which declares a binary operation to
@@
 group's carrier set.
+% \begin{verbatim}  
 \begin{minted}{coq}
@@
 \end{minted}
+% \end{verbatim}
+The lines like \verb|monoid_semigroup :> Semigroup equiv op;| simply coerce
+the monoid typeclass into a semigroup.
 
@@
 subgroup and making every element of that subgroup equivalent to the identity.
-With \(P\) being the predicate for the subgroup, there are two ways to make an
-equivalence relation from this description.
+With \texttt{P} being the predicate for the subgroup, there are two ways to
+make an equivalence relation from this description.
+% \begin{verbatim}
 \begin{minted}{coq}
@@
 \end{minted}
+% \end{verbatim}
 When these two relations coincide, then we can prove that the equivalence
@@
 property are called \emph{normal subgroups}.
+% \begin{verbatim}
 \begin{minted}{coq}
@@
 \end{minted}
+% \end{verbatim}
+
+It is because of quotients that we used equivalence relations to define the
+components of group structure. If we were to use the regular Leibniz equality,
+this would make it very difficult to say that a quotient group is another
+group. But by having the definition of a group depend upon an arbitrary
+equivalence relation, we enable our theory to state that a quotient group is
+simply a group with under a different equivalence. We didn't loose much as we
+could still rely upon Coq's setoid rewrite tactics. Setoids are types equipped
+with an equivalence relation.
 
@@
 while having no larger ideal except for the ring itself. Below is the
-definition in Coq, which uses \(P\) as the predicate for the ideal.
+definition in Coq, which uses \texttt{P} as the predicate for the ideal.
+% \begin{verbatim}
 \begin{minted}{coq}
@@
     exists (r: Carrier), (not (P r) /\
-      forall (Q: Carrier -> Prop)(Q_proper: Proper (equiv ==> iff) Q)
+      forall (Q: Carrier -> Prop)
+          (Q_proper: Proper (equiv ==> iff) Q)
           (Q_ideal: Ideal add zero minus mul Q),
@@
 \end{minted}
+% \end{verbatim}
 We could then define a local ring, which is a ring with a single maximal ideal.
+% \begin{verbatim}
 \begin{minted}{coq}
   Definition local_ring :=
-    exists (P: Carrier -> Prop)(P_proper: Proper (equiv ==> iff) P)
+    exists (P: Carrier -> Prop)
+        (P_proper: Proper (equiv ==> iff) P)
         (P_ideal: Ideal add zero minus mul P),
       maximal_ideal P /\
-      (forall (Q: Carrier -> Prop)(Q_proper: Proper (equiv ==> iff) Q)
+      (forall (Q: Carrier -> Prop)
+          (Q_proper: Proper (equiv ==> iff) Q)
           (Q_ideal: Ideal add zero minus mul Q),
@@
 \end{minted}
+% \end{verbatim}
 
@@
 \begin{quote}
-    Set \(I_{1}\coloneqq (x)\) to be the principal ideal for \(x\). If
-    \(I_{1}\) is not maximal, then there exists a strictly larger ideal
-    \(I_{2}\), i.e. \(x\in I_{1}\subsetneq I_{2}\). If \(I_{2}\) is not
-    maximal, then there exists another strictly larger ideal \(I_{3}\).
-    Continue these arguments infinitely many times if necessary in order to get
-    an infinite chain of ideals containing \(x\).
+    Set \(I_{1}\coloneqq (x)\) to be the principal ideal for \(x\), i.e. the
+    ideal generated by the single element \(x\). If \(I_{1}\) is not maximal,
+    then there exists a strictly larger ideal \(I_{2}\), i.e.
+    \(x\in I_{1}\subsetneq I_{2}\). If \(I_{2}\) is not maximal, then there
+    exists another strictly larger ideal \(I_{3}\). Continue these arguments
+    infinitely many times if necessary in order to get an infinite chain of
+    ideals containing \(x\).
     \[x\in I_{1}\subsetneq I_{2}\subsetneq I_{3}\subsetneq\cdots\subsetneq R\]
@@
 \end{quote}
+Zorn's lemma is equivalent to the axiom of choice. So we had to add at least
+one axiom here in order to proceed. By adding the axiom that we did, not only
+will we encapsulate an infinite argument, but we will also avoid the need for
+the axiom of choice.
 
-We used classical logic to prove that \(1 - x\) is a unit where \(x\) is a
-non-unit in any local ring. The proof used the rule \(\neg\neg P\rightarrow
+Also, we used classical logic to prove that \(1 - x\) is a unit where \(x\) is
+a non-unit in any local ring. The proof used the rule \(\neg\neg P\rightarrow
 P\) in order to do a proof by contradiction.
@@
   \cdots & 0\end{pmatrix}^{T}\), \textellipsis, \(\mathbf{e}_{n} =
-  \begin{pmatrix} 0 & 0 & 0 & \cdots & 1\end{pmatrix}^{T}\). In our code, \(M\)
-is the type of module elements, \(R\) is the type of ring elements which act
-as coefficients, and \(t A n\) is a list whose elements are of type \(A\) and
-whose length is \(n\).
+  \begin{pmatrix} 0 & 0 & 0 & \cdots & 1\end{pmatrix}^{T}\). In our code,
+\texttt{M} is the type of module elements, \texttt{R} is the type of ring
+elements which act as coefficients, and \texttt{t A n} is a list whose elements
+are of type \texttt{A} and whose length is \texttt{n}.
+% \begin{verbatim}
 \begin{minted}{coq}
@@
 \end{minted}
+% \end{verbatim}
 \end{document}

### 2022-06-22 nakayama/paper.tex
Updated paper + more documentation

@@
 \documentclass{article}
+\usepackage{amsthm}
 \usepackage{amssymb}
@@
 \usepackage{minted}
+
+\newtheorem*{theorem}{Theorem}
+
 \begin{document}
@@
 these definitions is notation for an arbitrary equivalence relation over the
-group's carrier set.
+group's carrier set which acts as equality.
 % \begin{verbatim}
@@
 the ideal whenever \(a\) is in the ideal and \(r\) is any element of the ring.
-Again, we defined quotient rings but found them unnecessary in the end. Maximal
-ideals were defined next. These are ideals that are proper subsets of the ring
-while having no larger ideal except for the ring itself. Below is the
-definition in Coq, which uses \texttt{P} as the predicate for the ideal.
+Again, we defined quotient rings but found them unnecessary in the end. Note
+that should an ideal \(I\) contain a unit, an element \(x\) with a
+multiplicative inverse \(x^{-1}\), then \(I\) would be the entire ring by the
+absorbing property: given any element \(a\) of the ring, then \(a x^{-1}\) is
+also in the ring, and \(a x^{-1} x = a 1 = a\in I\). Maximal ideals were
+defined next. These are ideals that are proper subsets of the ring while having
+no larger ideal except for the ring itself. Below is the definition in Coq,
+which uses \texttt{P} as the predicate for the ideal.
 % \begin{verbatim}
@@
 % \end{verbatim}
-We could then define a local ring, which is a ring with a single maximal ideal.
+Almost by definition, maximal ideals can contain no units, otherwise they would
+fail to be a proper subset of the ring. We could then define a local ring,
+which is a ring with a single maximal ideal.
 % \begin{verbatim}
@@
 % \end{verbatim}
+
+Next, we defined the product of an ideal \(I\) and a module \(M\), denoted as
+\(I M\), which is defined to be all linear combinations of vectors from \(M\)
+and coefficients from \(I\). This can be easily shown to be a submodule of
+\(M\). We represented this in Coq as a predicate over \(M\).
+% \begin{verbatim}
+\begin{minted}{coq}
+  Context (P: R -> Prop).
+  Context {P_proper: Proper (Requiv ==> iff) P}.
+  Context {P_ideal: Ideal Radd Rzero Rminus Rmul P}.
+
+  Definition ideal_module (x: M): Prop :=
+    exists (n: nat)(coeffs: t R n)(vectors: t M n),
+      Forall P coeffs /\
+      x =M= linear_combin Madd Mzero action coeffs vectors.
+\end{minted}
+% \end{verbatim}
+The \verb|Forall P coeffs| ensures that every element of the coefficient list
+\texttt{coeffs} satisfies the predicate \texttt{P}. From here, we can move to
+stating Nakayama's lemma.
+
+\begin{theorem}[Nakayama's lemma]
+  Let \(M\) be a finitely generated module over a local ring \(R\) with maximal
+  ideal \(\mathfrak{m}\). If \(\mathfrak{m} M = M\), then \(M = 0\), which is
+  to say that \(M\) is the zero module which consists of exactly one element,
+  that being the zero vector.
+\end{theorem}
+
+We needed a lemma before moving on to prove the main theorem which states that
+for a finitely generated module \(M\) with a basis
+\(b_{1}, b_{2}, \dots, b_{n}\), any element \(x\in I M\) where \(I\) is an
+ideal can be written as a linear combination of the basis vectors with
+coefficients coming from \(I\). The proof of this lemma is straightforward and
+follows the standard, informal mathematical argument which inductively goes
+through the vectors needed to generate \(x\) and shows that each vector can be
+rewritten in terms of the basis vectors times elements of the ideal \(I\) as
+follows.
+\begin{align*}
+  x & = \sum_{k=1}^{m} u_{k} a_{k} \\
+    & = \sum_{k=1}^{m} u_{k} (r_{k1} b_{1} + \cdots + r_{kn} b_{n}) \\
+    & = \sum_{j=1}^{n} (u_{1} r_{1j} + \cdots + u_{m} r_{mj}) b_{j}
+\end{align*}
+Since each \(u_{k}\) comes from the ideal \(I\), the absorbing property of
+ideals guarantees that \(u_{k} r_{k j}\) is also contained in \(I\). As ideals
+are also closed under addition, it follows that \(u_{1} r_{1j} + \cdots +
+u_{m} r_{m j}\) are all elements of \(I\). Thus, \(x\) can be written as a
+linear combination of the basis vectors with the coefficients coming from
+\(I\).
+
+For the proof of Nakayama's lemma, it too follows the standard, informal
+mathematical argument. Do induction on the number of vectors needed to generate
+the module \(M\). The base case where \(M\) is generated by 0 vectors is by
+definition true since an empty linear combination is conventionally taken to be
+the zero vector. The inductive case where \(M\) is generated by the vectors
+\(b_{1}, \dots, b_{m}, b_{m+1}\). By assumption \(M = \mathfrak{m} M\) with
+\(b_{1}\in M\). Then \(b_{1}\in\mathfrak{m} M\) meaning that by our lemma,
+there exists a linear combination for \(b_{1}\), say
+\[b_{1} = u_{1} b_{1} + \cdots + u_{m+1} b_{m+1}\]
+for some \(u_{1}, \dots, u_{m+1}\in\mathfrak{m}\). Collect the \(b_{1}\) terms
+on the left-hand side of the equation to get that
+\[(1 - u_{1}) b_{1} = u_{2} b_{2} + \cdots + u_{m+1} b_{m+1}\text{.}\]
+As mentioned when defining maximal ideals, \(\mathfrak{m}\) can only contain
+non-units. Namely, \(u_{1}\) must be a non-unit. Then we had already proven
+that \(1 - u_{1}\) is a unit as we are in a local ring. Let \(v_{1}\) be the
+multiplicative inverse of \(1 - u_{1}\), and multiply it on both sides of the
+equation.
+\begin{align*}
+  v_{1} (1 - u_{1}) b_{1}
+    & = v_{1} u_{2} b_{2} + \cdots + v_{1} u_{m+1} b_{m+1} \\
+  1 b_{1} & = \\
+  b_{1} & = v_{1} u_{2} b_{2} + \cdots + v_{1} u_{m+1} b_{m+1} \\
+\end{align*}
+We have thus found that one of the basis vectors is not needed to generate this
+module. Using the induction hypothesis, we have that \(M = 0\). Showing that
+the induction hypothesis holds in Coq takes more work than in an informal
+proof, but this extra work is just a lot of bookkeeping.
 \end{document}

### 2022-10-19 nakayama/paper.tex
Started introduction and added minor updates to preamble and references

@@
 
-\newtheorem*{theorem}{Theorem}
+\input{preamble.tex}
 
@@
 % ssreflect still looks to only deal with finite/discrete objects
+
+\title{Formalizing Theoretical Commutative Algebra in Coq: \\ Nakayama's Lemma}
+
+%\thanks{}
+\date{}
+
+%\author{}
+%\address{}
+%\email{}
+
+\maketitle
+
+%\begin{abstract}
+%	Abstract here
+%\end{abstract}
+
+\section{Introduction}
+
+A number of structures from abstract algebra have been formalized using the proof assistant Coq \cite{the_coq_development_team_2019_3476303}.  
+That said, for higher-level algebra, there currently appears to be a computational emphasis. 
+For instance, the commutative-algebraic notion of a Gr\"obner basis, a special type of generating set for an ideal in a ring of polynomials, and which has cryptographic applications, has gathered significant attention (e.g., see \cite{thery-buchberger}).
+
+The mathematical field of commutative algebra not only has further applications to cryptography, but also in other areas of science and technology such as data science and the study of the human genome.
+Commutative algebra stems from the study of polynomial equations, and now centers around commutative rings--rings whose multiplication satisfies the commutative law, ideals of these rings, and modules over them.
+It has powerful connections with other areas of theoretical mathematics including number theory and algebraic geometry.
+
+We create a formal proof of Nakayama's lemma, a classical theorem in commutative algebra, in Coq. 
+%
+% ``lemma'' appearing in its name 
+%\footnote{},
+%
+In doing so, we formalize, from scratch, certain algebraic structures that are essential to higher-level algebra, including local rings and modules over commutative rings. 
+%
+The notion of a module over a ring is an extension of the linear-algebraic notion of a vector space over a field, ubiquitous in mathematics and its applications. 
+Nakayama's lemma exhibits one way that a finitely generated module over a commutative ring behaves like a vector space over a field.
+
+\begin{nak*}
+Let $R$ be a commutative local ring with maximal ideal $\mathfrak{m}$, and suppose that $M$ is a finitely generated $R$-module.  If $M = \mathfrak{m} M$, then $M = 0$.
+\end{nak*}
+
+\section{Mathematical Basis and Motivation}
+
+\section{Formalization}
 
@@
 proof, but this extra work is just a lot of bookkeeping.
+
+\bibliographystyle{plain}
+\bibliography{references}
+
 \end{document}

### 2022-10-20 nakayama/paper.tex
Updated Introduction, minor updates to preamble and references files

@@
 
-\title{Formalizing Theoretical Commutative Algebra in Coq: \\ Nakayama's Lemma}
+\title{%Formalizing 
+Theoretical Commutative Algebra in Coq: \\ Nakayama's Lemma}
 
@@
 A number of structures from abstract algebra have been formalized using the proof assistant Coq \cite{the_coq_development_team_2019_3476303}.  
-That said, for higher-level algebra, there currently appears to be a computational emphasis. 
+That said, there currently appears to be a computational emphasis with regard to higher-level algebra, with more formalization of discrete objects and algorithmic processes rather than the verification of more abstract theorems.
 For instance, the commutative-algebraic notion of a Gr\"obner basis, a special type of generating set for an ideal in a ring of polynomials, and which has cryptographic applications, has gathered significant attention (e.g., see \cite{thery-buchberger}).
 
-The mathematical field of commutative algebra not only has further applications to cryptography, but also in other areas of science and technology such as data science and the study of the human genome.
-Commutative algebra stems from the study of polynomial equations, and now centers around commutative rings--rings whose multiplication satisfies the commutative law, ideals of these rings, and modules over them.
-It has powerful connections with other areas of theoretical mathematics including number theory and algebraic geometry.
+The mathematical field of commutative algebra not only has further applications to cryptography, but also in other areas of science and technology such as data science, and the study of the human genome.
+The field stems from the study of polynomial equations, and now centers around commutative rings, i.e., those whose multiplication satisfies the commutative law, along with ideals of these rings, and modules over them.
+Commutative algebra has meaningful connections with other areas of theoretical mathematics, including number theory and algebraic geometry.
 
-We create a formal proof of Nakayama's lemma, a classical theorem in commutative algebra, in Coq. 
-%
-% ``lemma'' appearing in its name 
-%\footnote{},
-%
-In doing so, we formalize, from scratch, certain algebraic structures that are essential to higher-level algebra, including local rings and modules over commutative rings. 
+We construct a formal proof of \emph{Nakayama's lemma} \cite{nakayama-1951, azumaya}, a fundamental theorem in the field of commutative algebra, in Coq. 
+Sometimes also called the Krull-Azumaya theorem\footnote{Hideyuki Matsumura explains in his text \emph{Commutative Algebra} \cite{matsumura}:  \emph{This simple but important lemma is due to T.\ Nakayama, G.\ Azumaya
+and W.\ Krull. Priority is obscure, and although it is usually called the Lemma of Nakayama, late Prof.\ 
+Nakayama did not like the name.}}  \cite{nagata}, Nakayama's lemma is typically introduced in a first graduate course in commutative algebra \cite{atiyah-macdonald, matsumura, eisenbud}, and is applied widely in the field.
+%It is widely applied throughout algebra. %, true to the convention that ``lemma'' often refers to a result serving as a stepping stone toward another.  However, Nakayama's lemma 
+%is also an important result in its own right, and can be thought of as one of the fundamental theorems of 
+%commutative algebra, not unlike the fundamental theorems of calculus describing the inverse relationship between derivatives and integrals or the fundamental theorem of arithmetic that makes precise the notion of unique factorization.
+%, or the fundamental theorem of algebra (or \emph{d'Alembert's theorem}) on the roots of complex polynomials.
+
+In order to prove Nakayama's lemma,  we formalize certain algebraic structures that are essential to higher-level algebra, including \emph{local rings} and \emph{modules over commutative rings}. 
 %
@@
 
+\emily[inline]{Add link to github for code?}
+
+\section{Mathematical basis and motivation}
+
 \begin{nak*}
@@
 \end{nak*}
-
-\section{Mathematical Basis and Motivation}
 

### 2022-11-01 nakayama/paper.tex
Added Gonthier & Mahboubi SSR tutorial
Updates to mathematical basis section

@@
 
-A number of structures from abstract algebra have been formalized using the proof assistant Coq \cite{the_coq_development_team_2019_3476303}.  
-That said, there currently appears to be a computational emphasis with regard to higher-level algebra, with more formalization of discrete objects and algorithmic processes rather than the verification of more abstract theorems.
-For instance, the commutative-algebraic notion of a Gr\"obner basis, a special type of generating set for an ideal in a ring of polynomials, and which has cryptographic applications, has gathered significant attention (e.g., see \cite{thery-buchberger}).
+The mathematical field of \emph{commutative algebra} stems from the study of solutions to polynomial equations, and now centers around \emph{commutative rings}, i.e., rings whose multiplication satisfies the commutative law, \emph{ideals} of these rings, and \emph{modules} over them.
+Commutative algebra has broad applications to science and technology, including in the field of robotics, and the study of the human genome.
+The commutative-algebraic notion of a Gr\"obner basis, a special type of generating set for an ideal in a ring of polynomials, has become a fundamental computational tool in 
+coding theory and cryptography (e.g., see  \cite{grobner-bases-cryptography}).
+A implementation of Buchberger's algorithm \cite{buchberger} for determining 
+Gr\'obner bases of ideals in polynomial rings has been proved correct within the proof assistant Coq \cite{the_coq_development_team_2019_3476303,thery-buchberger}, and an integrated formal development of the algorithm in Coq has also been carried out \cite{persson2001integrated} (see also \cite{grobner-type-theory}).
 
-The mathematical field of commutative algebra not only has further applications to cryptography, but also in other areas of science and technology such as data science, and the study of the human genome.
-The field stems from the study of polynomial equations, and now centers around commutative rings, i.e., those whose multiplication satisfies the commutative law, along with ideals of these rings, and modules over them.
-Commutative algebra has meaningful connections with other areas of theoretical mathematics, including number theory and algebraic geometry.
+In a more theoretical direction, 
+we formally prove \emph{Nakayama's lemma} \cite{nakayama-1951, azumaya}, a fundamental theorem in the field of commutative algebra, in Coq.
 
-We construct a formal proof of \emph{Nakayama's lemma} \cite{nakayama-1951, azumaya}, a fundamental theorem in the field of commutative algebra, in Coq. 
 Sometimes also called the Krull-Azumaya theorem\footnote{Hideyuki Matsumura explains in his text \emph{Commutative Algebra} \cite{matsumura}:  \emph{This simple but important lemma is due to T.\ Nakayama, G.\ Azumaya
@@
 \bibliography{references}
-
 \end{document}

### 2022-11-02 nakayama/paper.tex
Minor updates to motivation section

@@
 
-%\begin{abstract}
-%	Abstract here
-%\end{abstract}
+\begin{abstract}
+\emily[inline]{	Abstract here }
+\end{abstract}
+
+\emily[inline]{Any suggested changes to the current title are welcome.  Moreover, different fields have different standards for style, etc., so feel free to update prose/citations as appropriate. }
+\emily[inline]{Add link to github for code?}
 
@@
 
-In a more theoretical direction, 
-we formally prove \emph{Nakayama's lemma} \cite{nakayama-1951, azumaya}, a fundamental theorem in the field of commutative algebra, in Coq.
+Our goal is to newly formalize theoretical, rather than computational, commutative algebra in Coq.
+We formally prove \emph{Nakayama's lemma} \cite{nakayama-1951, azumaya}, a fundamental theorem in the field.
+In the process of doing so,  we formalize certain algebraic structures  essential to higher-level algebra, including \emph{local rings} and \emph{modules over commutative rings}.
 
-Sometimes also called the Krull-Azumaya theorem\footnote{Hideyuki Matsumura explains in his text \emph{Commutative Algebra} \cite{matsumura}:  \emph{This simple but important lemma is due to T.\ Nakayama, G.\ Azumaya
-and W.\ Krull. Priority is obscure, and although it is usually called the Lemma of Nakayama, late Prof.\ 
-Nakayama did not like the name.}}  \cite{nagata}, Nakayama's lemma is typically introduced in a first graduate course in commutative algebra \cite{atiyah-macdonald, matsumura, eisenbud}, and is applied widely in the field.
-%It is widely applied throughout algebra. %, true to the convention that ``lemma'' often refers to a result serving as a stepping stone toward another.  However, Nakayama's lemma 
+The notion of a module over a ring is an extension of the linear-algebraic notion of a vector space over a field, ubiquitous in mathematics and its applications. 
+Less frequently referred to as the \emph{Krull-Azumaya theorem}\footnote{Hideyuki Matsumura explains in his text \emph{Commutative Algebra} \cite{matsumura}:  ``{This simple but important lemma is due to T.\ Nakayama, G.\ Azumaya
+and W.\ Krull. Priority is obscure, and although it is usually called the Lemma of Nakayama, late Prof.\  Nakayama did not like the name.''}}\,\cite{nagata}, Nakayama's lemma 
+describes one way that a finitely generated module over an arbitrary commutative ring acts like a vector space over a field.  
+True to the convention that ``lemma'' often refers to a result serving as a stepping stone toward another goal, Nakayama's lemma is applied widely throughout the field, and the result is typically introduced in a first graduate course in commutative algebra \cite{atiyah-macdonald, matsumura, eisenbud}.
+
+%It is widely applied throughout algebra. %, true to .  However, Nakayama's lemma 
 %is also an important result in its own right, and can be thought of as one of the fundamental theorems of 
@@
 
-In order to prove Nakayama's lemma,  we formalize certain algebraic structures that are essential to higher-level algebra, including \emph{local rings} and \emph{modules over commutative rings}. 
-%
-The notion of a module over a ring is an extension of the linear-algebraic notion of a vector space over a field, ubiquitous in mathematics and its applications. 
-Nakayama's lemma exhibits one way that a finitely generated module over a commutative ring behaves like a vector space over a field.
+\section{Mathematical basis and motivation}
 
-\emily[inline]{Add link to github for code?}
+In abstract algebra, the quintessential example of a \emph{commutative ring} is the collection of all integers \[\mathbb{Z} = \{ \ldots, -3, 2, -1, 0, 1, 2, 3, \ldots \}\]
+One can add or multiply any two integers to obtain another, both of these binary operations satisfy the associative and commutative laws, and the distributive law governing their compatibility holds.
 
-\section{Mathematical basis and motivation}
+In general, a ring is a set $R$ with two binary operations, which we call \emph{addition} and \emph{mutiplication}, typically denoted $\cdot$ and $+$, respectively.
+Under addition, $R$ must be an abelian group, meaning that addition satisfies the associative and commutative laws, and $R$ must contain an additive identity and negatives, i.e., there exists an element $0 \in R$ such that for all $r \in R$,  $r+0 = r$  and there exists an element denoted $-r$ in $R$ for which $r + (-r) = 0$.
+Moreover, multiplication must satisfy the associative law, and the distributive law on the compatibility of addition and multiplication must hold, i.e., for all $r, s, t \in R$, $r \cdot (s+t) = (r \cdot s)  + (r \cdot t)$ and $(r+s)\cdot t = (r \cdot t) + (s \cdot t)$.
+
+%$R$ must have an multiplicative identity, an element $1 \in R$ such that $1 \cdot r = r \cdot 1 = r$ for every $r \in R$, .  Finally, the
+
+The
+
+An \emph{ideal} of commutative ring $R$ is a subset $I$ of $R$ that is itself
 
@@
 \end{nak*}
+
+\emily[inline]{Add description of alternate statements of Nakayama.}
 

### 2022-11-03 nakayama/paper.tex
Updates to math background, and references added

@@
 
-\title{%Formalizing 
-Theoretical Commutative Algebra in Coq: \\ Nakayama's Lemma}
+\title{ 
+Formal Commutative Algebra in Coq: \\ Nakayama's Lemma\thanks{Source code for this work is available on the following site: \url{https://github.com/ku-sldg/algebra}}
+}
 
-%\thanks{}
 \date{}
@@
 %\author{}
-%\address{}
+\author{
+
+	Authors
+
+	\vspace{.2cm}
+
+	\\
+
+	Institute for Information Sciences \\
+	The University of Kansas \\
+	Lawrence, KS 66045}
 %\email{}
+
+%\thanks{Witt acknowledges support from NSF CAREER Award DMS-1945611 and the 2022-23 Ruth I.\, Michler Memorial Prize from the Association for Women in Mathematics.}
 
@@
 
-\emily[inline]{Any suggested changes to the current title are welcome.  Moreover, different fields have different standards for style, etc., so feel free to update prose/citations as appropriate. }
-\emily[inline]{Add link to github for code?}
+\noindent \textbf{Keywords:}
+Formalization of Mathematics,
+Formal Proof,
+Commutative Algebra,
+Commutative Ring,
+Ideal,
+Module over a Ring.
 
@@
 
-The mathematical field of \emph{commutative algebra} stems from the study of solutions to polynomial equations, and now centers around \emph{commutative rings}, i.e., rings whose multiplication satisfies the commutative law, \emph{ideals} of these rings, and \emph{modules} over them.
-Commutative algebra has broad applications to science and technology, including in the field of robotics, and the study of the human genome.
+The mathematical field of \emph{commutative algebra} stems from the study of solutions to polynomial equations.
+Research in the field now centers around \emph{commutative rings}--rings in which order does not affect multiplication, i.e., $x \cdot y = y \cdot x$ for any ring elements $x$ and $y$--and fundamental algebraic objects associated to them:  \emph{ideals} of these rings, and \emph{modules} over them.
+Commutative algebra has deep connections with other areas of theoretical mathematics, including number theory and algebraic geometry.
+
+Commutative algebra also has broad applications to science and technology.
+For instance, it has been integral to advances in robotics \cite{cox-little-oshea}, and has helped form our current understanding of the human genome \cite{genetic-algebra}.
 The commutative-algebraic notion of a Gr\"obner basis, a special type of generating set for an ideal in a ring of polynomials, has become a fundamental computational tool in 
@@
 A implementation of Buchberger's algorithm \cite{buchberger} for determining 
-Gr\'obner bases of ideals in polynomial rings has been proved correct within the proof assistant Coq \cite{the_coq_development_team_2019_3476303,thery-buchberger}, and an integrated formal development of the algorithm in Coq has also been carried out \cite{persson2001integrated} (see also \cite{grobner-type-theory}).
+Gr\"obner bases of ideals in polynomial rings has been proved correct within the proof assistant Coq \cite{the_coq_development_team_2019_3476303,thery-buchberger}, and an integrated formal development of the algorithm in Coq has also been carried out \cite{persson2001integrated} (see also \cite{grobner-type-theory}).
 
@@
 
-\section{Mathematical basis and motivation}
+\section{Mathematical Basis and Motivation}
 
-In abstract algebra, the quintessential example of a \emph{commutative ring} is the collection of all integers \[\mathbb{Z} = \{ \ldots, -3, 2, -1, 0, 1, 2, 3, \ldots \}\]
-One can add or multiply any two integers to obtain another, both of these binary operations satisfy the associative and commutative laws, and the distributive law governing their compatibility holds.
+\subsection{The Fundamental Algebraic Objects}
 
-In general, a ring is a set $R$ with two binary operations, which we call \emph{addition} and \emph{mutiplication}, typically denoted $\cdot$ and $+$, respectively.
-Under addition, $R$ must be an abelian group, meaning that addition satisfies the associative and commutative laws, and $R$ must contain an additive identity and negatives, i.e., there exists an element $0 \in R$ such that for all $r \in R$,  $r+0 = r$  and there exists an element denoted $-r$ in $R$ for which $r + (-r) = 0$.
-Moreover, multiplication must satisfy the associative law, and the distributive law on the compatibility of addition and multiplication must hold, i.e., for all $r, s, t \in R$, $r \cdot (s+t) = (r \cdot s)  + (r \cdot t)$ and $(r+s)\cdot t = (r \cdot t) + (s \cdot t)$.
+\emily[inline]{Something about building up a lot}
 
-%$R$ must have an multiplicative identity, an element $1 \in R$ such that $1 \cdot r = r \cdot 1 = r$ for every $r \in R$, .  Finally, the
+\paragraph{Commutative rings.}
+In abstract algebra, the quintessential example of a commutative ring is the set of integers
+\[\mathbb{Z} = \{ \ldots, -3, -2, -1, 0, 1, 2, 3, \ldots \}.\]
+using the natural definitions of addition and multiplication.
 
-The
+Adding two integers produces another, and the associative and commutative laws hold for addition.
+The integers form an \emph{abelian group} under addition since $0 \in \mathbb{Z}$ is the \emph{additive identity} in the sense that adding zero has no effect on any integer, and given any integer $n$, the integer $-n$ is its \emph{additive inverse} in the sense that the sum of $n$ and $-n$ is the additive identity $0$.
 
+The set of integers also forms a \emph{ring} because it is closed under multiplication, which again satisfies associativity, and the distributive law governing the compatibility of addition and multiplication holds.
+Even more, the integers form a 
+\emph{commutative ring} since $n \cdot m = m \cdot n$ for all integers $n$ and $m$.
+Moreover,  the integer $1$ is the ring's \emph{multiplicative identity}, since for any  $n \in \mathbb{Z}$ one has $n \cdot 1 = 1 \cdot n = n$, $\mathbb{Z}$ is, furthermore, a \emph{commutative ring with identity}.
+
+In general, a \emph{ring} is a set $R$ with two binary operations, which we call \emph{addition} and \emph{mutiplication}, typically denoted $\cdot$ and $+$, respectively.
+As motivated by the properties of the ring of integers, addition, $R$ must be an abelian group, multiplication must be associative, and the distributive law must hold, i.e., for all $x, y, z \in R$, $(x+y)\cdot z = x \cdot z + y \cdot z$ and $x \cdot (y+z) = x \cdot y + x \cdot z$.
+
+\emily[inline]{Quickly mention familiar examples}
+
+We will use $0$ to refer to an additive identity, and $1$ will represent a multiplicative identity.
+
+Rather than call upon the \emph{Mathematical Components Library} 
+ for Coq \cite{mathcomp}
+
+\paragraph{Ideals.}
+The concept of an {ideal} of a ring can be thought of as an extension of the notion of an integer $x$ in the ring of integers $\mathbb{Z}$. 
 An \emph{ideal} of commutative ring $R$ is a subset $I$ of $R$ that is itself 
+an abelian group under addition,  
+which satisfies the following ``absorption'' property: Given any element $a$ of $I$, 
+the product  $x \cdot a$ is again in $I$ for any ring element $x \in R$.
+
+One can verify that given any integer $n$, the set $n\mathbb{Z}$ of its multiples forms an ideal of $\mathbb{Z}$.
+For instance, $2 \mathbb{Z}$ consists of all even numbers, and is an abelian group under addition: the sum of two even numbers is even, the additive identity $0$ is eve, and the negative of an even number is even.
+Moreover, the absorption property holds since the product of any integer and an even number is again even. 
+In fact, every ideal of the ring of integers has this form $n\mathbb{Z}$ for some integer $n$, though ideals in general commutative rings can have more complicated properties.
+
+Since every integer $n$ can be written as $1 \cdot n$, the ideal $1 \mathbb{Z}$ is the entire ring $\mathbb{Z}$.
+One can see that given a commutative ring $R$ itself satisfies the axioms required to be an ideal of $R$.
+We call an ideal $I$ of $R$ \emph{proper} if it is strictly contained in $R$.
+Every commutative ring with unity contains the proper ideal consisting solely of the additive identity $0$.
+
+A \emph{maximal ideal} of a commutative ring is a proper ideal that is maximal with respect to inclusion, i.e., no other proper ideal strictly contains it. 
+Going back to the ring of integers, $6 \mathbb{Z} \subsetneq 2 \mathbb{Z}$ since every multiple of $6$ is even, 
+so $6 \mathbb{Z}$ is not a maximal ideal of $\mathbb{Z}$. 
+However, no proper ideal $I$ contains $2 \mathbb{Z}$:  If $2 \mathbb{Z}\subsetneq I \subsetneq \mathbb{Z}$, then $I$  would necessarily contain an odd number $n$.
+Writing $n=2k+1$ for some integer $k$, we notice that since $-2k = 2 \cdot -k$  is in $2\mathbb{Z}$, it is also an element of the larger set $I$, and since $I$ is an abelian group under addition, $(2k+1) + $
+
+In fact, $3 \mathbb{Z}$
+
+\subsection{Nakayama's Lemma, Informally}
 
@@
 \section{Formalization}
+
+\subsection{Our Algebraic Hierarchy}
 
@@
 
+\section{Formally Proving Nakayama's Lemma}
+
 \begin{theorem}[Nakayama's lemma]

### 2022-11-04 nakayama/paper.tex
Finished draft of math background, moving to informal NAK description

@@
 \author{ 
-
 	Authors  
-
+%	
 	\vspace{.2cm}		
-
 	\\ 
-
+%	
 	Institute for Information Sciences \\
 	The University of Kansas \\
-	Lawrence, KS 66045}
+	Lawrence, KS 66045
+	}
 %\email{}
@@
 \begin{abstract}
-\emily[inline]{	Abstract here }
+\emily[inline]{Abstract here }
 \end{abstract}
@@
 Commutative Ring,
+Local Ring,
 Ideal,
-Module over a Ring.
+Module over a Ring,
+Finitely Generated Module.
 
@@
 Our goal is to newly formalize theoretical, rather than computational, commutative algebra in Coq. 
-We formally prove \emph{Nakayama's lemma} \cite{nakayama-1951, azumaya}, a fundamental theorem in the field.
-In the process of doing so,  we formalize certain algebraic structures  essential to higher-level algebra, including \emph{local rings} and \emph{modules over commutative rings}.
+We formally prove \emph{Nakayama's lemma} \cite{nakayama-1951, azumaya}, an essential result in the field. 
+In doing so, we formalize algebraic structures that are fundamental to higher-level algebra, such as 
+\emph{local rings} and \emph{(finitely generated) modules over commutative rings}. 
+Rather than build upon some of the basic objects from abstract algebra, such as groups and rings, that have been formalized in Coq, e.g., in the  
+\emph{Mathematical Components Library} 
+\cite{mathcomp}, we start from scratch.
 
@@
 
-\subsection{The Fundamental Algebraic Objects}
+\subsection{The Fundamental Algebraic Structures}
 
-\emily[inline]{Something about building up a lot}
+Here, we touch upon the mathematical structures from commutative algebra that are formalized.
 
@@
 
-The set of integers also forms a \emph{ring} because it is closed under multiplication, which again satisfies associativity, and the distributive law governing the compatibility of addition and multiplication holds.
+The set of integers also forms a \emph{ring} due to its properties of multiplication.  
+It is closed under this binary operation, which satisfies associativity.  
+The integer $1$ is a   \emph{multiplicative identity} since for any  $n \in \mathbb{Z}$ one has $n \cdot 1 = 1 \cdot n = n$.
+Finally, the the distributive law governing the compatibility of addition and multiplication holds.
 Even more, the integers form a 
 \emph{commutative ring} since $n \cdot m = m \cdot n$ for all integers $n$ and $m$.
-Moreover,  the integer $1$ is the ring's \emph{multiplicative identity}, since for any  $n \in \mathbb{Z}$ one has $n \cdot 1 = 1 \cdot n = n$, $\mathbb{Z}$ is, furthermore, a \emph{commutative ring with identity}.
 
-In general, a \emph{ring} is a set $R$ with two binary operations, which we call \emph{addition} and \emph{mutiplication}, typically denoted $\cdot$ and $+$, respectively.
-As motivated by the properties of the ring of integers, addition, $R$ must be an abelian group, multiplication must be associative, and the distributive law must hold, i.e., for all $x, y, z \in R$, $(x+y)\cdot z = x \cdot z + y \cdot z$ and $x \cdot (y+z) = x \cdot y + x \cdot z$.
+In general, a commutative ring is a set $R$ with two binary operations, which we call \emph{addition} and \emph{mutiplication}, typically denoted $\cdot$ and $+$, respectively.
+As motivated by the properties of the ring of integers, addition, $R$ must be an abelian group, multiplication must be associative, $R$ must have a multiplicative identity, and the distributive law must hold, i.e., for all $r, s, t \in R$, $(r+s)\cdot t = r \cdot t + s \cdot t$ and $r \cdot (s+t) = r \cdot s + r \cdot t$.
 
-\emily[inline]{Quickly mention familiar examples}
-
-We will use $0$ to refer to an additive identity, and $1$ will represent a multiplicative identity.
-
-Rather than call upon the \emph{Mathematical Components Library} 
- for Coq \cite{mathcomp}
+Other familiar examples of commutative rings include the integers modulo a fixed integer $n>0$, fields--commutative rings in which every nonzero element has a multiplicative inverse--such as the rings of rational numbers, real numbers, and complex numbers, and rings of polynomials in a variable $x$ with integer coefficients, or with coefficients in a field.
 
@@
 One can verify that given any integer $n$, the set $n\mathbb{Z}$ of its multiples forms an ideal of $\mathbb{Z}$.
-For instance, $2 \mathbb{Z}$ consists of all even numbers, and is an abelian group under addition: the sum of two even numbers is even, the additive identity $0$ is eve, and the negative of an even number is even.
+For instance, $2 \mathbb{Z}$ consists of all even numbers, and is an abelian group under addition: the sum of two even numbers is even, the additive identity $0$ is even, and the negative of an even number is even.
 Moreover, the absorption property holds since the product of any integer and an even number is again even. 
@@
 A \emph{maximal ideal} of a commutative ring is a proper ideal that is maximal with respect to inclusion, i.e., no other proper ideal strictly contains it. 
-Going back to the ring of integers, $6 \mathbb{Z} \subsetneq 2 \mathbb{Z}$ since every multiple of $6$ is even, 
+Returning to our example of the ring of integers, $6 \mathbb{Z} \subsetneq 2 \mathbb{Z}$ since every multiple of $6$ is even, 
 so $6 \mathbb{Z}$ is not a maximal ideal of $\mathbb{Z}$. 
 However, no proper ideal $I$ contains $2 \mathbb{Z}$:  If $2 \mathbb{Z}\subsetneq I \subsetneq \mathbb{Z}$, then $I$  would necessarily contain an odd number $n$.
-Writing $n=2k+1$ for some integer $k$, we notice that since $-2k = 2 \cdot -k$  is in $2\mathbb{Z}$, it is also an element of the larger set $I$, and since $I$ is an abelian group under addition, $(2k+1) + $
+Writing $n=2k+1$ for some integer $k$, we notice that since $-2k$ is in $2\mathbb{Z}$, it is also an element of the larger set $I$, and since $I$ is an abelian group under addition, $(2k+1) + (-2k) = 1$ is also in the ideal $I$.
+However, in this case, every integer $n = n \cdot 1$ is in $I$ by absorption, so $I = \mathbb{Z}$ is not a proper ideal, a contradiction.
 
-In fact, $3 \mathbb{Z}$
+In fact, $3 \mathbb{Z}$ is the only other maximal ideal of $\mathbb{Z}$ containing $6 \mathbb{Z}$, and in general, the prime ideals in the ring of integers besides the zero ideal are those of the form $p \mathbb{Z}$, where $p$ a prime number.
+
+A commutative ring is \emph{local} if it has exactly one maximal ideal.  
+Every field is local since the only proper ideal of a field is the zero ideal. 
+By our observations above, the ring of integers is not local. 
+However, the set of all rational numbers that can be written with an odd denominator does form a subring of all rational numbers, and its unique maximal ideal consists of the elements with even numerator; in fact, this ring is the so-called \emph{localization} of $\mathbb{Z}$ at the maximal ideal $2 \mathbb{Z}$.
+The ring of polynomials over a field in a variable $x$ is not local, but the ring of all formal power series is local; its maximal ideal consists of the power series with no constant term. 
+The ring of integers modulo $n>1$ is local if and only if $n$ is a power of a prime number $p$,  in which case the unique maximal ideal consists of all multiples of $p$.
+
+%Hence the ring of integers is not local, but 
+%the ring of integers modulo an integer $n>1$,  often denoted $\mathbb{Z}/n\mathbb{Z}$ or $\mathbb{Z}_n$, are local
+
+\paragraph{A module over a commutative ring.}  Let  $R$ be a commutative ring. 
+A \emph{module over $R$}, or \emph{$R$-module}, is an abelian group $M$ under a binary operation $+$, and a {scalar multiplication} $R \times M \to M$ denoted $\cdot$, satisfying the following compatibility properties for all $r, s \in R$ and $u, v \in M$.
+
+\begin{enumerate}[leftmargin=2cm,topsep=0cm,itemsep=0cm]
+\item  $r \cdot (u + v)  = r \cdot u + r \cdot v$
+\item $(r+s) \cdot u = r \cdot u + s \cdot u$
+\item $(rs) \cdot u = r \cdot (s \cdot u)$
+\item $1 \cdot u = u$ 
+\end{enumerate}
+
+From this definition, one can see that a module over a field $F$ is precisely an $F$-vector space, so the notion of a module over an arbitrary commutative ring extends that of a vector space over a field.
+Finitely generated vector spaces form the foundation for matrix algebra, and the extension of this notion to module theory is needed to state Nakayama's Lemma.
+We call an $R$-module $M$ \emph{finitely generated} if there exist a fixed finite number of elements $u_1, \ldots, u_n$ of $M$ with the following property:  Given any  $w \in M$, there exist $r_1, \ldots, r_n \in R$ for which
+\[
+w = r_1 u_1 + r_1 u_2 + \cdots + r_n u_n.
+\]
+When $R=F$ is a field and $M=V$ is a finite-dimensional vector space over $F$, one can choose $u_1, \ldots, u_n$ to be a basis for $V$, i.e., $n = \dim V$.
+In this case, the choice of scalar coefficients in the expression above for $w \in V$ is unique.
+When $R$ is not a field, modules can have more subtle properties, and such expression is typically not unique.
 
 \subsection{Nakayama's Lemma, Informally}
+
+In order to state Nakayama's Lemma, we clarify some notation:  If $I$ is an ideal of a commutative ring $R$ and 
+ $M$ is an $R$-module, then $IM$ is the set of elements of the form 
+	$a_1 u_1 + a_2 u_2 + \cdots + a_k u_k$, where $a_1, \ldots, a_k \in I$ and $u_1, \ldots, u_k \in M$.  
+Notice that by the absorption property of ideals, $IM$ is an $R$-module contained in $M$.
 

### 2022-11-04 nakayama/paper.tex
Finished draft of Informal NAK section

@@
 
-Here, we touch upon the mathematical structures from commutative algebra that are formalized.
+Here, we give a brief description of the major mathematical structures from commutative algebra that are relevant to Nakayama's Lemma.
 
@@
 We call an ideal $I$ of $R$ \emph{proper} if it is strictly contained in $R$.
-Every commutative ring with unity contains the proper ideal consisting solely of the additive identity $0$.
+The \emph{zero ideal} consisting solely of its additive identity is a proper ideal of any commutative ring.
 
@@
 A commutative ring is \emph{local} if it has exactly one maximal ideal.  
-Every field is local since the only proper ideal of a field is the zero ideal. 
-By our observations above, the ring of integers is not local. 
+Every field is local since the only proper ideal of a field is the zero ideal, though by our observations above, the ring of integers is not local. 
 However, the set of all rational numbers that can be written with an odd denominator does form a subring of all rational numbers, and its unique maximal ideal consists of the elements with even numerator; in fact, this ring is the so-called \emph{localization} of $\mathbb{Z}$ at the maximal ideal $2 \mathbb{Z}$.
-The ring of polynomials over a field in a variable $x$ is not local, but the ring of all formal power series is local; its maximal ideal consists of the power series with no constant term. 
 The ring of integers modulo $n>1$ is local if and only if $n$ is a power of a prime number $p$,  in which case the unique maximal ideal consists of all multiples of $p$.
+
+The ring of polynomials over a field $F$ in a variable $x$ is not local; in fact, given any irreducible polynomial $f(x)$, the set of its multiples is a maximal ideal of the polynomial ring $F[x]$.
+On the other hand , the ring of formal power series over $F$ in $x$  is local; its maximal ideal consists of the power series with no constant term.
 
@@
 
-\subsection{Nakayama's Lemma, Informally}
+\subsection{Nakayama's Lemma, Informal Statement}
 
-In order to state Nakayama's Lemma, we clarify some notation:  If $I$ is an ideal of a commutative ring $R$ and 
+In order to state Nakayama's Lemma, we explain some notation:  If $I$ is an ideal of a commutative ring $R$ and 
  $M$ is an $R$-module, then $IM$ is the set of elements of the form 
-	$a_1 u_1 + a_2 u_2 + \cdots + a_k u_k$, where $a_1, \ldots, a_k \in I$ and $u_1, \ldots, u_k \in M$.  
-Notice that by the absorption property of ideals, $IM$ is an $R$-module contained in $M$.
+	$a_1 u_1 + a_2 u_2 + \cdots + a_k u_k$, where, for some positive integer $k$, $a_1, \ldots, a_k \in I$ and $u_1, \ldots, u_k \in M$.  
+Notice that due to the absorption property of ideals, $IM$ is an $R$-module contained in $M$.
+
+If an $R$-module $M$ consists of only one element, this element must be its additive identity $0$ as an abelian group under addition.  We use the notation $M=0$ in this case.
 
 \begin{nak*}
-Let $R$ be a commutative local ring with maximal ideal $\mathfrak{m}$, and suppose that $M$ is a finitely generated $R$-module.  If $M = \mathfrak{m} M$, then $M = 0$.
+Let $R$ be a commutative local ring, and let $\mathfrak{m}$ denote its unique maximal ideal. 
+If $M$ is a finitely generated $R$-module and $M = \mathfrak{m} M$, then $M = 0$.
 \end{nak*}
 
-\emily[inline]{Add description of alternate statements of Nakayama.}
+When $R=F$ is a field, its unique maximal ideal is the zero ideal, and given any vector space $M=V$ over $F$, the only linear combination of vectors with coefficients in the zero ideal is the zero vector.
+Hence in this special case, the hypothesis that  $M = \mathfrak{m} M$ is equivalent to the conclusion that $M=0$.
+Hence Nakayama's lemma describes one way that finitely generated modules over commutative local rings are similar to vector spaces.
+
+In general, the quotient $R/\mathfrak{m}$ of a local ring modulo its maximal ideal $\mathfrak{m}$ is a field, and the quotient of a module $M$ modulo the submodule $\mathfrak{m}M$ is an $R/\mathfrak{m}$-module, i.e., $M/\mathfrak{m}M$ is a vector space over $R/\mathfrak{m}$.
+Nakayama's lemma implies that if $M$ is finitely generated, then bases for $M/\mathfrak{m}M$ corresponds, via lifting, to minimal sets of generators of
+$M$.
+
+There are several alternate statements of Nakayama's Lemma that remove the hypothesis that $R$ must be local.
+One can replace the unique maximal ideal with the Jacobson radical of the ring, which is the intersection of all maximal ideals.
+Alternatively, $I$ is an arbitrary proper ideal of a commutative ring $R$ and
+ $M$ is a finitely generated $R$-module for which $M=I M$, then this ensures the existence of a ring element $r$ congruent to $1$ modulo $I$ such that $rM = 0$, i.e., $r u = 0$ for every $u \in M$.
 

### 2022-11-04 nakayama/paper.tex
Edits to prose and math explanation

@@
 The set of integers also forms a \emph{ring} due to its properties of multiplication.  
-It is closed under this binary operation, which satisfies associativity.  
-The integer $1$ is a   \emph{multiplicative identity} since for any  $n \in \mathbb{Z}$ one has $n \cdot 1 = 1 \cdot n = n$.
-Finally, the the distributive law governing the compatibility of addition and multiplication holds.
-Even more, the integers form a 
-\emph{commutative ring} since $n \cdot m = m \cdot n$ for all integers $n$ and $m$.
+It is closed under this binary operation, which satisfies associativity, and the distributive law governing the compatibility of addition and multiplication holds. 
+Even more, the integers form a \emph{commutative ring} 
+ since $n \cdot m = m \cdot n$ for all integers $n$ and $m$.  We require commutative rings to contain a \emph{multiplicative identity}, and $1 \in \mathbb{Z}$ is such an element since 
+   $n \in \mathbb{Z}$ one has $n \cdot 1 = 1 \cdot n = n$.
 
@@
 The ring of polynomials over a field $F$ in a variable $x$ is not local; in fact, given any irreducible polynomial $f(x)$, the set of its multiples is a maximal ideal of the polynomial ring $F[x]$.
-On the other hand , the ring of formal power series over $F$ in $x$  is local; its maximal ideal consists of the power series with no constant term.
+On the other hand, the set of all formal power series  in $x$ over $F$ is a local ring; its maximal ideal consists of the power series with no constant term.
 
@@
 be associative. From here, we build up through monoids, which introduce
-identities, to groups, which introduce inverses. Note the double equals in
+identities, to groups, which introduce inverses. Note the double equals ``$==$'' in
 these definitions is notation for an arbitrary equivalence relation over the
-group's carrier set which acts as equality.
-% \begin{verbatim}
+group's carrier set, which acts as equality.
+
 \begin{minted}{coq}
@@
 \end{minted}
-% \end{verbatim}
-The lines like \verb|monoid_semigroup :> Semigroup equiv op;| simply coerce
+The lines of the form, e.g.,  ``\verb|monoid_semigroup :> Semigroup equiv op;|'' simply coerce
 the monoid typeclass into a semigroup.
 
-While we found later on that we did not need quotients, it is worth remarking
-that we got quotients working rather nicely in Coq using typeclasses. An
-algebraic quotient are an equivalence relation on the algebraic structure which
-preserve that structure. For example, quotient groups are formed by taking a
-subgroup and making every element of that subgroup equivalent to the identity.
-With \texttt{P} being the predicate for the subgroup, there are two ways to
+%While we found later on that we did not need quotients, 
+While in the end, our formal proof did not call upon quotients of algebraic structures, quotient rings and quotient modules are fundamental to commutative algebra, and one can use them to construct alternate proofs of Nakayama's lemma.
+It is worth pointing out that we have formalized quotients of algebraic objects  in Coq using typeclasses, which appear to work rather nicely.
+
+An algebraic quotient is, roughly, the set of equivalence classes of an algebraic structure with respect to an equivalence relation on its elements, for which the set of equivalence classes inherit the same kind of algebraic structure.
+For example, consider the quotient of a group modulo a subgroup, i.e. a subset of elements of the group that it itself a group under the group operations. 
+Under equivalence relation on the group, every element of the subgroup must be in the same equivalence class as the identity.  
+With \texttt{P} the predicate for the subgroup, there are two ways to
 make an equivalence relation from this description.
-% \begin{verbatim}
+
 \begin{minted}{coq}
@@
 % \end{verbatim}
-When these two relations coincide, then we can prove that the equivalence
-relation(s) actually preserve the group structure. Subgroups which have this
+When these two relations coincide, then we can prove that this common equivalence
+relation actually preserves the group structure. Subgroups which have this
 property are called \emph{normal subgroups}.
@@
 \end{minted}
-% \end{verbatim}
 
-It is because of quotients that we used equivalence relations to define the
-components of group structure. If we were to use the regular Leibniz equality,
-this would make it very difficult to say that a quotient group is another
-group. But by having the definition of a group depend upon an arbitrary
-equivalence relation, we enable our theory to state that a quotient group is
-simply a group with under a different equivalence. We didn't loose much as we
-could still rely upon Coq's setoid rewrite tactics. Setoids are types equipped
+The importance of quotients in commutative algebra motivates our use of equivalence relations to define the
+components of a group structure. 
+If one were to instead use the regular Leibniz equality,
+it would be very difficult to identify a quotient group with another
+group. 
+However, by  defining a group in terms of an arbitrary equivalence relation, we enable our theory to state that a quotient group is
+simply a group under a different equivalence. 
+Not much is lost,  as Coq's setoid rewrite tactics can still be called upon; 
+a setoid is a type equipped
 with an equivalence relation.
 
-Moving onwards, we then defined structures for rings, which have two binary
-operations: a commutative plus \(+\) and a non-commutative times \(\cdot\), and
-structures for commutative rings, where multiplication is commutative and has
-an identity. Here we define \emph{ideals} which are normal subgroups under
-addition and are absorbing with regards to multiplication, i.e. \(r a\) is in
-the ideal whenever \(a\) is in the ideal and \(r\) is any element of the ring.
+Moving onward, we formalized the structure of a ring, which has two binary
+operations:
+addition, which must be commutative, and multiplication, which need not be commutative in general.
+Next we defined the structure of a commutative ring, further requiring commutativity of multiplication, as well as a multiplicative identity. 
+At this point,, we define {ideals} of commutative rings as normal subgroups of the ring under
+addition that satisfy the absorption property under multiplication, i.e., \(r a\) is in
+the ideal for every element \(a\) of the ideal, and every element \(r\) of the commutative ring.
+
 Again, we defined quotient rings but found them unnecessary in the end. Note
@@
 
-\section{Formally Proving Nakayama's Lemma}
+\section{Formal Proof of Nakayama's Lemma}
 

### 2022-11-04 nakayama/images/algebraic-structures.tex
Added figure, abstract, and made some prose edits

\documentclass{standalone}

\usepackage{amsmath,amsthm,amsfonts,amssymb}

\usepackage{tikz}
\usetikzlibrary{positioning}

\tikzset{
    node/.style = {
       shape=rectangle, %rounded corners,
       align=center,
       minimum width = .4cm,
       minimum height = .4cm,
 %      fill = gray!30
 %      fill = cyan!40
 %      fill = blue!50!white!80
    },
    Snode/.style = {
       shape=rectangle, %rounded corners,
       align=center,
       minimum width = .4cm,
       minimum height = .4cm,
       fill = green!60!blue!70
    }
%    bad/.style = {
%       shape=rectangle, %rounded corners,
%       align=center,
%       minimum width = .4cm,
%       minimum height = .4cm,
%       fill = red!70
%    }
}
\begin{document}

\begin{tikzpicture}[->,>=stealth,shorten >=1pt,auto,node distance=1cm,semithick]
   \node[Snode] (Semigroup) {Semigroup};
   \node[Snode] (Monoid) [below = of Semigroup]{Monoid};
   \node[Snode] (Group) [below =of Monoid] {Group};
   \node[Snode] (AbelianGroup) [below =of Group] {Abelian Group};
   \node[Snode] (Subgroup) [left =1.3cm of AbelianGroup] {Subgroup};
   \node[Snode] (Ring) [below = of Subgroup] {Ring};
   \node[Snode] (CommutativeRing) [below =of Ring] {Commutative Ring};
   \node[Snode] (Ideal) [right =1.3 of CommutativeRing] {Ideal};
   \node[Snode] (Module) [right = 1.3cm of Ideal] {Module};
%   \node[node] (H1) [below = of G1] { };
%   \node[node] (H2) [below = of G2] { };
\path
(Semigroup) edge (Monoid)
(Monoid) edge (Group)
(Group) edge (AbelianGroup)
(Group) edge (Subgroup)
(AbelianGroup) edge (Ideal)
(AbelianGroup) edge (Ring)
(AbelianGroup) edge (Module)
(Ring) edge (CommutativeRing);
%(G1) edge (H1);
%(G2) edge (H2);
\end{tikzpicture}

\end{document}

### 2022-11-04 nakayama/paper.tex
Added figure, abstract, and made some prose edits

@@
 \title{ 
-Formal Commutative Algebra in Coq: \\ Nakayama's Lemma\thanks{Source code for this work is available on the following site: \url{https://github.com/ku-sldg/algebra}}
+Formalizing Commutative Algebra in Coq: \\ Nakayama's Lemma\thanks{Source code for this work is available on the following site: \url{https://github.com/ku-sldg/algebra}}
 }
@@
 \author{ 
-	Authors  
+	Andrew Cousino \\ {\tt acousino@ku.edu}
+	\and 
+	Emily E.\ Witt \\ {\tt witt@ku.edu}	
+	\and 
+	Perry Alexander \\ {\tt palexand@ku.edu}
+}	
 	%
-	\vspace{.2cm}		
-	\\ 
-%	
+
+\maketitle
+
+\vspace{-.3cm}
+
+{\large
+\begin{center}
 	Institute for Information Sciences \\
@@
 	Lawrence, KS 66045
+\end{center}
 }
-%\email{}
 
@@
 
-\maketitle
+\todo[inline]{To do:  Add to/alter author list, title, and/or abstract as necessary}
 
 \begin{abstract}
-\emily[inline]{Abstract here }
+We describe our formal proof of Nakayama's Lemma, a fundamental theorem in the mathematical field of commutative algebra.
+The statement and proof of this result involve several commutative-algebraic structures including commutative rings, ideals of these rings, and modules over them, and we also explain our process of formalizing these structures.
 \end{abstract}
@@
 \emph{Mathematical Components Library} 
-\cite{mathcomp}, we start from scratch.
+\cite{mathcomp}, we start from scratch. \todo{To do: Verify whether MathComp only formalized finite algebraic structures}
+ The theory, including the formalization of all algebraic structures, is approximately  $100$ kB and \textcolor{red}{??}\todo{To do:  Add number} lines of code.
 
@@
 Here, we give a brief description of the major mathematical structures from commutative algebra that are relevant to Nakayama's Lemma.
+
+\emily[inline]{Emily: It might be more consistent to require a ring to contain $1$ in general, instead of adding this to the axioms of a commutative ring.
+Perhaps we could do this in the code, and then here, without too much effort?
+}
 
@@
 
-\begin{enumerate}[leftmargin=2cm,topsep=0cm,itemsep=0cm]
+\begin{enumerate}[leftmargin=6cm,topsep=0cm,itemsep=0cm]
 \item  $r \cdot (u + v)  = r \cdot u + r \cdot v$
@@
 
-In order to state Nakayama's Lemma, we explain some notation:  If $I$ is an ideal of a commutative ring $R$ and 
+In order to state Nakayama's Lemma, we first explain some notation:  If $I$ is an ideal of a commutative ring $R$ and 
  $M$ is an $R$-module, then $IM$ is the set of elements of the form 
@@
 
-If an $R$-module $M$ consists of only one element, this element must be its additive identity $0$ as an abelian group under addition.  We use the notation $M=0$ in this case.
+If an $R$-module $M$ consists of only one element, this element must be its additive identity $0$ as an abelian group under addition.  The notation $M=0$ means that we are in this situtation.
 
@@
 
-There are several alternate statements of Nakayama's Lemma that remove the hypothesis that $R$ must be local.
+There are alternate statements of Nakayama's Lemma that remove the hypothesis that $R$ must be local.
 One can replace the unique maximal ideal with the Jacobson radical of the ring, which is the intersection of all maximal ideals.
@@
 
+We start by describing the process of formalization of algebraic structures, and with that in hand, then move on to the formal proof of Nakayama's lemma.
+
 \subsection{Our Algebraic Hierarchy}
+
+\begin{figure}[t]
+\caption{The hierarchy of our algebraic structures}
+\includegraphics[width=.4\textwidth]{algebraic-structures.pdf}
+\centering
+\todo[inline]{To do:  Check source code to verify whether the hierarchy figure should be altered (subgroups/other subobjects, quotients, finitely generated modules, etc.)}
+\end{figure}
 
@@
 
-\section{Formal Proof of Nakayama's Lemma}
+\subsection{Formal Proof of Nakayama's Lemma}
 

### 2022-11-05 nakayama/paper.tex
Changed en dashes to em.

@@
 % Mention an attempt with modules
-% Formalizing algebra => crypto
-% Interesting steps of the proof
 % ssreflect still looks to only deal with finite/discrete objects
@@
 The mathematical field of \emph{commutative algebra} stems from the study of solutions to polynomial equations.
-Research in the field now centers around \emph{commutative rings}--rings in which order does not affect multiplication, i.e., $x \cdot y = y \cdot x$ for any ring elements $x$ and $y$--and fundamental algebraic objects associated to them:  \emph{ideals} of these rings, and \emph{modules} over them.
+Research in the field now centers around \emph{commutative rings}---rings in which order does not affect multiplication, i.e., $x \cdot y = y \cdot x$ for any ring elements $x$ and $y$---and fundamental algebraic objects associated to them:  \emph{ideals} of these rings, and \emph{modules} over them.
 Commutative algebra has deep connections with other areas of theoretical mathematics, including number theory and algebraic geometry.
@@
 
-Other familiar examples of commutative rings include the integers modulo a fixed integer $n>0$, fields--commutative rings in which every nonzero element has a multiplicative inverse--such as the rings of rational numbers, real numbers, and complex numbers, and rings of polynomials in a variable $x$ with integer coefficients, or with coefficients in a field.
+Other familiar examples of commutative rings include the integers modulo a fixed integer $n>0$, fields---commutative rings in which every nonzero element has a multiplicative inverse---such as the rings of rational numbers, real numbers, and complex numbers, and rings of polynomials in a variable $x$ with integer coefficients, or with coefficients in a field.
 
@@
 \subsection{Formal Proof of Nakayama's Lemma}
-
 \begin{theorem}[Nakayama's lemma]

### 2022-11-05 nakayama/paper.tex
Edits

--- 2022-11-04 nakayama/paper.tex
@@
 
-\vspace{-.3cm}
+\vspace{-1cm}
 
@@
 Our goal is to newly formalize theoretical, rather than computational, commutative algebra in Coq. 
-We formally prove \emph{Nakayama's lemma} \cite{nakayama-1951, azumaya}, an essential result in the field. 
+We formally prove \emph{Nakayama's Lemma} \cite{nakayama-1951, azumaya}, an essential result in the field. 
 In doing so, we formalize algebraic structures that are fundamental to higher-level algebra, such as 
@@
 Less frequently referred to as the \emph{Krull-Azumaya theorem}\footnote{Hideyuki Matsumura explains in his text \emph{Commutative Algebra} \cite{matsumura}:  ``{This simple but important lemma is due to T.\ Nakayama, G.\ Azumaya
-and W.\ Krull. Priority is obscure, and although it is usually called the Lemma of Nakayama, late Prof.\  Nakayama did not like the name.''}}\,\cite{nagata}, Nakayama's lemma 
+and W.\ Krull. Priority is obscure, and although it is usually called the Lemma of Nakayama, late Prof.\  Nakayama did not like the name.''}}\,\cite{nagata}, Nakayama's Lemma 
 describes one way that a finitely generated module over an arbitrary commutative ring acts like a vector space over a field.  
-True to the convention that ``lemma'' often refers to a result serving as a stepping stone toward another goal, Nakayama's lemma is applied widely throughout the field, and the result is typically introduced in a first graduate course in commutative algebra \cite{atiyah-macdonald, matsumura, eisenbud}.
+True to the convention that ``lemma'' often refers to a result serving as a stepping stone toward another goal, Nakayama's Lemma is applied widely throughout the field, and the result is typically introduced in a first graduate course in commutative algebra \cite{atiyah-macdonald, matsumura, eisenbud}.
 
@@
 Hence in this special case, the hypothesis that  $M = \mathfrak{m} M$ is equivalent to the conclusion that $M=0$.
-Hence Nakayama's lemma describes one way that finitely generated modules over commutative local rings are similar to vector spaces.
+Hence Nakayama's Lemma describes one way that finitely generated modules over commutative local rings are similar to vector spaces.
 
 In general, the quotient $R/\mathfrak{m}$ of a local ring modulo its maximal ideal $\mathfrak{m}$ is a field, and the quotient of a module $M$ modulo the submodule $\mathfrak{m}M$ is an $R/\mathfrak{m}$-module, i.e., $M/\mathfrak{m}M$ is a vector space over $R/\mathfrak{m}$.
-Nakayama's lemma implies that if $M$ is finitely generated, then bases for $M/\mathfrak{m}M$ corresponds, via lifting, to minimal sets of generators of
+Nakayama's Lemma implies that if $M$ is finitely generated, then bases for $M/\mathfrak{m}M$ corresponds, via lifting, to minimal sets of generators of
 $M$.
@@
 
-We start by describing the process of formalization of algebraic structures, and with that in hand, then move on to the formal proof of Nakayama's lemma.
+We start by describing the process of formalization of algebraic structures, and with that in hand, then move on to the formal proof of Nakayama's Lemma.
 
@@
 \end{minted}
-The lines of the form, e.g.,  ``\verb|monoid_semigroup :> Semigroup equiv op;|'' simply coerce
+The lines such as  ``\verb|monoid_semigroup :> Semigroup equiv op;|'' simply coerce
 the monoid typeclass into a semigroup.
@@
 %While we found later on that we did not need quotients, 
-While in the end, our formal proof did not call upon quotients of algebraic structures, quotient rings and quotient modules are fundamental to commutative algebra, and one can use them to construct alternate proofs of Nakayama's lemma.
+While in the end, our formal proof did not call upon quotients of algebraic structures, quotient rings and quotient modules are fundamental to commutative algebra, and one can use them to construct alternate proofs of Nakayama's Lemma.
 It is worth pointing out that we have formalized quotients of algebraic objects  in Coq using typeclasses, which appear to work rather nicely.
@@
 \end{minted}
-% \end{verbatim}
+
 When these two relations coincide, then we can prove that this common equivalence
@@
 property are called \emph{normal subgroups}.
-% \begin{verbatim}
+
 \begin{minted}{coq}
@@
 Next we defined the structure of a commutative ring, further requiring commutativity of multiplication, as well as a multiplicative identity. 
-At this point,, we define {ideals} of commutative rings as normal subgroups of the ring under
+At this point, we formalized the notion of an ideal of a commutative rings as a normal subgroup  \emily{Emily:  Drew, this is what I read when I mentioned  ideals as normal subgroups.
+We should check if this should be rewritten}
+of the ring under
 addition that satisfy the absorption property under multiplication, i.e., \(r a\) is in
 the ideal for every element \(a\) of the ideal, and every element \(r\) of the commutative ring.
+We also defined quotient rings.
 
-Again, we defined quotient rings but found them unnecessary in the end. Note
+Note
 that should an ideal \(I\) contain a unit, an element \(x\) with a
@@
 absorbing property: given any element \(a\) of the ring, then \(a x^{-1}\) is
-also in the ring, and \(a x^{-1} x = a 1 = a\in I\). Maximal ideals were
-defined next. These are ideals that are proper subsets of the ring while having
-no larger ideal except for the ring itself. Below is the definition in Coq,
+also in the ring, and \(a x^{-1} x = a 1 = a\in I\). 
+\todo{To do: Check whether we need this paragraph}
+
+Next, we formally defined maximal ideals.
+Recall that a maximal ideal is a proper ideal that are maximal with respect to inclusion, i.e., if it is strictly contained in another ideal, this larger ideal must be the entire ring.
+Below is the definition in Coq,
 which uses \texttt{P} as the predicate for the ideal.
-% \begin{verbatim}
+
 \begin{minted}{coq}
@@
 \end{minted}
-% \end{verbatim}
+
 Almost by definition, maximal ideals can contain no units, otherwise they would
-fail to be a proper subset of the ring. We could then define a local ring,
-which is a ring with a single maximal ideal.
-% \begin{verbatim}
+fail to be a proper subset of the ring. \todo{To do:  Similar to above, do we need the first sentence here?}
+ Using the definition of a maximal ideal, we could then define a local ring, i.e., a commutative ring with a single maximal ideal.
+
  \begin{minted}{coq}
@@
 \end{minted}
-% \end{verbatim}
 
@@
 
-The next structure defined were modules over rings which generalize vector
-spaces over fields. We needed to capture the notion of linear combinations of
+The next structure defined was a module over a commutative ring, the commutative-algebraic generalization of the notion of a vector
+spaces over a fields,.  Here we needed to capture the notion of linear combinations of
 coefficients and module vectors. This was done by dependently typed vectors,
@@
 
-Next, we defined the product of an ideal \(I\) and a module \(M\), denoted as
-\(I M\), which is defined to be all linear combinations of vectors from \(M\)
-and coefficients from \(I\). This can be easily shown to be a submodule of
+Next, given an ideal \(I\) of a commutative ring $R$ and and an $R$-module \(M\), 
+we defined the submodule $IM$, the set consisting of all scalar combinations of elements of \(M\) whose coefficients are in  \(I\). This can be easily shown to be a submodule of
 \(M\). We represented this in Coq as a predicate over \(M\).
@@
 % \end{verbatim}
-The \verb|Forall P coeffs| ensures that every element of the coefficient list
-\texttt{coeffs} satisfies the predicate \texttt{P}. From here, we can move to
-stating Nakayama's lemma.
+The use of  ``\verb|Forall P coeffs|'' ensures that every element of the coefficient list
+\texttt{coeffs} satisfies the predicate \texttt{P}.
 
@@
 
-\begin{theorem}[Nakayama's lemma]
-  Let \(M\) be a finitely generated module over a local ring \(R\) with maximal
-  ideal \(\mathfrak{m}\). If \(\mathfrak{m} M = M\), then \(M = 0\), which is
-  to say that \(M\) is the zero module which consists of exactly one element,
-  that being the zero vector.
-\end{theorem}
+Finally, we turn to our formal proof of Nakayama's Lemma, our ultimate goal.
+
+\begin{nak*}
+Let $R$ be a commutative local ring, and let $\mathfrak{m}$ denote its maximal ideal. 
+Suppose that $M$ is a finitely generated $R$-module. 
+If $M = \mathfrak{m} M$, then $M = 0$, i.e., $M$ must be the $R$-module containing only one element, its identity as an additive abelian group. 
+\end{nak*}
 
@@
 
-For the proof of Nakayama's lemma, it too follows the standard, informal
+For the proof of Nakayama's Lemma, it too follows the standard, informal
 mathematical argument. Do induction on the number of vectors needed to generate

### 2022-11-05 nakayama/paper.tex
Minor edits to formalization section

@@
 The next structure defined was a module over a commutative ring, the commutative-algebraic generalization of the notion of a vector
-spaces over a fields,.  Here we needed to capture the notion of linear combinations of
+space over a field.
+
+Toward proving 
+Here we needed to formalize the notion of linear combinations of
 coefficients and module vectors. This was done by dependently typed vectors,
@@
 term ``vector'', we will use that term to refer to module vectors, and use the
-term ``list'' to mean length parameterized lists. As we don't use the simpler
+term ``list'' to mean length-parameterized lists. As we don't use the simpler
 kind of lists, this avoids any name collisions. A finitely generated module is

### 2022-11-07 nakayama/images/algebraic-structures.tex
Edits to scientific prose, comments added

@@
    \node[Snode] (Group) [below =of Monoid] {Group};
-   \node[Snode] (AbelianGroup) [below =of Group] {Abelian Group};
+   \node[Snode] (AbelianGroup) [below =of Group] {AbelianGroup};
    \node[Snode] (Subgroup) [left =1.3cm of AbelianGroup] {Subgroup};
-   \node[Snode] (Ring) [below = of Subgroup] {Ring};
-   \node[Snode] (CommutativeRing) [below =of Ring] {Commutative Ring};
-   \node[Snode] (Ideal) [right =1.3 of CommutativeRing] {Ideal};
-   \node[Snode] (Module) [right = 1.3cm of Ideal] {Module};
+
+   \node[Snode] (Ring) [below = of AbelianGroup] {Ring};
+   \node[Snode] (CommutativeRing) [below =of Ring] {CommRing};
+   \node[Snode] (Module) [right = 1.3cm of CommutativeRing] {Module};
+   \node[Snode] (Submodule) [left = 1.0 of CommutativeRing] {Submodule};
+   \node[Snode] (Ideal) [left =1.0 of Submodule] {Ideal};
    %   \node[node] (H1) [below = of G1] { };
@@
 (Group) edge (Subgroup)
-(AbelianGroup) edge (Ideal)
+(Subgroup) edge (Ideal)
 (AbelianGroup) edge (Ring)
 (AbelianGroup) edge (Module)
-(Ring) edge (CommutativeRing);
+(Ring) edge (CommutativeRing)
+(Subgroup) edge (Submodule);
 %(G1) edge (H1);

### 2022-11-07 nakayama/paper.tex
Fixed complaints from nag package
Edits to scientific prose, comments added

@@
 \author{ 
-	Andrew Cousino \\ {\tt acousino@ku.edu}
+	Andrew Cousino \\ {\ttfamily acousino@ku.edu}
 	\and 
-	Emily E.\ Witt \\ {\tt witt@ku.edu}	
+	Emily E.\ Witt \\ {\ttfamily witt@ku.edu}	
 	\and 
-	Perry Alexander \\ {\tt palexand@ku.edu}
+	Perry Alexander \\ {\ttfamily palexand@ku.edu}
 }	
@@
 \emily[inline]{Emily: It might be more consistent to require a ring to contain $1$ in general, instead of adding this to the axioms of a commutative ring.
-Perhaps we could do this in the code, and then here, without too much effort?
-}
+After thinking for a while, I think it is a good idea to make this change in the code, and then here to match.
+Drew, does this sound OK?}
 
@@
 
-\paragraph{Ideals.}
+\paragraph{Ideals of commutative rings.}
 The concept of an {ideal} of a ring can be thought of as an extension of the notion of an integer $x$ in the ring of integers $\mathbb{Z}$. 
@@
 an abelian group under addition,  
-which satisfies the following ``absorption'' property: Given any element $a$ of $I$, 
+which also satisfies the following ``absorption'' property: Given any element $a$ of $I$, 
 the product  $x \cdot a$ is again in $I$ for any ring element $x \in R$.
@@
 
+\paragraph{Local rings.}
 A commutative ring is \emph{local} if it has exactly one maximal ideal.  
@@
 
-\paragraph{A module over a commutative ring.}  Let  $R$ be a commutative ring. 
+\paragraph{Module over commutative rings.}  Let  $R$ be a commutative ring. 
 A \emph{module over $R$}, or \emph{$R$-module}, is an abelian group $M$ under a binary operation $+$, and a {scalar multiplication} $R \times M \to M$ denoted $\cdot$, satisfying the following compatibility properties for all $r, s \in R$ and $u, v \in M$.
 
-\begin{enumerate}[leftmargin=6cm,topsep=0cm,itemsep=0cm]
+\begin{enumerate}[leftmargin=5cm,topsep=0cm,itemsep=0cm]
 \item  $r \cdot (u + v)  = r \cdot u + r \cdot v$
@@
 \]
+The set $\{u_1, \ldots, u_n\}$ is called a \emph{generating set} for the $M$ as an $R$-module.
+
 When $R=F$ is a field and $M=V$ is a finite-dimensional vector space over $F$, one can choose $u_1, \ldots, u_n$ to be a basis for $V$, i.e., $n = \dim V$.
 In this case, the choice of scalar coefficients in the expression above for $w \in V$ is unique.
-When $R$ is not a field, modules can have more subtle properties, and such expression is typically not unique.
+When $R$ is not a field, however, such an expression is typically not unique.
 
@@
 
-There are alternate statements of Nakayama's Lemma that remove the hypothesis that $R$ must be local.
+We point out that there are alternate statements of Nakayama's Lemma that do not require the hypothesis that $R$ must be local.
 One can replace the unique maximal ideal with the Jacobson radical of the ring, which is the intersection of all maximal ideals.
@@
 
-We start by describing the process of formalization of algebraic structures, and with that in hand, then move on to the formal proof of Nakayama's Lemma.
+We start by describing our process of formalizing the required algebraic structures detailed in the previous section.  Then, with that in hand, we move on to the formal proof of Nakayama's Lemma.
 
@@
 \centering
-\todo[inline]{To do:  Check source code to verify whether the hierarchy figure should be altered (subgroups/other subobjects, quotients, finitely generated modules, etc.)}
+\todo[inline]{To do:  Check source code to verify whether the hierarchy figure should be altered (subobjects, quotients, finitely generated modules, local rings, etc.)}
 \end{figure}
 
-We started by defining a semigroup class, which declares a binary operation to
-be associative. From here, we build up through monoids, which introduce
-identities, to groups, which introduce inverses. Note the double equals ``$==$'' in
+Our foundation begins by defining a semigroup class, which declares a binary operation to
+be associative. 
+From here, we build up through monoids, which introduce
+identities, to groups, which introduce inverses.  
+Note the double equals ``$==$'' appearing in
 these definitions is notation for an arbitrary equivalence relation over the
@@
 
-The next structure defined was a module over a commutative ring, the commutative-algebraic generalization of the notion of a vector
+\emily[inline]{Emily:  Unfortunately, I think we need to update naming conventions since in mathematics ``vector'' is reserved for an element of a vector space over a field, rather than an element of an arbitrary module, causing confusion.
+Similar with ``basis,'' which is especially tricking since two different generating sets of a finitely generated module can have different sizes, but all bases of a vector space have the same cardinality, and an element of a module can typically be written as a scalar combination in multiple ways, while bases are linearly independent.
+I've proposed a rewrite of the blue paragraph above it.
+Drew, can you check it for accuracy with respect to the code?
+}
+\emily[inline]{
+We'll also need to update the code.  I think {\tt Vectors} should be something like {\tt ScalarCombinations}. 
+}
+
+Finally, we formalized the definition of a module over a commutative ring, the  commutative-algebraic generalization of the notion of a vector
 space over a field.
+Nakayama's Lemma is a statement about finitely generated modules, and hence we must formalize the notion of a scalar combination of a fixed finite collection of elements $u_1, \ldots, u_n$ of an $R$-module $M$, i.e., expressions of the form
+$r_1 u_1 + r_1 u_2 + \cdots + r_n u_n$, where each $r_i \in R$.
 
-Toward proving 
-Here we needed to formalize the notion of linear combinations of
+In our formalization of scalar combinations, 
+we use  ``list'' to mean length-parameterized lists; since we don't use the simpler
+kind of lists, there are no name collisions.
+In our code, \texttt{M} is the type of module elements, \texttt{R} is the type of ring
+elements,  act as coefficients, and \texttt{t A n} is a list whose elements
+are of type \texttt{A} and whose length is \texttt{n}.
+
+\textcolor{blue}{Here we needed to formalize the notion of linear combinations of
 coefficients and module vectors. This was done by dependently typed vectors,
@@
 are of type \texttt{A} and whose length is \texttt{n}.
-% \begin{verbatim}
+}
+
 \begin{minted}{coq}
@@
 
-\subsection{Formal Proof of Nakayama's Lemma}
+\subsection{Formally Proving of Nakayama's Lemma}
 

### 2022-11-07 nakayama/paper.tex
Updates to paper

@@
 Next we defined the structure of a commutative ring, further requiring commutativity of multiplication, as well as a multiplicative identity. 
-At this point, we formalized the notion of an ideal of a commutative rings as a normal subgroup  \emily{Emily:  Drew, this is what I read when I mentioned  ideals as normal subgroups.
-We should check if this should be rewritten}
+At this point, we formalized the notion of an ideal of a commutative ring, a subgroup 
 of the ring under
-addition that satisfy the absorption property under multiplication, i.e., \(r a\) is in
+addition that satisfies the absorption property under multiplication, i.e., \(r a\) is in
 the ideal for every element \(a\) of the ideal, and every element \(r\) of the commutative ring.
-We also defined quotient rings.
+We also used this to formalize the notion of a quotient ring $R/I$, where $I$ is an ideal of a commutative ring $R$.
 
-Note
-that should an ideal \(I\) contain a unit, an element \(x\) with a
-multiplicative inverse \(x^{-1}\), then \(I\) would be the entire ring by the
-absorbing property: given any element \(a\) of the ring, then \(a x^{-1}\) is
-also in the ring, and \(a x^{-1} x = a 1 = a\in I\). 
-\todo{To do: Check whether we need this paragraph}
+We proved that an ideal $I$ of a commutative rings that contains a unit, then it must be the entire ring.  A unit is 
+an element $x$ with a multiplicative inverse $x^{-1}$, i.e., the for which the product $x \cdot x^{-1}$ is the multiplicative identity $1$.
+By the absorption property, since $x \in I$, we have that $x \cdot x^{-1} = 1 \in I$, and so for every element $r$ of $R$, $r = r \cdot 1$ is also in $I$, i.e., $I=R$.
 
-Next, we formally defined maximal ideals.
-Recall that a maximal ideal is a proper ideal that are maximal with respect to inclusion, i.e., if it is strictly contained in another ideal, this larger ideal must be the entire ring.
+Next, we formally defined a maximal ideal, a proper ideal that are maximal with respect to inclusion, i.e., if it is strictly contained in another ideal, this larger ideal must be the entire ring. 
 Below is the definition in Coq,
@@
 
-Almost by definition, maximal ideals can contain no units, otherwise they would
-fail to be a proper subset of the ring. \todo{To do:  Similar to above, do we need the first sentence here?}
- Using the definition of a maximal ideal, we could then define a local ring, i.e., a commutative ring with a single maximal ideal.
+Using the definition of a maximal ideal, we then were able to define a local ring, i.e., a commutative ring with a single maximal ideal.
 
@@
 \end{minted}
+
+\emily[inline]{Emily:  I'm thinking this discussion could possibly be moved.  I'll think about it a bit more.}
 
@@
 
-Finally, we formalized the definition of a module over a commutative ring, the  commutative-algebraic generalization of the notion of a vector
+At this point we formalized the definition of a module over a commutative ring, the  commutative-algebraic generalization of the notion of a vector
 space over a field.
@@
 Next, given an ideal \(I\) of a commutative ring $R$ and and an $R$-module \(M\), 
-we defined the submodule $IM$, the set consisting of all scalar combinations of elements of \(M\) whose coefficients are in  \(I\). This can be easily shown to be a submodule of
-\(M\). We represented this in Coq as a predicate over \(M\).
-% \begin{verbatim}
+we defined the submodule $IM$, the set consisting of all scalar combinations of elements of \(M\) whose coefficients are in  \(I\). We represented this in Coq as a predicate over \(M\).
+
 \begin{minted}{coq}
@@
 \end{minted}
-% \end{verbatim}
+
 The use of  ``\verb|Forall P coeffs|'' ensures that every element of the coefficient list
@@
 \subsection{Formally Proving of Nakayama's Lemma}
+
+\emily[inline]{I think we need to include more code here!  There are a lot of pieces of formal proof that would be illustrative.}
 

### 2022-11-07 nakayama/paper.tex
Updates to first part of Formal Proof section

@@
 	\and 
-	Emily E.\ Witt \\ {\ttfamily witt@ku.edu}	
-	\and 
+	Emily E.\ Witt\thanks{Witt acknowledges support from NSF CAREER Award DMS-1945611 and the 2022-23 Ruth I.\, Michler Memorial Prize from the Association for Women in Mathematics.}
+ \\ {\ttfamily witt@ku.edu} \and 
 	Perry Alexander \\ {\ttfamily palexand@ku.edu}
@@
 
-%\thanks{Witt acknowledges support from NSF CAREER Award DMS-1945611 and the 2022-23 Ruth I.\, Michler Memorial Prize from the Association for Women in Mathematics.}
-
-\todo[inline]{To do:  Add to/alter author list, title, and/or abstract as necessary}
+\todo[inline]{To do:  Add to/alter author list, funding acknowledgments, title, and/or abstract as needed}
 
@@
 In doing so, we formalize algebraic structures that are fundamental to higher-level algebra, such as 
-\emph{local rings} and \emph{(finitely generated) modules over commutative rings}. 
+\emph{local rings} and \emph{modules over commutative rings}, and \emph{quotient rings and modules}.  
 Rather than build upon some of the basic objects from abstract algebra, such as groups and rings, that have been formalized in Coq, e.g., in the  
@@
 \cite{mathcomp}, we start from scratch. \todo{To do: Verify whether MathComp only formalized finite algebraic structures}
- The theory, including the formalization of all algebraic structures, is approximately  $100$ kB and \textcolor{red}{??}\todo{To do:  Add number} lines of code.
+ The theory, including the formalization of all algebraic structures, makes up approximately $100$ kB and 3300 lines of code.
 
@@
 
-\emily[inline]{Emily: It might be more consistent to require a ring to contain $1$ in general, instead of adding this to the axioms of a commutative ring.
+\emily[inline]{Emily: It would be more consistent to require a ring to contain $1$ in general, instead of adding this to the axioms of a commutative ring.
 After thinking for a while, I think it is a good idea to make this change in the code, and then here to match.
@@
 \centering
-\todo[inline]{To do:  Check source code to verify whether the hierarchy figure should be altered (subobjects, quotients, finitely generated modules, local rings, etc.)}
+\todo[inline]{To do:  Double check source code to verify whether the hierarchy figure should be altered (subobjects, quotients, finitely generated modules, local rings, etc.)}
 \end{figure}
@@
 
-We proved that an ideal $I$ of a commutative rings that contains a unit, then it must be the entire ring.  A unit is 
-an element $x$ with a multiplicative inverse $x^{-1}$, i.e., the for which the product $x \cdot x^{-1}$ is the multiplicative identity $1$.
-By the absorption property, since $x \in I$, we have that $x \cdot x^{-1} = 1 \in I$, and so for every element $r$ of $R$, $r = r \cdot 1$ is also in $I$, i.e., $I=R$.
-
+\emily[inline]{It would be nice to differentiate between our structures that are typeclasses (e.g., {\tt Ideal}), and other definitions (e.g., {\tt maximal ideal})}
 Next, we formally defined a maximal ideal, a proper ideal that are maximal with respect to inclusion, i.e., if it is strictly contained in another ideal, this larger ideal must be the entire ring. 
@@
 
-\emily[inline]{Emily:  I'm thinking this discussion could possibly be moved.  I'll think about it a bit more.}
-
-Here we had to include an axiom that in commutative ring, any non-unit \(x\) is
-contained in some maximal ideal. This was made into an axiom as the standard
-mathematical argument is a proof with potentially infinitely many steps. The
-standard argument goes as follows.
-\begin{quote}
-    Set \(I_{1}\coloneqq (x)\) to be the principal ideal for \(x\), i.e. the
-    ideal generated by the single element \(x\). If \(I_{1}\) is not maximal,
-    then there exists a strictly larger ideal \(I_{2}\), i.e.
-    \(x\in I_{1}\subsetneq I_{2}\). If \(I_{2}\) is not maximal, then there
-    exists another strictly larger ideal \(I_{3}\). Continue these arguments
-    infinitely many times if necessary in order to get an infinite chain of
-    ideals containing \(x\).
-    \[x\in I_{1}\subsetneq I_{2}\subsetneq I_{3}\subsetneq\cdots\subsetneq R\]
-    It is a simple matter to show that \(\bigcup_{k=1}^{\infty} I_{k}\) is also
-    an ideal containing in \(x\). So by Zorn's lemma, there exists a maximal
-    ideal in \(R\) which contains \(x\).
-\end{quote}
-Zorn's lemma is equivalent to the axiom of choice. So we had to add at least
-one axiom here in order to proceed. By adding the axiom that we did, not only
-will we encapsulate an infinite argument, but we will also avoid the need for
-the axiom of choice.
-
-Also, we used classical logic to prove that \(1 - x\) is a unit where \(x\) is
-a non-unit in any local ring. The proof used the rule \(\neg\neg P\rightarrow
-P\) in order to do a proof by contradiction.
-
-\emily[inline]{Emily:  Unfortunately, I think we need to update naming conventions since in mathematics ``vector'' is reserved for an element of a vector space over a field, rather than an element of an arbitrary module, causing confusion.
+\emily[inline]{Emily:  Unfortunately, I think we need to update naming conventions since in mathematics, ``vector'' is reserved for an element of a vector space over a field, rather than an element of an arbitrary module.
+So this could cause confusion.
 Similar with ``basis,'' which is especially tricking since two different generating sets of a finitely generated module can have different sizes, but all bases of a vector space have the same cardinality, and an element of a module can typically be written as a scalar combination in multiple ways, while bases are linearly independent.
-I've proposed a rewrite of the blue paragraph above it.
-Drew, can you check it for accuracy with respect to the code?
+I've proposed a rewrite of the blue paragraph right above it.
+Drew, can you double check it for accuracy with respect to the code?
 }
 \emily[inline]{
-We'll also need to update the code.  I think {\tt Vectors} should be something like {\tt ScalarCombinations}. 
+We'll also need to update the code.  I think {\tt vectors} should be something like {\tt scalar-combinations}, and {\tt basis} something like {\tt generating-set}. 
 }
@@
 
-\subsection{Formally Proving of Nakayama's Lemma}
+\subsection{Building the Formal Proof}
 
 \emily[inline]{I think we need to include more code here!  There are a lot of pieces of formal proof that would be illustrative.}
+
+Beyond formalizing the relevant structures from higher algebra, we also formally establish some basic theory. 
+For instance, a \emph{unit} of a commutative ring $R$ is an element $x \in R$ with a multiplicative inverse, i.e., an element $x^{-1} \in R$ for which $x \cdot x^{-1}$ is the multiplicative identity $1 \in R$.
+
+We formally proved that an ideal $I$ of a commutative ring $R$ that contains a unit $x$, then $I$ must be the trivial ideal, i.e., the entire ring.
+The informal logic is as follows:  By the absorption property, since $x \in I$, we have that $x \cdot x^{-1} = 1 \in I$.
+Hence for every element $r$ of $R$, $r = r \cdot 1$ is also in $I$, i.e., $I=R$.
+
+Every non-unit element of a commutative ring is contained in some maximal ideal. 
+This fact relies on the Axiom of Choice. 
+The following standard informal proof calls upon Zorn's lemma, which is equivalent to the Axiom of Choice, and says that given a partially ordered set $S$, if every chain in $S$ has an upper bound, then $S$ must have at least one maximal element.
+
+\begin{quote}
+    Set \(I_{1}\) to be the principal ideal generated by an element \(x\) of a commutative ring $R$, i.e. the
+    smallest ideal containing the element $x$, which consists of all $R$-multiples of $x$.
+
+    If \(I_{1}\) is not a maximal ideal,
+    then there exists a strictly larger proper ideal \(I_{2}\) of $R$, i.e.
+    $x\in I_{1}\subsetneq I_{2} \subsetneq R$.
+    Moreover, if  \(I_{2}\) is not maximal, then there
+    exists a strictly larger proper ideal $I_{3} \supsetneq I_2$.
+
+    Continuing this process, if it terminates at some step, we have found a maximal ideal, and if not, 
+    one obtains an infinite chain of
+    ideals containing \(x\).
+    \[x\in I_{1}\subsetneq I_{2}\subsetneq I_{3}\subsetneq\cdots\subsetneq R\]
+
+    It is straightfoward to show that \(\bigcup_{k=1}^{\infty} I_{k}\) satisfies the definition of an ideal of $R$, 
+    and this union certainly contains \(x\). So by Zorn's lemma, since every ascending chain of ideals containing $x$ 
+    with respect to inclusion has its union as an upper bound, there exists a maximal
+    ideal of \(R\) containing \(x\).
+\end{quote}
+
+This argument has potentially infinitely many steps, 
+and chose to avoid this issue by including an axiom that in 
+ any non-unit \(x\) is
+contained in some maximal ideal.
+
+\todo[inline]{Include some relevant code}
+
+We also used classical logic to prove that \(1 - x\) is a unit where \(x\) is
+a non-unit in any local ring. The proof used the rule \(\neg\neg P\rightarrow
+P\) in order to do a proof by contradiction.
+
+\todo[inline]{Include some relevant code}
 
@@
 We needed a lemma before moving on to prove the main theorem which states that
-for a finitely generated module \(M\) with a basis
-\(b_{1}, b_{2}, \dots, b_{n}\), any element \(x\in I M\) where \(I\) is an
-ideal can be written as a linear combination of the basis vectors with
-coefficients coming from \(I\). The proof of this lemma is straightforward and
-follows the standard, informal mathematical argument which inductively goes
+for a finitely generated $R$-module \(M\) with generating set\emily{Changed ``basis'' to ``generating set'' here}
+\(u_{1}, u_{2}, \dots, u_{n}\), any element \(x\in I M\), where \(I\) is an
+ideal of $R$, can be written as a linear combination of the basis vectors with
+coefficients coming from \(I\). \emily{I'm confused:  Isn't this how we defined $IM$?}
+ The proof of this lemma is straightforward and
+follows the standard, informal mathematical argument, which inductively goes
 through the vectors needed to generate \(x\) and shows that each vector can be

### 2022-11-07 nakayama/paper.tex
Updates to section describing formal proof

@@
 
-\emily[inline]{I think we need to include more code here!  There are a lot of pieces of formal proof that would be illustrative.}
-
 Beyond formalizing the relevant structures from higher algebra, we also formally establish some basic theory. 
@@
 for a finitely generated $R$-module \(M\) with generating set\emily{Changed ``basis'' to ``generating set'' here}
-\(u_{1}, u_{2}, \dots, u_{n}\), any element \(x\in I M\), where \(I\) is an
+\(b_{1}, b_{2}, \dots, b_{n}\), any element \(x\in I M\), where \(I\) is an
 ideal of $R$, can be written as a linear combination of the basis vectors with
-coefficients coming from \(I\). \emily{I'm confused:  Isn't this how we defined $IM$?}
+coefficients coming from \(I\). \emily{I'm confused:  Isn't this how we defined $IM$? Where are the $u$'s and $a$'s coming from?}
  The proof of this lemma is straightforward and
@@
 
-For the proof of Nakayama's Lemma, it too follows the standard, informal
-mathematical argument. Do induction on the number of vectors needed to generate
-the module \(M\). The base case where \(M\) is generated by 0 vectors is by
+\emily[inline]{I think we need to include more code here!  There are a lot of pieces of formal proof that would be illustrative.}
+
+Now we move to describe the skeleton of our formal proof of Nakayama's lemma. 
+We proceed by induction on the number of elements in a generating set for the finitely-generated module $M$. 
+. The base case where \(M\) is generated by 0 vectors is by
 definition true since an empty linear combination is conventionally taken to be
-the zero vector. The inductive case where \(M\) is generated by the vectors
+the zero vector. \emily{I think we should consider using one generator for the base case. }
+The inductive case where \(M\) is generated by the vectors
 \(b_{1}, \dots, b_{m}, b_{m+1}\). By assumption \(M = \mathfrak{m} M\) with

### 2022-11-08 nakayama/paper.tex
Cleaned up a few issues from nag package

@@
 \begin{document}
-
-% Mention an attempt with modules
-% ssreflect still looks to only deal with finite/discrete objects
-
 \title{ 
@@
 
-%\author{}
 \author{ 
@@
 }
-	%
 
@@
 
-\emily[inline]{It would be nice to differentiate between our structures that are typeclasses (e.g., {\tt Ideal}), and other definitions (e.g., {\tt maximal ideal})}
+\emily[inline]{It would be nice to differentiate between our structures that are typeclasses (e.g., {\ttfamily Ideal}), and other definitions (e.g., {\ttfamily maximal ideal})}
 Next, we formally defined a maximal ideal, a proper ideal that are maximal with respect to inclusion, i.e., if it is strictly contained in another ideal, this larger ideal must be the entire ring. 
@@
 \emily[inline]{
-We'll also need to update the code.  I think {\tt vectors} should be something like {\tt scalar-combinations}, and {\tt basis} something like {\tt generating-set}. 
+We'll also need to update the code.  I think {\ttfamily vectors} should be something like {\ttfamily scalar-combinations}, and {\ttfamily basis} something like {\ttfamily generating-set}. 
 }

### 2022-11-12 nakayama/paper.tex
Minor edits, fitted text to 80 columns

@@
 \title{ 
-Formalizing Commutative Algebra in Coq: \\ Nakayama's Lemma\thanks{Source code for this work is available on the following site: \url{https://github.com/ku-sldg/algebra}}
+Formalizing Commutative Algebra in Coq: \\
+Nakayama's Lemma\thanks{Source code for this work is available on the following
+site: \url{https://github.com/ku-sldg/algebra}}
 }
@@
 	\and 
-	Emily E.\ Witt\thanks{Witt acknowledges support from NSF CAREER Award DMS-1945611 and the 2022-23 Ruth I.\, Michler Memorial Prize from the Association for Women in Mathematics.}
- \\ {\ttfamily witt@ku.edu} \and 
+	Emily E.\ Witt\thanks{Witt acknowledges support from NSF CAREER Award
+    DMS-1945611 and the 2022-23 Ruth I.\, Michler Memorial Prize from the
+    Association for Women in Mathematics.} \\ {\ttfamily witt@ku.edu}
+  \and 
 	Perry Alexander \\ {\ttfamily palexand@ku.edu}
@@
 
-\todo[inline]{To do:  Add to/alter author list, funding acknowledgments, title, and/or abstract as needed}
+\todo[inline]{To do:  Add to/alter author list, funding acknowledgments, title,
+  and/or abstract as needed}
 
 \begin{abstract}
-We describe our formal proof of Nakayama's Lemma, a fundamental theorem in the mathematical field of commutative algebra.
-The statement and proof of this result involve several commutative-algebraic structures including commutative rings, ideals of these rings, and modules over them, and we also explain our process of formalizing these structures.
+  We describe our formal proof of Nakayama's Lemma, a fundamental theorem in
+  the mathematical field of commutative algebra. The statement and proof of
+  this result involve several commutative-algebraic structures including
+  commutative rings, ideals of these rings, and modules over them, and we also
+  explain our process of formalizing these structures.
 \end{abstract}
@@
 \section{Introduction}
+The mathematical field of \emph{commutative algebra} stems from the study of
+solutions to polynomial equations. Research in the field now centers around
+\emph{commutative rings}---rings in which order does not affect multiplication,
+i.e., $x \cdot y = y \cdot x$ for any ring elements $x$ and $y$---and
+fundamental algebraic objects associated to them:  \emph{ideals} of these
+rings, and \emph{modules} over them. Commutative algebra has deep connections
+with other areas of theoretical mathematics, including number theory and
+algebraic geometry.
 
-The mathematical field of \emph{commutative algebra} stems from the study of solutions to polynomial equations.
-Research in the field now centers around \emph{commutative rings}---rings in which order does not affect multiplication, i.e., $x \cdot y = y \cdot x$ for any ring elements $x$ and $y$---and fundamental algebraic objects associated to them:  \emph{ideals} of these rings, and \emph{modules} over them.
-Commutative algebra has deep connections with other areas of theoretical mathematics, including number theory and algebraic geometry.
+Commutative algebra also has broad applications to science and technology. For
+instance, it has been integral to advances in robotics \cite{cox-little-oshea},
+and has helped form our current understanding of the human genome
+\cite{genetic-algebra}. The commutative-algebraic notion of a Gr\"{o}bner
+basis, a special type of generating set for an ideal in a ring of polynomials,
+has become a fundamental computational tool in coding theory and cryptography
+(e.g., see  \cite{grobner-bases-cryptography}). A implementation of
+Buchberger's algorithm \cite{buchberger} for determining Gr\"obner bases of
+ideals in polynomial rings has been proved correct within the proof assistant
+Coq \cite{the_coq_development_team_2019_3476303,thery-buchberger}, and an
+integrated formal development of the algorithm in Coq has also been carried out
+\cite{persson2001integrated} (see also \cite{grobner-type-theory}).
 
-Commutative algebra also has broad applications to science and technology.
-For instance, it has been integral to advances in robotics \cite{cox-little-oshea}, and has helped form our current understanding of the human genome \cite{genetic-algebra}.
-The commutative-algebraic notion of a Gr\"obner basis, a special type of generating set for an ideal in a ring of polynomials, has become a fundamental computational tool in 
-coding theory and cryptography (e.g., see  \cite{grobner-bases-cryptography}).
-A implementation of Buchberger's algorithm \cite{buchberger} for determining 
-Gr\"obner bases of ideals in polynomial rings has been proved correct within the proof assistant Coq \cite{the_coq_development_team_2019_3476303,thery-buchberger}, and an integrated formal development of the algorithm in Coq has also been carried out \cite{persson2001integrated} (see also \cite{grobner-type-theory}).
+Our goal is to newly formalize theoretical, rather than computational,
+commutative algebra in Coq. We formally prove \emph{Nakayama's Lemma}
+\cite{nakayama-1951, azumaya}, an essential result in the field. In doing so,
+we formalize algebraic structures that are fundamental to higher-level algebra,
+such as \emph{local rings} and \emph{modules over commutative rings}, and
+\emph{quotient rings and modules}. Rather than build upon some of the basic
+objects from abstract algebra, such as groups and rings, that have been
+formalized in Coq, e.g., in the \emph{Mathematical Components Library}
+\cite{mathcomp}, we start from scratch.
+\todo{To do: Verify whether MathComp only formalized finite algebraic
+  structures. Drew is about as certain as he can be that this is the case.}
+The theory, including the formalization of all algebraic structures, makes up
+approximately $100$ kB and 3300 lines of code.
 
-Our goal is to newly formalize theoretical, rather than computational, commutative algebra in Coq. 
-We formally prove \emph{Nakayama's Lemma} \cite{nakayama-1951, azumaya}, an essential result in the field. 
-In doing so, we formalize algebraic structures that are fundamental to higher-level algebra, such as 
-\emph{local rings} and \emph{modules over commutative rings}, and \emph{quotient rings and modules}.  
-Rather than build upon some of the basic objects from abstract algebra, such as groups and rings, that have been formalized in Coq, e.g., in the  
-\emph{Mathematical Components Library} 
-\cite{mathcomp}, we start from scratch. \todo{To do: Verify whether MathComp only formalized finite algebraic structures}
- The theory, including the formalization of all algebraic structures, makes up approximately $100$ kB and 3300 lines of code.
+The notion of a module over a ring is an extension of the linear-algebraic
+notion of a vector space over a field, ubiquitous in mathematics and its
+applications. Less frequently referred to as the \emph{Krull-Azumaya theorem}
+\footnote{Hideyuki Matsumura explains in his text \emph{Commutative Algebra}
+  \cite{matsumura}: ``{This simple but important lemma is due to T.\ Nakayama,
+  G.\ Azumaya, and W.\ Krull. Priority is obscure, and although it is usually
+  called the Lemma of Nakayama, late Prof.\  Nakayama did not like the
+  name.''}}
+\,\cite{nagata}, Nakayama's Lemma describes one way that a finitely generated
+module over an arbitrary commutative ring acts like a vector space over a
+field. True to the convention that ``lemma'' often refers to a result serving
+as a stepping stone toward another goal, Nakayama's Lemma is applied widely
+throughout the field, and the result is typically introduced in a first
+graduate course in commutative algebra \cite{atiyah-macdonald, matsumura,
+eisenbud}.
 
-The notion of a module over a ring is an extension of the linear-algebraic notion of a vector space over a field, ubiquitous in mathematics and its applications. 
-Less frequently referred to as the \emph{Krull-Azumaya theorem}\footnote{Hideyuki Matsumura explains in his text \emph{Commutative Algebra} \cite{matsumura}:  ``{This simple but important lemma is due to T.\ Nakayama, G.\ Azumaya
-and W.\ Krull. Priority is obscure, and although it is usually called the Lemma of Nakayama, late Prof.\  Nakayama did not like the name.''}}\,\cite{nagata}, Nakayama's Lemma 
-describes one way that a finitely generated module over an arbitrary commutative ring acts like a vector space over a field.  
-True to the convention that ``lemma'' often refers to a result serving as a stepping stone toward another goal, Nakayama's Lemma is applied widely throughout the field, and the result is typically introduced in a first graduate course in commutative algebra \cite{atiyah-macdonald, matsumura, eisenbud}.
-
-%It is widely applied throughout algebra. %, true to .  However, Nakayama's lemma 
-%is also an important result in its own right, and can be thought of as one of the fundamental theorems of 
-%commutative algebra, not unlike the fundamental theorems of calculus describing the inverse relationship between derivatives and integrals or the fundamental theorem of arithmetic that makes precise the notion of unique factorization.
-%, or the fundamental theorem of algebra (or \emph{d'Alembert's theorem}) on the roots of complex polynomials.
+% It is widely applied throughout algebra. %, true to. However, Nakayama's lemma 
+% is also an important result in its own right, and can be thought of as one of
+% the fundamental theorems of 
+% commutative algebra, not unlike the fundamental theorems of calculus
+% describing the inverse relationship between derivatives and integrals or the
+% fundamental theorem of arithmetic that makes precise the notion of unique
+% factorization.
+% , or the fundamental theorem of algebra (or \emph{d'Alembert's theorem}) on
+% the roots of complex polynomials.
 
 \section{Mathematical Basis and Motivation}
+\subsection{The Fundamental Algebraic Structures}
+Here, we give a brief description of the major mathematical structures from
+commutative algebra that are relevant to Nakayama's Lemma.
 
-\subsection{The Fundamental Algebraic Structures}
-
-Here, we give a brief description of the major mathematical structures from commutative algebra that are relevant to Nakayama's Lemma.
-
-\emily[inline]{Emily: It would be more consistent to require a ring to contain $1$ in general, instead of adding this to the axioms of a commutative ring.
-After thinking for a while, I think it is a good idea to make this change in the code, and then here to match.
-Drew, does this sound OK?}
+\emily[inline]{Emily: It would be more consistent to require a ring to contain
+$1$ in general, instead of adding this to the axioms of a commutative ring.
+After thinking for a while, I think it is a good idea to make this change in
+the code, and then here to match. Drew, does this sound OK?}
 
 \paragraph{Commutative rings.}
-In abstract algebra, the quintessential example of a commutative ring is the set of integers
+In abstract algebra, the quintessential example of a commutative ring is the
+set of integers
 \[\mathbb{Z} = \{ \ldots, -3, -2, -1, 0, 1, 2, 3, \ldots \}.\]
@@
 
-Adding two integers produces another, and the associative and commutative laws hold for addition.
-The integers form an \emph{abelian group} under addition since $0 \in \mathbb{Z}$ is the \emph{additive identity} in the sense that adding zero has no effect on any integer, and given any integer $n$, the integer $-n$ is its \emph{additive inverse} in the sense that the sum of $n$ and $-n$ is the additive identity $0$.
+Adding two integers produces another, and the associative and commutative laws
+hold for addition. The integers form an \emph{abelian group} under addition
+since $0 \in \mathbb{Z}$ is the \emph{additive identity} in the sense that
+adding zero has no effect on any integer, and given any integer $n$, the
+integer $-n$ is its \emph{additive inverse} in the sense that the sum of $n$
+and $-n$ is the additive identity $0$.
 
-The set of integers also forms a \emph{ring} due to its properties of multiplication.  
-It is closed under this binary operation, which satisfies associativity, and the distributive law governing the compatibility of addition and multiplication holds. 
-Even more, the integers form a \emph{commutative ring} 
- since $n \cdot m = m \cdot n$ for all integers $n$ and $m$.  We require commutative rings to contain a \emph{multiplicative identity}, and $1 \in \mathbb{Z}$ is such an element since 
-   $n \in \mathbb{Z}$ one has $n \cdot 1 = 1 \cdot n = n$.
+The set of integers also forms a \emph{ring} due to its properties of
+multiplication. It is closed under this binary operation, which satisfies
+associativity, and the distributive law governing the compatibility of addition
+and multiplication holds. Even more, the integers form a
+\emph{commutative ring} since $n \cdot m = m \cdot n$ for all integers $n$ and
+$m$. We require commutative rings to contain a \emph{multiplicative identity},
+and $1 \in \mathbb{Z}$ is such an element since $n \in \mathbb{Z}$ one has
+$n \cdot 1 = 1 \cdot n = n$.
 
-In general, a commutative ring is a set $R$ with two binary operations, which we call \emph{addition} and \emph{mutiplication}, typically denoted $\cdot$ and $+$, respectively.
-As motivated by the properties of the ring of integers, addition, $R$ must be an abelian group, multiplication must be associative, $R$ must have a multiplicative identity, and the distributive law must hold, i.e., for all $r, s, t \in R$, $(r+s)\cdot t = r \cdot t + s \cdot t$ and $r \cdot (s+t) = r \cdot s + r \cdot t$.
+In general, a commutative ring is a set $R$ with two binary operations, which
+we call \emph{addition} and \emph{mutiplication}, typically denoted $\cdot$ and
+$+$, respectively. As motivated by the properties of the ring of integers,
+addition, $R$ must be an abelian group, multiplication must be associative, $R$
+must have a multiplicative identity, and the distributive law must hold, i.e.,
+for all $r, s, t \in R$, $(r+s)\cdot t = r \cdot t + s \cdot t$ and
+$r \cdot (s+t) = r \cdot s + r \cdot t$.
 
-Other familiar examples of commutative rings include the integers modulo a fixed integer $n>0$, fields---commutative rings in which every nonzero element has a multiplicative inverse---such as the rings of rational numbers, real numbers, and complex numbers, and rings of polynomials in a variable $x$ with integer coefficients, or with coefficients in a field.
+Other familiar examples of commutative rings include the integers modulo a
+fixed integer $n>0$, fields---commutative rings in which every nonzero element
+has a multiplicative inverse---such as the rings of rational numbers, real
+numbers, and complex numbers, and rings of polynomials in a variable $x$ with
+integer coefficients, or with coefficients in a field.
 
 \paragraph{Ideals of commutative rings.}
-The concept of an {ideal} of a ring can be thought of as an extension of the notion of an integer $x$ in the ring of integers $\mathbb{Z}$. 
-An \emph{ideal} of commutative ring $R$ is a subset $I$ of $R$ that is itself 
-an abelian group under addition,  
-which also satisfies the following ``absorption'' property: Given any element $a$ of $I$, 
-the product  $x \cdot a$ is again in $I$ for any ring element $x \in R$.
+The concept of an {ideal} of a ring can be thought of as an extension of the
+notion of an integer $x$ in the ring of integers $\mathbb{Z}$. An \emph{ideal}
+of commutative ring $R$ is a subset $I$ of $R$ that is itself an abelian group
+under addition, which also satisfies the following ``absorption'' property:
+Given any element $a$ of $I$, the product  $x \cdot a$ is again in $I$ for any
+ring element $x \in R$.
 
-One can verify that given any integer $n$, the set $n\mathbb{Z}$ of its multiples forms an ideal of $\mathbb{Z}$.
-For instance, $2 \mathbb{Z}$ consists of all even numbers, and is an abelian group under addition: the sum of two even numbers is even, the additive identity $0$ is even, and the negative of an even number is even.
-Moreover, the absorption property holds since the product of any integer and an even number is again even. 
-In fact, every ideal of the ring of integers has this form $n\mathbb{Z}$ for some integer $n$, though ideals in general commutative rings can have more complicated properties.
+One can verify that given any integer $n$, the set $n\mathbb{Z}$ of its
+multiples forms an ideal of $\mathbb{Z}$. For instance, $2 \mathbb{Z}$
+consists of all even numbers, and is an abelian group under addition: the sum
+of two even numbers is even, the additive identity $0$ is even, and the
+negative of an even number is even. Moreover, the absorption property holds
+since the product of any integer and an even number is again even. In fact,
+every ideal of the ring of integers has this form $n\mathbb{Z}$ for some
+integer $n$, though ideals in general commutative rings can have more
+complicated properties.
 
-Since every integer $n$ can be written as $1 \cdot n$, the ideal $1 \mathbb{Z}$ is the entire ring $\mathbb{Z}$.
-One can see that given a commutative ring $R$ itself satisfies the axioms required to be an ideal of $R$.
-We call an ideal $I$ of $R$ \emph{proper} if it is strictly contained in $R$.
-The \emph{zero ideal} consisting solely of its additive identity is a proper ideal of any commutative ring.
+Since every integer $n$ can be written as $1 \cdot n$, the ideal $1 \mathbb{Z}$
+is the entire ring $\mathbb{Z}$. One can see that given a commutative ring
+$R$ itself satisfies the axioms required to be an ideal of $R$. We call an
+ideal $I$ of $R$ \emph{proper} if it is strictly contained in $R$. The
+\emph{zero ideal} consisting solely of its additive identity is a proper ideal
+of any commutative ring.
 
-A \emph{maximal ideal} of a commutative ring is a proper ideal that is maximal with respect to inclusion, i.e., no other proper ideal strictly contains it. 
-Returning to our example of the ring of integers, $6 \mathbb{Z} \subsetneq 2 \mathbb{Z}$ since every multiple of $6$ is even, 
-so $6 \mathbb{Z}$ is not a maximal ideal of $\mathbb{Z}$. 
-However, no proper ideal $I$ contains $2 \mathbb{Z}$:  If $2 \mathbb{Z}\subsetneq I \subsetneq \mathbb{Z}$, then $I$  would necessarily contain an odd number $n$.
-Writing $n=2k+1$ for some integer $k$, we notice that since $-2k$ is in $2\mathbb{Z}$, it is also an element of the larger set $I$, and since $I$ is an abelian group under addition, $(2k+1) + (-2k) = 1$ is also in the ideal $I$.
-However, in this case, every integer $n = n \cdot 1$ is in $I$ by absorption, so $I = \mathbb{Z}$ is not a proper ideal, a contradiction.
+A \emph{maximal ideal} of a commutative ring is a proper ideal that is maximal
+with respect to inclusion, i.e., no other proper ideal strictly contains it. 
+Returning to our example of the ring of integers,
+$6 \mathbb{Z} \subsetneq 2 \mathbb{Z}$ since every multiple of $6$ is even, so
+$6 \mathbb{Z}$ is not a maximal ideal of $\mathbb{Z}$. However, no proper ideal
+$I$ contains $2 \mathbb{Z}$: If $2\mathbb{Z}\subsetneq I\subsetneq \mathbb{Z}$,
+then $I$  would necessarily contain an odd number $n$. Writing $n=2k+1$ for
+some integer $k$, we notice that since $-2k$ is in $2\mathbb{Z}$, it is also an
+element of the larger set $I$, and since $I$ is an abelian group under
+addition, $(2k+1) + (-2k) = 1$ is also in the ideal $I$. However, in this case,
+every integer $n = n \cdot 1$ is in $I$ by absorption, so $I = \mathbb{Z}$ is
+not a proper ideal, a contradiction.
 
-In fact, $3 \mathbb{Z}$ is the only other maximal ideal of $\mathbb{Z}$ containing $6 \mathbb{Z}$, and in general, the prime ideals in the ring of integers besides the zero ideal are those of the form $p \mathbb{Z}$, where $p$ a prime number.
+In fact, $3 \mathbb{Z}$ is the only other maximal ideal of $\mathbb{Z}$
+containing $6 \mathbb{Z}$, and in general, the prime ideals in the ring of
+integers besides the zero ideal are those of the form $p \mathbb{Z}$, where $p$
+a prime number.
 
@@
 A commutative ring is \emph{local} if it has exactly one maximal ideal. 
-Every field is local since the only proper ideal of a field is the zero ideal, though by our observations above, the ring of integers is not local. 
-However, the set of all rational numbers that can be written with an odd denominator does form a subring of all rational numbers, and its unique maximal ideal consists of the elements with even numerator; in fact, this ring is the so-called \emph{localization} of $\mathbb{Z}$ at the maximal ideal $2 \mathbb{Z}$.
-The ring of integers modulo $n>1$ is local if and only if $n$ is a power of a prime number $p$,  in which case the unique maximal ideal consists of all multiples of $p$.
+Every field is local since the only proper ideal of a field is the zero ideal,
+though by our observations above, the ring of integers is not local. 
+However, the set of all rational numbers that can be written with an odd
+denominator does form a subring of all rational numbers, and its unique maximal
+ideal consists of the elements with even numerator; in fact, this ring is the
+so-called \emph{localization} of $\mathbb{Z}$ at the maximal ideal
+$2\mathbb{Z}$. The ring of integers modulo $n>1$ is local if and only if $n$ is
+a power of a prime number $p$, in which case the unique maximal ideal consists
+of all multiples of $p$.
 
-The ring of polynomials over a field $F$ in a variable $x$ is not local; in fact, given any irreducible polynomial $f(x)$, the set of its multiples is a maximal ideal of the polynomial ring $F[x]$.
-On the other hand, the set of all formal power series  in $x$ over $F$ is a local ring; its maximal ideal consists of the power series with no constant term.
+The ring of polynomials over a field $F$ in a variable $x$ is not local; in
+fact, given any irreducible polynomial $f(x)$, the set of its multiples is a
+maximal ideal of the polynomial ring $F[x]$. On the other hand, the set of all
+formal power series  in $x$ over $F$ is a local ring; its maximal ideal
+consists of the power series with no constant term.
 
-%Hence the ring of integers is not local, but 
-%the ring of integers modulo an integer $n>1$,  often denoted $\mathbb{Z}/n\mathbb{Z}$ or $\mathbb{Z}_n$, are local
+% Hence the ring of integers is not local, but the ring of integers modulo an
+% integer $n>1$, often denoted $\mathbb{Z}/n\mathbb{Z}$ or $\mathbb{Z}_n$, are
+% local
 
-\paragraph{Module over commutative rings.}  Let  $R$ be a commutative ring. 
-A \emph{module over $R$}, or \emph{$R$-module}, is an abelian group $M$ under a binary operation $+$, and a {scalar multiplication} $R \times M \to M$ denoted $\cdot$, satisfying the following compatibility properties for all $r, s \in R$ and $u, v \in M$.
+\paragraph{Module over commutative rings.}
+Let  $R$ be a commutative ring. 
+A \emph{module over $R$}, or \emph{$R$-module}, is an abelian group $M$ under a
+binary operation $+$, and a {scalar multiplication} $R \times M \to M$ denoted
+$\cdot$, satisfying the following compatibility properties for all $r, s \in R$
+and $u, v \in M$.
 
@@
 
-From this definition, one can see that a module over a field $F$ is precisely an $F$-vector space, so the notion of a module over an arbitrary commutative ring extends that of a vector space over a field.
-Finitely generated vector spaces form the foundation for matrix algebra, and the extension of this notion to module theory is needed to state Nakayama's Lemma.
-We call an $R$-module $M$ \emph{finitely generated} if there exist a fixed finite number of elements $u_1, \ldots, u_n$ of $M$ with the following property:  Given any  $w \in M$, there exist $r_1, \ldots, r_n \in R$ for which
-\[
-w = r_1 u_1 + r_1 u_2 + \cdots + r_n u_n.
-\]
-The set $\{u_1, \ldots, u_n\}$ is called a \emph{generating set} for the $M$ as an $R$-module.
+From this definition, one can see that a module over a field $F$ is precisely
+an $F$-vector space, so the notion of a module over an arbitrary commutative
+ring extends that of a vector space over a field. Finitely generated vector
+spaces form the foundation for matrix algebra, and the extension of this notion
+to module theory is needed to state Nakayama's Lemma. We call an $R$-module
+$M$ \emph{finitely generated} if there exist a fixed finite number of elements
+$u_1, \ldots, u_n$ of $M$ with the following property:  Given any  $w \in M$,
+there exist $r_1, \ldots, r_n \in R$ for which  
+\[w = r_1 u_1 + r_1 u_2 + \cdots + r_n u_n\text{.}\]
+The set $\{u_1, \ldots, u_n\}$ is called a \emph{generating set} for the $M$ as
+an $R$-module.
 
-When $R=F$ is a field and $M=V$ is a finite-dimensional vector space over $F$, one can choose $u_1, \ldots, u_n$ to be a basis for $V$, i.e., $n = \dim V$.
-In this case, the choice of scalar coefficients in the expression above for $w \in V$ is unique.
-When $R$ is not a field, however, such an expression is typically not unique.
+When $R = F$ is a field and $M = V$ is a finite-dimensional vector space over
+$F$, one can choose $u_1, \ldots, u_n$ to be a basis for $V$, i.e.,
+$n = \dim V$. In this case, the choice of scalar coefficients in the expression
+above for $w \in V$ is unique. When $R$ is not a field, however, such an
+expression is typically not unique.
 
@@
 
-In order to state Nakayama's Lemma, we first explain some notation:  If $I$ is an ideal of a commutative ring $R$ and 
- $M$ is an $R$-module, then $IM$ is the set of elements of the form 
-	$a_1 u_1 + a_2 u_2 + \cdots + a_k u_k$, where, for some positive integer $k$, $a_1, \ldots, a_k \in I$ and $u_1, \ldots, u_k \in M$.  
-Notice that due to the absorption property of ideals, $IM$ is an $R$-module contained in $M$.
+In order to state Nakayama's Lemma, we first explain some notation:  If $I$ is
+an ideal of a commutative ring $R$ and $M$ is an $R$-module, then $IM$ is the
+set of elements of the form $a_1 u_1 + a_2 u_2 + \cdots + a_k u_k$, where, for
+some positive integer $k$, $a_1, \ldots, a_k \in I$ and
+$u_1, \ldots, u_k \in M$. Notice that due to the absorption property of ideals,
+$I M$ is an $R$-module contained in $M$.
 
-If an $R$-module $M$ consists of only one element, this element must be its additive identity $0$ as an abelian group under addition.  The notation $M=0$ means that we are in this situtation.
+If an $R$-module $M$ consists of only one element, this element must be its
+additive identity $0$ as an abelian group under addition. The notation $M=0$
+means that we are in this situation.
 
 \begin{nak*}
-Let $R$ be a commutative local ring, and let $\mathfrak{m}$ denote its unique maximal ideal. 
-If $M$ is a finitely generated $R$-module and $M = \mathfrak{m} M$, then $M = 0$. 
+Let $R$ be a commutative local ring, and let $\mathfrak{m}$ denote its unique
+maximal ideal. If $M$ is a finitely generated $R$-module and
+$M = \mathfrak{m} M$, then $M = 0$. 
 \end{nak*}
 
-When $R=F$ is a field, its unique maximal ideal is the zero ideal, and given any vector space $M=V$ over $F$, the only linear combination of vectors with coefficients in the zero ideal is the zero vector.
-Hence in this special case, the hypothesis that  $M = \mathfrak{m} M$ is equivalent to the conclusion that $M=0$.
-Hence Nakayama's Lemma describes one way that finitely generated modules over commutative local rings are similar to vector spaces.
+When $R=F$ is a field, its unique maximal ideal is the zero ideal, and given
+any vector space $M=V$ over $F$, the only linear combination of vectors with
+coefficients in the zero ideal is the zero vector. Hence in this special case,
+the hypothesis that  $M = \mathfrak{m} M$ is equivalent to the conclusion that
+$M=0$. Hence Nakayama's Lemma describes one way that finitely generated modules
+over commutative local rings are similar to vector spaces.
 
-In general, the quotient $R/\mathfrak{m}$ of a local ring modulo its maximal ideal $\mathfrak{m}$ is a field, and the quotient of a module $M$ modulo the submodule $\mathfrak{m}M$ is an $R/\mathfrak{m}$-module, i.e., $M/\mathfrak{m}M$ is a vector space over $R/\mathfrak{m}$.
-Nakayama's Lemma implies that if $M$ is finitely generated, then bases for $M/\mathfrak{m}M$ corresponds, via lifting, to minimal sets of generators of
-$M$.
+In general, the quotient $R/\mathfrak{m}$ of a local ring modulo its maximal
+ideal $\mathfrak{m}$ is a field, and the quotient of a module $M$ modulo the
+submodule $\mathfrak{m}M$ is an $R/\mathfrak{m}$-module, i.e.,
+$M/\mathfrak{m}M$ is a vector space over $R/\mathfrak{m}$. Nakayama's Lemma
+implies that if $M$ is finitely generated, then bases for $M/\mathfrak{m}M$
+corresponds, via lifting, to minimal sets of generators of $M$.
 
-We point out that there are alternate statements of Nakayama's Lemma that do not require the hypothesis that $R$ must be local.
-One can replace the unique maximal ideal with the Jacobson radical of the ring, which is the intersection of all maximal ideals.
-Alternatively, $I$ is an arbitrary proper ideal of a commutative ring $R$ and
- $M$ is a finitely generated $R$-module for which $M=I M$, then this ensures the existence of a ring element $r$ congruent to $1$ modulo $I$ such that $rM = 0$, i.e., $r u = 0$ for every $u \in M$.
+We point out that there are alternate statements of Nakayama's Lemma that do
+not require the hypothesis that $R$ must be local. One can replace the unique
+maximal ideal with the Jacobson radical of the ring, which is the intersection
+of all maximal ideals. Alternatively, $I$ is an arbitrary proper ideal of a
+commutative ring $R$ and $M$ is a finitely generated $R$-module for which
+$M=I M$, then this ensures the existence of a ring element $r$ congruent to
+$1$ modulo $I$ such that $r M = 0$, i.e., $r u = 0$ for every $u \in M$.
 
 \section{Formalization}
-
-We start by describing our process of formalizing the required algebraic structures detailed in the previous section.  Then, with that in hand, we move on to the formal proof of Nakayama's Lemma.
+We start by describing our process of formalizing the required algebraic
+structures detailed in the previous section. Then, with that in hand, we move
+on to the formal proof of Nakayama's Lemma.
 
 \subsection{Our Algebraic Hierarchy}
-
 \begin{figure}[t]
@@
   \centering
-\todo[inline]{To do:  Double check source code to verify whether the hierarchy figure should be altered (subobjects, quotients, finitely generated modules, local rings, etc.)}
 \end{figure}
+\todo[inline]{To do:  Double check source code to verify whether the hierarchy
+figure should be altered (subobjects, quotients, finitely generated modules,
+local rings, etc.) It looks good to Drew.}
 
-Our foundation begins by defining a semigroup class, which declares a binary operation to
-be associative. 
-From here, we build up through monoids, which introduce
-identities, to groups, which introduce inverses.  
-Note the double equals ``$==$'' appearing in
-these definitions is notation for an arbitrary equivalence relation over the
-group's carrier set, which acts as equality.
+Our foundation begins by defining a semigroup class, which declares a binary
+operation to be associative. From here, we build up through monoids, which
+introduce identities, to groups, which introduce inverses. Note the double
+equals ``$==$'' appearing in these definitions is notation for an arbitrary
+equivalence relation over the group's carrier set, which acts as equality.
 
@@
 \end{minted}
-The lines such as  ``\verb|monoid_semigroup :> Semigroup equiv op;|'' simply coerce
+Lines such as  ``\verb|monoid_semigroup :> Semigroup equiv op;|'' simply coerce
 the monoid typeclass into a semigroup.
@@
 %While we found later on that we did not need quotients, 
-While in the end, our formal proof did not call upon quotients of algebraic structures, quotient rings and quotient modules are fundamental to commutative algebra, and one can use them to construct alternate proofs of Nakayama's Lemma.
-It is worth pointing out that we have formalized quotients of algebraic objects  in Coq using typeclasses, which appear to work rather nicely.
+While in the end, our formal proof did not call upon quotients of algebraic
+structures, quotient rings and quotient modules are fundamental to commutative
+algebra, and one can use them to construct alternate proofs of Nakayama's
+Lemma. It is worth pointing out that we have formalized quotients of algebraic
+objects in Coq using typeclasses, which appear to work rather nicely.
 
-An algebraic quotient is, roughly, the set of equivalence classes of an algebraic structure with respect to an equivalence relation on its elements, for which the set of equivalence classes inherit the same kind of algebraic structure.
-For example, consider the quotient of a group modulo a subgroup, i.e. a subset of elements of the group that it itself a group under the group operations. 
-Under equivalence relation on the group, every element of the subgroup must be in the same equivalence class as the identity.  
-With \texttt{P} the predicate for the subgroup, there are two ways to
-make an equivalence relation from this description.
+An algebraic quotient is, roughly, the set of equivalence classes of an
+algebraic structure with respect to an equivalence relation on its elements,
+for which the set of equivalence classes inherit the same kind of algebraic
+structure. For example, consider the quotient of a group modulo a subgroup,
+i.e., a subset of elements of the group that it itself a group under the group
+operations. Under equivalence relation on the group, every element of the
+subgroup must be in the same equivalence class as the identity. With \texttt{P}
+the predicate for the subgroup, there are two ways to make an equivalence
+relation from this description.
 
@@
 
-When these two relations coincide, then we can prove that this common equivalence
-relation actually preserves the group structure. Subgroups which have this
-property are called \emph{normal subgroups}.
+When these two relations coincide, then we can prove that this common
+equivalence relation actually preserves the group structure. Subgroups which
+have this property are called \emph{normal subgroups}.
 
@@
 
-The importance of quotients in commutative algebra motivates our use of equivalence relations to define the
-components of a group structure. 
-If one were to instead use the regular Leibniz equality,
-it would be very difficult to identify a quotient group with another
-group. 
-However, by  defining a group in terms of an arbitrary equivalence relation, we enable our theory to state that a quotient group is
-simply a group under a different equivalence. 
-Not much is lost,  as Coq's setoid rewrite tactics can still be called upon; 
-a setoid is a type equipped
-with an equivalence relation.
+The importance of quotients in commutative algebra motivates our use of
+equivalence relations to define the components of a group structure. If one
+were to instead use the regular Leibniz equality, it would be very difficult to
+identify a quotient group with another group. However, by  defining a group in
+terms of an arbitrary equivalence relation, we enable our theory to state that
+a quotient group is simply a group under a different equivalence. Not much is
+lost, as Coq's setoid rewrite tactics can still be called upon; a setoid is a
+type equipped with an equivalence relation.
 
 Moving onward, we formalized the structure of a ring, which has two binary
-operations:
-addition, which must be commutative, and multiplication, which need not be commutative in general.
-Next we defined the structure of a commutative ring, further requiring commutativity of multiplication, as well as a multiplicative identity. 
-At this point, we formalized the notion of an ideal of a commutative ring, a subgroup 
-of the ring under
-addition that satisfies the absorption property under multiplication, i.e., \(r a\) is in
-the ideal for every element \(a\) of the ideal, and every element \(r\) of the commutative ring.
-We also used this to formalize the notion of a quotient ring $R/I$, where $I$ is an ideal of a commutative ring $R$.
+operations: addition, which must be commutative, and multiplication, which need
+not be commutative in general. Next we defined the structure of a commutative
+ring, further requiring commutativity of multiplication, as well as a
+multiplicative identity. At this point, we formalized the notion of an ideal of
+a commutative ring, a subgroup of the ring under addition that satisfies the
+absorption property under multiplication, i.e., \(r a\) is in the ideal for
+every element \(a\) of the ideal, and every element \(r\) of the commutative
+ring. We also used this to formalize the notion of a quotient ring $R/I$, where
+$I$ is an ideal of a commutative ring $R$.
 
-\emily[inline]{It would be nice to differentiate between our structures that are typeclasses (e.g., {\ttfamily Ideal}), and other definitions (e.g., {\ttfamily maximal ideal})}
-Next, we formally defined a maximal ideal, a proper ideal that are maximal with respect to inclusion, i.e., if it is strictly contained in another ideal, this larger ideal must be the entire ring. 
-Below is the definition in Coq,
-which uses \texttt{P} as the predicate for the ideal.
+\emily[inline]{It would be nice to differentiate between our structures that
+  are typeclasses (e.g., {\ttfamily Ideal}), and other definitions (e.g.,
+  {\ttfamily maximal ideal})}
+
+Next, we formally defined a maximal ideal, a proper ideal that are maximal with
+respect to inclusion, i.e., if it is strictly contained in another ideal, this
+larger ideal must be the entire ring. Below is the definition in Coq, which
+uses \texttt{P} as the predicate for the ideal.
 
@@
 
-Using the definition of a maximal ideal, we then were able to define a local ring, i.e., a commutative ring with a single maximal ideal.
+Using the definition of a maximal ideal, we then were able to define a local
+ring, i.e., a commutative ring with a single maximal ideal.
 
@@
 
-\emily[inline]{Emily:  Unfortunately, I think we need to update naming conventions since in mathematics, ``vector'' is reserved for an element of a vector space over a field, rather than an element of an arbitrary module.
-So this could cause confusion.
-Similar with ``basis,'' which is especially tricking since two different generating sets of a finitely generated module can have different sizes, but all bases of a vector space have the same cardinality, and an element of a module can typically be written as a scalar combination in multiple ways, while bases are linearly independent.
-I've proposed a rewrite of the blue paragraph right above it.
-Drew, can you double check it for accuracy with respect to the code?
+\emily[inline]{Emily:  Unfortunately, I think we need to update naming
+  conventions since in mathematics, ``vector'' is reserved for an element of a
+  vector space over a field, rather than an element of an arbitrary module.  So
+  this could cause confusion.  Similar with ``basis,'' which is especially
+  tricking since two different generating sets of a finitely generated module
+  can have different sizes, but all bases of a vector space have the same
+  cardinality, and an element of a module can typically be written as a scalar
+  combination in multiple ways, while bases are linearly independent.  I've
+  proposed a rewrite of the blue paragraph right above it.  Drew, can you
+  double check it for accuracy with respect to the code? 
 }
-\emily[inline]{
-We'll also need to update the code.  I think {\ttfamily vectors} should be something like {\ttfamily scalar-combinations}, and {\ttfamily basis} something like {\ttfamily generating-set}. 
+\emily[inline]{We'll also need to update the code.  I think {\ttfamily vectors}
+  should be something like {\ttfamily scalar-combinations}, and
+  {\ttfamily basis} something like {\ttfamily generating-set}. 
 }
 
-At this point we formalized the definition of a module over a commutative ring, the  commutative-algebraic generalization of the notion of a vector
-space over a field.
-Nakayama's Lemma is a statement about finitely generated modules, and hence we must formalize the notion of a scalar combination of a fixed finite collection of elements $u_1, \ldots, u_n$ of an $R$-module $M$, i.e., expressions of the form
-$r_1 u_1 + r_1 u_2 + \cdots + r_n u_n$, where each $r_i \in R$.
+At this point we formalized the definition of a module over a commutative ring,
+the commutative-algebraic generalization of the notion of a vector space over a
+field. Nakayama's Lemma is a statement about finitely generated modules, and
+hence we must formalize the notion of a scalar combination of a fixed finite
+collection of elements $u_1, \ldots, u_n$ of an $R$-module $M$, i.e.,
+expressions of the form $r_1 u_1 + r_1 u_2 + \cdots + r_n u_n$, where each
+$r_i \in R$.
 
-In our formalization of scalar combinations, 
-we use  ``list'' to mean length-parameterized lists; since we don't use the simpler
-kind of lists, there are no name collisions.
-In our code, \texttt{M} is the type of module elements, \texttt{R} is the type of ring
-elements,  act as coefficients, and \texttt{t A n} is a list whose elements
-are of type \texttt{A} and whose length is \texttt{n}.
+In our formalization of scalar combinations, we use  ``list'' to mean
+length-parameterized lists; since we don't use the simpler kind of lists, there
+are no name collisions. In our code, \texttt{M} is the type of module elements,
+\texttt{R} is the type of ring elements, act as coefficients, and
+\texttt{t A n} is a list whose elements are of type \texttt{A} and whose length
+is \texttt{n}.
 
-\textcolor{blue}{Here we needed to formalize the notion of linear combinations of
-coefficients and module vectors. This was done by dependently typed vectors,
-i.e. lists parameterized by their length. Because there is an overload of the
-term ``vector'', we will use that term to refer to module vectors, and use the
-term ``list'' to mean length-parameterized lists. As we don't use the simpler
-kind of lists, this avoids any name collisions. A finitely generated module is
-like the vector space \(\mathbf{R}^{n}\) in that there are finitely many
-vectors which can generate all other vectors, for \(\mathbf{R}^{n}\) one such
-collection of generators are \(\mathbf{e}_{1} = \begin{pmatrix} 1 & 0 & 0 &
-  \cdots & 0\end{pmatrix}^{T}\), \(\mathbf{e}_{2} = \begin{pmatrix} 0 & 1 & 0 &
-  \cdots & 0\end{pmatrix}^{T}\), \textellipsis, \(\mathbf{e}_{n} =
-  \begin{pmatrix} 0 & 0 & 0 & \cdots & 1\end{pmatrix}^{T}\). In our code,
-\texttt{M} is the type of module elements, \texttt{R} is the type of ring
-elements which act as coefficients, and \texttt{t A n} is a list whose elements
-are of type \texttt{A} and whose length is \texttt{n}.
+\textcolor{blue}{Here we needed to formalize the notion of linear combinations
+  of coefficients and module vectors. This was done by dependently typed
+  vectors, i.e., lists parameterized by their length. Because there is an
+  overload of the term ``vector'', we will use that term to refer to module
+  vectors, and use the term ``list'' to mean length-parameterized lists. As we
+  don't use the simpler kind of lists, this avoids any name collisions. A
+  finitely generated module is like the vector space \(\mathbf{R}^{n}\) in that
+  there are finitely many vectors which can generate all other vectors, for
+  \(\mathbf{R}^{n}\) one such collection of generators are
+  \(\mathbf{e}_{1} = \begin{pmatrix} 1 & 0 & 0 & \cdots & 0\end{pmatrix}^{T}\),
+  \(\mathbf{e}_{2} = \begin{pmatrix} 0 & 1 & 0 & \cdots & 0\end{pmatrix}^{T}\),
+  \textellipsis,
+  \(\mathbf{e}_{n} = \begin{pmatrix} 0 & 0 & 0 & \cdots & 1\end{pmatrix}^{T}\).
+  In our code, \texttt{M} is the type of module elements, \texttt{R} is the
+  type of ring elements which act as coefficients, and \texttt{t A n} is a list
+  whose elements are of type \texttt{A} and whose length is \texttt{n}.
 }
@@
 
-Next, given an ideal \(I\) of a commutative ring $R$ and and an $R$-module \(M\), 
-we defined the submodule $IM$, the set consisting of all scalar combinations of elements of \(M\) whose coefficients are in  \(I\). We represented this in Coq as a predicate over \(M\).
+Next, given an ideal \(I\) of a commutative ring $R$ and and an $R$-module
+\(M\),  we defined the submodule $IM$, the set consisting of all scalar
+combinations of elements of \(M\) whose coefficients are in  \(I\). We
+represented this in Coq as a predicate over \(M\).
 
@@
 
-The use of  ``\verb|Forall P coeffs|'' ensures that every element of the coefficient list
-\texttt{coeffs} satisfies the predicate \texttt{P}.
+The use of  ``\verb|Forall P coeffs|'' ensures that every element of the
+coefficient list \texttt{coeffs} satisfies the predicate \texttt{P}.
 
 \subsection{Building the Formal Proof}
+Beyond formalizing the relevant structures from higher algebra, we also
+formally establish some basic theory. For instance, a \emph{unit} of a
+commutative ring $R$ is an element $x \in R$ with a multiplicative inverse,
+i.e., an element $x^{-1} \in R$ for which $x \cdot x^{-1}$ is the
+multiplicative identity $1 \in R$.
 
-Beyond formalizing the relevant structures from higher algebra, we also formally establish some basic theory. 
-For instance, a \emph{unit} of a commutative ring $R$ is an element $x \in R$ with a multiplicative inverse, i.e., an element $x^{-1} \in R$ for which $x \cdot x^{-1}$ is the multiplicative identity $1 \in R$.
+We formally proved that an ideal $I$ of a commutative ring $R$ that contains a
+unit $x$, then $I$ must be the trivial ideal, i.e., the entire ring.  The
+informal logic is as follows:  By the absorption property, since $x \in I$, we
+have that $x \cdot x^{-1} = 1 \in I$.  Hence for every element $r$ of $R$,
+$r = r \cdot 1$ is also in $I$, i.e., $I=R$.
 
-We formally proved that an ideal $I$ of a commutative ring $R$ that contains a unit $x$, then $I$ must be the trivial ideal, i.e., the entire ring.
-The informal logic is as follows:  By the absorption property, since $x \in I$, we have that $x \cdot x^{-1} = 1 \in I$.
-Hence for every element $r$ of $R$, $r = r \cdot 1$ is also in $I$, i.e., $I=R$.
-
-Every non-unit element of a commutative ring is contained in some maximal ideal. 
-This fact relies on the Axiom of Choice. 
-The following standard informal proof calls upon Zorn's lemma, which is equivalent to the Axiom of Choice, and says that given a partially ordered set $S$, if every chain in $S$ has an upper bound, then $S$ must have at least one maximal element.
+Every non-unit element of a commutative ring is contained in some maximal
+ideal. This fact relies on the Axiom of Choice. The following standard informal
+proof calls upon Zorn's lemma, which is equivalent to the Axiom of Choice, and
+says that given a partially ordered set $S$, if every chain in $S$ has an upper
+bound, then $S$ must have at least one maximal element.
 
 \begin{quote}
-    Set \(I_{1}\) to be the principal ideal generated by an element \(x\) of a commutative ring $R$, i.e. the
-    smallest ideal containing the element $x$, which consists of all $R$-multiples of $x$.
+    Set \(I_{1}\) to be the principal ideal generated by an element \(x\) of a
+    commutative ring $R$, i.e. the smallest ideal containing the element $x$,
+    which consists of all $R$-multiples of $x$.
 
-    If \(I_{1}\) is not a maximal ideal,
-    then there exists a strictly larger proper ideal \(I_{2}\) of $R$, i.e.
-    $x\in I_{1}\subsetneq I_{2} \subsetneq R$.
-    Moreover, if  \(I_{2}\) is not maximal, then there
-    exists a strictly larger proper ideal $I_{3} \supsetneq I_2$.
+    If \(I_{1}\) is not a maximal ideal, then there exists a strictly larger
+    proper ideal \(I_{2}\) of $R$, i.e.,
+    $x\in I_{1}\subsetneq I_{2} \subsetneq R$. Moreover, if  \(I_{2}\) is not
+    maximal, then there exists a strictly larger proper ideal
+    $I_{3} \supsetneq I_2$.
 
-    Continuing this process, if it terminates at some step, we have found a maximal ideal, and if not, 
-    one obtains an infinite chain of
-    ideals containing \(x\).
+    Continuing this process, if it terminates at some step, we have found a
+    maximal ideal, and if not, one obtains an infinite chain of ideals
+    containing \(x\).
     \[x\in I_{1}\subsetneq I_{2}\subsetneq I_{3}\subsetneq\cdots\subsetneq R\]
 
-    It is straightfoward to show that \(\bigcup_{k=1}^{\infty} I_{k}\) satisfies the definition of an ideal of $R$, 
-    and this union certainly contains \(x\). So by Zorn's lemma, since every ascending chain of ideals containing $x$ 
-    with respect to inclusion has its union as an upper bound, there exists a maximal
-    ideal of \(R\) containing \(x\).
+    It is straight-forward to show that \(\bigcup_{k=1}^{\infty} I_{k}\)
+    satisfies the definition of an ideal of $R$, and this union certainly
+    contains \(x\). So by Zorn's lemma, since every ascending chain of ideals
+    containing $x$ with respect to inclusion has its union as an upper bound,
+    there exists a maximal ideal of \(R\) containing \(x\).
 \end{quote}
 
-This argument has potentially infinitely many steps, 
-and chose to avoid this issue by including an axiom that in 
- any non-unit \(x\) is
-contained in some maximal ideal.
+This argument has potentially infinitely many steps, and chose to avoid this
+issue by including an axiom that in any non-unit \(x\) is contained in some
+maximal ideal.
 
@@
 \begin{nak*}
-Let $R$ be a commutative local ring, and let $\mathfrak{m}$ denote its maximal ideal. 
-Suppose that $M$ is a finitely generated $R$-module. 
-If $M = \mathfrak{m} M$, then $M = 0$, i.e., $M$ must be the $R$-module containing only one element, its identity as an additive abelian group. 
+Let $R$ be a commutative local ring, and let $\mathfrak{m}$ denote its maximal
+ideal. Suppose that $M$ is a finitely generated $R$-module. If
+$M = \mathfrak{m} M$, then $M = 0$, i.e., $M$ must be the $R$-module containing
+only one element, its identity as an additive abelian group. 
 \end{nak*}
@@
 We needed a lemma before moving on to prove the main theorem which states that
-for a finitely generated $R$-module \(M\) with generating set\emily{Changed ``basis'' to ``generating set'' here}
+for a finitely generated $R$-module \(M\) with generating set
 \(b_{1}, b_{2}, \dots, b_{n}\), any element \(x\in I M\), where \(I\) is an
-ideal of $R$, can be written as a linear combination of the basis vectors with
-coefficients coming from \(I\). \emily{I'm confused:  Isn't this how we defined $IM$? Where are the $u$'s and $a$'s coming from?}
- The proof of this lemma is straightforward and
-follows the standard, informal mathematical argument, which inductively goes
-through the vectors needed to generate \(x\) and shows that each vector can be
-rewritten in terms of the basis vectors times elements of the ideal \(I\) as
-follows.
+ideal of $R$, can be written as a linear combination of the generating set with
+coefficients coming from \(I\).
+\emily{I'm confused:  Isn't this how we defined $I M$? Where are the $u$'s and
+  $a$'s coming from?}
+In other words, given \(x\in I M\), there is by definition a linear combination
+between elements \(u_{1}, \dots, u_{m}\in I\), and elements
+\(a_{1},\dots, a_{m}\in M\), we need a lemma that states \(x\) can be written
+as a linear combination between elements of \(I\) and the generating set
+\(b_{1},\dots, b_{n}\in M\). This follows the informal mathematical argument
+going inductively through the elements needed to generate \(x\) and shows that
+each vector can be rewritten in terms of the generating set times coefficients
+from the ideal \(I\) as follows.
 \begin{align*}
@@
 u_{m} r_{m j}\) are all elements of \(I\). Thus, \(x\) can be written as a
-linear combination of the basis vectors with the coefficients coming from
+linear combination of the generating set with the coefficients coming from
 \(I\).
 
-\emily[inline]{I think we need to include more code here!  There are a lot of pieces of formal proof that would be illustrative.}
+\emily[inline]{I think we need to include more code here!  There are a lot of
+  pieces of formal proof that would be illustrative.}
 
 Now we move to describe the skeleton of our formal proof of Nakayama's lemma.
-We proceed by induction on the number of elements in a generating set for the finitely-generated module $M$. 
-. The base case where \(M\) is generated by 0 vectors is by
-definition true since an empty linear combination is conventionally taken to be
-the zero vector. \emily{I think we should consider using one generator for the base case. }
+We proceed by induction on the number of elements in a generating set for the
+finitely-generated module $M$. The base case where \(M\) is generated by 0
+elements is by definition true since an empty linear combination is
+conventionally taken to be the zero vector.
+\emily{I think we should consider using one generator for the base case.}
 The inductive case where \(M\) is generated by the vectors
-\(b_{1}, \dots, b_{m}, b_{m+1}\). By assumption \(M = \mathfrak{m} M\) with
-\(b_{1}\in M\). Then \(b_{1}\in\mathfrak{m} M\) meaning that by our lemma,
+\(b_{1}, \dots, b_{m}, b_{m+1}\). By assumption \(M = \mathfrak{m} M\).
+With \(b_{1}\in M\), then \(b_{1}\in\mathfrak{m} M\) meaning that by our lemma,
 there exists a linear combination for \(b_{1}\), say
@@
     & = v_{1} u_{2} b_{2} + \cdots + v_{1} u_{m+1} b_{m+1} \\
-  1 b_{1} & = \\
+  1 b_{1} & = v_{1} u_{2} b_{2} + \cdots + v_{1} u_{m+1} b_{m+1} \\
   b_{1} & = v_{1} u_{2} b_{2} + \cdots + v_{1} u_{m+1} b_{m+1} \\

### 2022-11-13 nakayama/paper.tex
Minor updates based on issues being addressed

@@
 
-\emily[inline]{Emily: It would be more consistent to require a ring to contain
-$1$ in general, instead of adding this to the axioms of a commutative ring.
-After thinking for a while, I think it is a good idea to make this change in
-the code, and then here to match. Drew, does this sound OK?}
-
 \paragraph{Commutative rings.}
@@
 associativity, and the distributive law governing the compatibility of addition
-and multiplication holds. Even more, the integers form a
-\emph{commutative ring} since $n \cdot m = m \cdot n$ for all integers $n$ and
-$m$. We require commutative rings to contain a \emph{multiplicative identity},
+and multiplication holds.  We require rings to contain a \emph{multiplicative identity},
 and $1 \in \mathbb{Z}$ is such an element since $n \in \mathbb{Z}$ one has
 $n \cdot 1 = 1 \cdot n = n$. 
+Even more, the integers form a
+\emph{commutative ring} since $n \cdot m = m \cdot n$ for all integers $n$ and
+$m$.
 
@@
 
-\subsection{Our Algebraic Hierarchy}
+\subsection{Building our Algebraic Hierarchy}
 \begin{figure}[t]
@@
 \end{figure}
-\todo[inline]{To do:  Double check source code to verify whether the hierarchy
-figure should be altered (subobjects, quotients, finitely generated modules,
-local rings, etc.) It looks good to Drew.}
 
@@
 
-Moving onward, we formalized the structure of a ring, which has two binary
+Moving onward, rings are the next step in our algebraic heirarchy; a ring has two binary
 operations: addition, which must be commutative, and multiplication, which need
-not be commutative in general. Next we defined the structure of a commutative
+not be commutative in general. Next, we formalized the definition of a commutative
 ring, further requiring commutativity of multiplication, as well as a
@@
 $I$ is an ideal of a commutative ring $R$.
-
-\emily[inline]{It would be nice to differentiate between our structures that
-  are typeclasses (e.g., {\ttfamily Ideal}), and other definitions (e.g.,
-  {\ttfamily maximal ideal})}
 
@@
 
-\emily[inline]{Emily:  Unfortunately, I think we need to update naming
-  conventions since in mathematics, ``vector'' is reserved for an element of a
-  vector space over a field, rather than an element of an arbitrary module.  So
-  this could cause confusion.  Similar with ``basis,'' which is especially
-  tricking since two different generating sets of a finitely generated module
-  can have different sizes, but all bases of a vector space have the same
-  cardinality, and an element of a module can typically be written as a scalar
-  combination in multiple ways, while bases are linearly independent.  I've
-  proposed a rewrite of the blue paragraph right above it.  Drew, can you
-  double check it for accuracy with respect to the code? 
-}
-\emily[inline]{We'll also need to update the code.  I think {\ttfamily vectors}
-  should be something like {\ttfamily scalar-combinations}, and
-  {\ttfamily basis} something like {\ttfamily generating-set}. 
-}
+%\emily[inline]{Emily:  Unfortunately, I think we need to update naming
+%  conventions since in mathematics, ``vector'' is reserved for an element of a
+%  vector space over a field, rather than an element of an arbitrary module.  So
+%  this could cause confusion.  Similar with ``basis,'' which is especially
+%  tricking since two different generating sets of a finitely generated module
+%  can have different sizes, but all bases of a vector space have the same
+%  cardinality, and an element of a module can typically be written as a scalar
+%  combination in multiple ways, while bases are linearly independent.  I've
+%  proposed a rewrite of the blue paragraph right above it.  Drew, can you
+%  double check it for accuracy with respect to the code? 
+%}
+%\emily[inline]{We'll also need to update the code.  I think {\ttfamily vectors}
+%  should be something like {\ttfamily scalar-combinations}, and
+%  {\ttfamily basis} something like {\ttfamily generating-set}. 
+%}
 
@@
 is \texttt{n}.
-
-\textcolor{blue}{Here we needed to formalize the notion of linear combinations
-  of coefficients and module vectors. This was done by dependently typed
-  vectors, i.e., lists parameterized by their length. Because there is an
-  overload of the term ``vector'', we will use that term to refer to module
-  vectors, and use the term ``list'' to mean length-parameterized lists. As we
-  don't use the simpler kind of lists, this avoids any name collisions. A
-  finitely generated module is like the vector space \(\mathbf{R}^{n}\) in that
-  there are finitely many vectors which can generate all other vectors, for
-  \(\mathbf{R}^{n}\) one such collection of generators are
-  \(\mathbf{e}_{1} = \begin{pmatrix} 1 & 0 & 0 & \cdots & 0\end{pmatrix}^{T}\),
-  \(\mathbf{e}_{2} = \begin{pmatrix} 0 & 1 & 0 & \cdots & 0\end{pmatrix}^{T}\),
-  \textellipsis,
-  \(\mathbf{e}_{n} = \begin{pmatrix} 0 & 0 & 0 & \cdots & 1\end{pmatrix}^{T}\).
-  In our code, \texttt{M} is the type of module elements, \texttt{R} is the
-  type of ring elements which act as coefficients, and \texttt{t A n} is a list
-  whose elements are of type \texttt{A} and whose length is \texttt{n}.
-}
 
@@
 
-\subsection{Building the Formal Proof}
+\subsection{Constructing the Formal Proof}
 Beyond formalizing the relevant structures from higher algebra, we also

### 2022-11-17 nakayama/paper.tex
Refined descriptions of formal proof, added more code excerpts

@@
 The concept of an {ideal} of a ring can be thought of as an extension of the
-notion of an integer $x$ in the ring of integers $\mathbb{Z}$. An \emph{ideal}
+notion of an integer $n$ in the ring of integers $\mathbb{Z}$. An \emph{ideal}
 of commutative ring $R$ is a subset $I$ of $R$ that is itself an abelian group
@@
 
+A \emph{prime ideal} of a commutative ring is a proper ideal $I$ with the following property:  
+If the product $x \cdot y$ of ring elements $x$ and $y$ is in $I$, then $x \in I$ or $y \in I$.
+The naming convention is motivated by the ring of integers, where the prime ideals are precisely those 
+of the form $p\mathbb{Z}$, where $p$ is a prime number, along with the zero ideal.
+
 A \emph{maximal ideal} of a commutative ring is a proper ideal that is maximal
@@
 containing $6 \mathbb{Z}$, and in general, the prime ideals in the ring of
-integers besides the zero ideal are those of the form $p \mathbb{Z}$, where $p$
+integers besides the zero ideal are  $p \mathbb{Z}$, where $p$
 a prime number. 
+It is not a coincidence that every maximal ideal of the ring of integers is also a prime 
+ideal; the analogous statement can be proved in arbitrary commutative rings.
 
@@
 
-\paragraph{Module over commutative rings.}
+\paragraph{Modules over commutative rings.}
 Let  $R$ be a commutative ring. 
@@
 binary operation $+$, and a {scalar multiplication} $R \times M \to M$ denoted
-$\cdot$, satisfying the following compatibility properties for all $r, s \in R$
+$\cdot$, satisfying the following properties for all $r, s \in R$
 and $u, v \in M$.
@@
 
-\subsection{Building our Algebraic Hierarchy}
+\subsection{Our Algebraic Hierarchy}
 \begin{figure}[t]
@@
 %While we found later on that we did not need quotients, 
-While in the end, our formal proof did not call upon quotients of algebraic
+While in the end, our formal proof
+does not require calling upon 
+ quotients of algebraic
 structures, quotient rings and quotient modules are fundamental to commutative
@@
 equivalence relations to define the components of a group structure. If one
-were to instead use the regular Leibniz equality, it would be very difficult to
-identify a quotient group with another group. However, by  defining a group in
-terms of an arbitrary equivalence relation, we enable our theory to state that
-a quotient group is simply a group under a different equivalence. Not much is
-lost, as Coq's setoid rewrite tactics can still be called upon; a setoid is a
-type equipped with an equivalence relation.
+were to instead use the regular Leibniz equality, it would be difficult to
+identify a quotient group and another group. However, by  defining a group in
+terms of an arbitrary equivalence relation, in our theory a quotient group is 
+simply defined as a group, but under an equivalence relation that is not the usual 
+equality. 
+Not much is lost due to Coq's rewrite tactics for setoids--types equipped with an equivalence relation--
+can still be called upon.
 
-Moving onward, rings are the next step in our algebraic heirarchy; a ring has two binary
+Moving onward, rings form the next step in our algebraic hierarchy; a ring has two binary
 operations: addition, which must be commutative, and multiplication, which need
@@
 
-Next, we formally defined a maximal ideal, a proper ideal that are maximal with
-respect to inclusion, i.e., if it is strictly contained in another ideal, this
-larger ideal must be the entire ring. Below is the definition in Coq, which
+Next, we formalized the definition of a  prime ideal, and then 
+moved on to do the same for the notion of a maximal ideal, a proper ideal 
+that is maximal with respect to inclusion. Below is the definition in Coq, which
 uses \texttt{P} as the predicate for the ideal.
@@
 
-Using the definition of a maximal ideal, we then were able to define a local
+We then were able to take advantage of the definition of a maximal ideal
+to formally define a local
 ring, i.e., a commutative ring with a single maximal ideal.
@@
 field. Nakayama's Lemma is a statement about finitely generated modules, and
-hence we must formalize the notion of a scalar combination of a fixed finite
-collection of elements $u_1, \ldots, u_n$ of an $R$-module $M$, i.e.,
+hence we must formalize the notion of a scalar combination of a finite
+collection of elements, $u_1, \ldots, u_n$, of an $R$-module $M$, i.e.,
 expressions of the form $r_1 u_1 + r_1 u_2 + \cdots + r_n u_n$, where each
@@
 i.e., an element $x^{-1} \in R$ for which $x \cdot x^{-1}$ is the
-multiplicative identity $1 \in R$.
+multiplicative identity $1 \in R$.  In fact, it $x$ is a unit, it has a unique  inverse.
 
@@
     maximal, then there exists a strictly larger proper ideal
-    $I_{3} \supsetneq I_2$.
+    $I_{3}$ containing $I_2$.
 
@@
 
-    It is straight-forward to show that \(\bigcup_{k=1}^{\infty} I_{k}\)
-    satisfies the definition of an ideal of $R$, and this union certainly
-    contains \(x\). So by Zorn's lemma, since every ascending chain of ideals
+    It is straightforward to verify that the increasing union of all $I_{k}$, $k \geq 1$, 
+    is by definition an ideal of $R$, and certainly
+    contains \(x\).  Hence by Zorn's lemma, since every ascending chain of ideals
     containing $x$ with respect to inclusion has its union as an upper bound,
@@
 This argument has potentially infinitely many steps, and chose to avoid this
-issue by including an axiom that in any non-unit \(x\) is contained in some
+issue by including an axiom that in any non-unit \(x\) of a ring is contained in some
 maximal ideal.
 
-\todo[inline]{Include some relevant code}
+\begin{minted}{coq}
+Axiom comm_ring_nonunit_maximal_ideal:
+  forall (x: Carrier),
+    ~ is_unit equiv mul one x ->
+    exists (P: Carrier -> Prop)(P_proper: Proper (equiv ==> iff) P)
+    	(P_ideal: Ideal add zero minus mul P),
+      P x /\ maximal_ideal P.
+\end{minted}
 
-We also used classical logic to prove that \(1 - x\) is a unit where \(x\) is
-a non-unit in any local ring. The proof used the rule \(\neg\neg P\rightarrow
-P\) in order to do a proof by contradiction.
+We also used classical logic to prove that \(1 - x\) is a unit whenever \(x\) is
+an element of a local ring that is not a unit. The proof is completed by way of contradiction, and uses the rule that  
+ \(\neg\neg P\rightarrow
+P\).
 
-\todo[inline]{Include some relevant code}
-
-Finally, we turn to our formal proof of Nakayama's Lemma, our ultimate goal.
+To start describing our proof, we formalize the statement of Nakayama's Lemma in Coq.
 
@@
 
-We needed a lemma before moving on to prove the main theorem which states that
-for a finitely generated $R$-module \(M\) with generating set
-\(b_{1}, b_{2}, \dots, b_{n}\), any element \(x\in I M\), where \(I\) is an
-ideal of $R$, can be written as a linear combination of the generating set with
-coefficients coming from \(I\).
-\emily{I'm confused:  Isn't this how we defined $I M$? Where are the $u$'s and
-  $a$'s coming from?}
-In other words, given \(x\in I M\), there is by definition a linear combination
-between elements \(u_{1}, \dots, u_{m}\in I\), and elements
-\(a_{1},\dots, a_{m}\in M\), we need a lemma that states \(x\) can be written
-as a linear combination between elements of \(I\) and the generating set
-\(b_{1},\dots, b_{n}\in M\). This follows the informal mathematical argument
-going inductively through the elements needed to generate \(x\) and shows that
-each vector can be rewritten in terms of the generating set times coefficients
-from the ideal \(I\) as follows.
+\begin{minted}{coq}
+Theorem nakayama:
+  forall {n: nat}(basis: t M n),
+    finitely_generated Mequiv Madd Mzero action basis ->
+  (forall a: M, ideal_module_pred a) ->
+  forall a: M, a =M= Mzero.
+\end{minted}
+
+To use as a building block in the formal proof of Nakayama's Lemma, we first formally stated and proved a lemma that gives a concrete description of the elements of the submodule $\mathfrak{m} M$  appearing in the statement of the the theorem.
+This lemma applies more generally, to any finitely generated module $M$ over a (not necessarily local) commutative ring, and any submodule of the form $IM$, for $I$ an arbitrary ideal. 
+By definition, $IM$ consists of scalar combinations of elements of $M$ with coefficients in $I$. 
+The lemma states that the elements from $M$ appearing in the expression can be chosen to be from any 
+ fixed finite generating set for $M$. 
+In other words, given any generating set  $u_{1},\dots, u_{n} \in M$  of a  finitely generated $R$-module $M$, every element $x$ of $I M$ can be written as a scalar combination $a_1 \cdot u_1 + a_2  \cdot u_2 + \cdots + a_n  \cdot u_n$, where each $a_i \in I$.
+
+\begin{minted}{coq}
+Lemma module_fin_gen_ideal_module:
+  forall {n: nat}(basis: t M n),
+    finitely_generated Mequiv Madd Mzero action basis ->
+    forall {m: nat}(coeffs: t R m)(vectors: t M m),
+      Forall P coeffs ->
+      exists (coeffs': t R n),
+        linear_combin Madd Mzero action coeffs vectors =M=
+          linear_combin Madd Mzero action coeffs' basis /\
+        Forall P coeffs'.
+\end{minted}
+
+The proof follows from a straightforward argument based on definitions, by induction on the number of elements in a fixed generating set for $M$, which we informally describe:  By definition, $x \in I M$ can  be written, for some positive integer $k$ and elements $r_i \in R$ and $w_i \in M$,  $1 \leq i \leq k$, as   $x = r_1 \cdot w_1 + r_2 \cdot w_2 + \cdots + r_k \cdot w_k$.
+What's more, by definition of a finite generating set $u_{1},\dots, u_{n}$ for $M$,  each $w_i$ equals 
+$c_{i1} \cdot u_1 + c_{i2} \cdot u_2 + \cdots + c_{in} \cdot u_n$ for appropriate choices of $c_{ij} \in R$. 
+Hence, inductively applying associativity, 
 \begin{align*}
-  x & = \sum_{k=1}^{m} u_{k} a_{k} \\
-    & = \sum_{k=1}^{m} u_{k} (r_{k1} b_{1} + \cdots + r_{kn} b_{n}) \\
-    & = \sum_{j=1}^{n} (u_{1} r_{1j} + \cdots + u_{m} r_{mj}) b_{j}
+  x = \sum_{i=1}^{k} r_i  \cdot  w_i  =  \sum_{i=1}^{k} r_i  \cdot  \left(  \sum_{j=1}^n c_{ij}  \cdot  u_j \right) 
+  =   \sum_{j=1}^n  \sum_{i=1}^{k} r_i   \cdot  (c_{ij}  \cdot  u_j ) 
+=  \sum_{j=1}^n \left( \sum_{i=1}^{k}  c_{ij}  \cdot   r_i \right)   \cdot  u_j.   
 \end{align*}
-Since each \(u_{k}\) comes from the ideal \(I\), the absorbing property of
-ideals guarantees that \(u_{k} r_{k j}\) is also contained in \(I\). As ideals
-are also closed under addition, it follows that \(u_{1} r_{1j} + \cdots +
-u_{m} r_{m j}\) are all elements of \(I\). Thus, \(x\) can be written as a
-linear combination of the generating set with the coefficients coming from
-\(I\).
+By absorption in ideals, each  $c_{ij}  \cdot r_i$ is in $I$, and since ideals are closed under addition, we inductively conclude that 
+the coefficient $a_j := c_{1j} \cdot  r_1 +  c_{2j} \cdot  r_2 +  \cdots c_{kj}\cdot r_k$ of $u_j$ is also in $I$.
 
-\emily[inline]{I think we need to include more code here!  There are a lot of
-  pieces of formal proof that would be illustrative.}
+Now we move forward to outline the formal proof of Nakayama's lemma.
+We proceed by induction on the number of elements in a generating set for the
+$R$-module $M$. 
+The base case is the situation when \(M\) requires no generators, so 
+$M$ consists solely of the empty scalar combination, i.e., the empty sum, which, by convention, is the zero element.
+In other words, $M = 0$ by assumption, and this is also precisely the 
+conclusion of Nakayama's Lemma.  Hence the statement trivially, without using the hypothesis that $M = \mathfrak{m} M$.
 
-Now we move to describe the skeleton of our formal proof of Nakayama's lemma.
-We proceed by induction on the number of elements in a generating set for the
-finitely-generated module $M$. The base case where \(M\) is generated by 0
-elements is by definition true since an empty linear combination is
-conventionally taken to be the zero vector.
-\emily{I think we should consider using one generator for the base case.}
-The inductive case where \(M\) is generated by the vectors
-\(b_{1}, \dots, b_{m}, b_{m+1}\). By assumption \(M = \mathfrak{m} M\).
-With \(b_{1}\in M\), then \(b_{1}\in\mathfrak{m} M\) meaning that by our lemma,
-there exists a linear combination for \(b_{1}\), say
-\[b_{1} = u_{1} b_{1} + \cdots + u_{m+1} b_{m+1}\]
-for some \(u_{1}, \dots, u_{m+1}\in\mathfrak{m}\). Collect the \(b_{1}\) terms
-on the left-hand side of the equation to get that
-\[(1 - u_{1}) b_{1} = u_{2} b_{2} + \cdots + u_{m+1} b_{m+1}\text{.}\]
-As mentioned when defining maximal ideals, \(\mathfrak{m}\) can only contain
-non-units. Namely, \(u_{1}\) must be a non-unit. Then we had already proven
-that \(1 - u_{1}\) is a unit as we are in a local ring. Let \(v_{1}\) be the
-multiplicative inverse of \(1 - u_{1}\), and multiply it on both sides of the
-equation.
+We turn to the inductive step.  Fixing an arbitrary nonnegative integer $n$, 
+we assume that Nakayama's Lemma holds in the case that $M$ has a generating set 
+consisting of $n$ elements.
+
+Now, 
+fix an $R$-module $M$ generated by $u_1, \ldots, u_{n+1} \in M$. 
+By assumption, \(M = \mathfrak{m} M\), and in particular, 
+the generator $u_1$ is an element of the submodule $\mathfrak{m}M$.
+The lemma described above guarantees the existence of ring elements $a_1, \ldots, a_n \in \mathfrak{m}$
+for which 
+\[u_{1} = a_{1} \cdot u_{1} + a_2 \cdot u_2 + \cdots + a_{n+1} \cdot u_{n+1}. \]
+
+Collecting the \(u_{1}\) terms
+on the left-hand side of the equation, applying the existence of additive inverses in $R$, and
+ distributivity of scalar multiplication for modules, we see that
+\begin{equation} \label{equation1: e}
+(1 - a_{1}) \cdot u_{1} = a_{2} \cdot u_{2} + \cdots + a_{n+1} \cdot u_{n+1}\text{.}
+\end{equation}
+
+Since a proper ideal contains no units and $a_1$ is taken to be in $\mathfrak{m}$, it is not a unit.  
+Hence, by the formalized statement mentioned earlier, $1-a_1$ is a unit of $R$.    
+Let $b_{1} \in R$ denote its 
+multiplicative inverse, so that $b_1 \cdot  (1 - a_{1}) = 1$.
+Multiplying this element on the either side of \eqref{equation1: e}, we deduce the following.  
 \begin{align*}
-  v_{1} (1 - u_{1}) b_{1}
-    & = v_{1} u_{2} b_{2} + \cdots + v_{1} u_{m+1} b_{m+1} \\
-  1 b_{1} & = v_{1} u_{2} b_{2} + \cdots + v_{1} u_{m+1} b_{m+1} \\
-  b_{1} & = v_{1} u_{2} b_{2} + \cdots + v_{1} u_{m+1} b_{m+1} \\
+b_1 \cdot \left(  (1 - a_{1}) \cdot u_{1} \right)  & = b_1 \cdot  ( a_{2} \cdot u_{2} + \cdots + a_{n+1} \cdot u_{n+1} ) \\
+\left( b_1 \cdot  (1 - a_{1})\right) \cdot u_{1}   & = b_1 \cdot  ( a_{2} \cdot u_{2} ) + \cdots + b_1  \cdot   (a_{n+1} \cdot u_{n+1} )  \\
+u_1 = 1 \cdot u_{1}   & = ( b_1 \cdot  a_{2}  ) \cdot u_{2}  + \cdots + ( b_1  \cdot  a_{n+1} ) \cdot u_{n+1}  
 \end{align*}
-We have thus found that one of the basis vectors is not needed to generate this
-module. Using the induction hypothesis, we have that \(M = 0\). Showing that
-the induction hypothesis holds in Coq takes more work than in an informal
+In particular, the generator $u_1$ can be written as a scalar combination of the $n$ generators $u_2, \ldots, u_{n+1}$, and is superfluous.
+Hence $M$ can be generated by $n$ elements, and $M=0$ by the inductive hypothesis.
+
+Showing that
+the inductive hypothesis holds in Coq is more work than in this informal
 proof, but this extra work is just a lot of bookkeeping.

### 2022-11-17 nakayama/paper.tex
Added comment about inclincluding more code from the formal proof

@@
 
+\emily[inline]{Emily:  Reflecting, I think it would be very valuable to include the formal proof.
+Pieces would work, though it is short, and it could be ``broken up'' among the description of the informal argument.
+As is, our description of the proof focuses on the informal argument, which is not new/interesting.
+}
+
 Showing that

### 2022-11-18 nakayama/paper.tex
Implemented Witt's suggestions
* Changed vector space terminology to more general module phrases.
* Moved 1 from commutative rings to rings.

@@
 equality. 
-Not much is lost due to Coq's rewrite tactics for setoids--types equipped with an equivalence relation--
+Not much is lost due to Coq's rewrite tactics for setoids--types equipped with an equivalence relation---
 can still be called upon.
 
-Moving onward, rings form the next step in our algebraic hierarchy; a ring has two binary
-operations: addition, which must be commutative, and multiplication, which need
-not be commutative in general. Next, we formalized the definition of a commutative
-ring, further requiring commutativity of multiplication, as well as a
-multiplicative identity. At this point, we formalized the notion of an ideal of
-a commutative ring, a subgroup of the ring under addition that satisfies the
-absorption property under multiplication, i.e., \(r a\) is in the ideal for
-every element \(a\) of the ideal, and every element \(r\) of the commutative
-ring. We also used this to formalize the notion of a quotient ring $R/I$, where
-$I$ is an ideal of a commutative ring $R$.
+Moving onward, rings form the next step in our algebraic hierarchy; a ring has
+two binary operations: addition, which must be commutative, and multiplication,
+which need not be commutative in general. In our formulation, rings must have a
+multiplicative identity. Next, we formalized the definition of a commutative
+ring, further requiring commutativity of multiplication. At this point, we
+formalized the notion of an ideal of a commutative ring, a subgroup of the ring
+under addition that satisfies the absorption property under multiplication,
+i.e., \(r a\) is in the ideal for every element \(a\) of the ideal, and every
+element \(r\) of the commutative ring. We also used this to formalize the
+notion of a quotient ring $R/I$, where $I$ is an ideal of a commutative ring
+$R$.
 
@@
 \begin{minted}{coq}
-  Definition finitely_generated {n: nat}(basis: t M n) :=
-    forall (vector: M),
+  Definition finitely_generated {n: nat}(generatingSet: t M n) :=
+    forall (elt: M),
       exists (coeffs: t R n),
-        vector =M= linear_combin coeffs basis.
+        elt =M= linear_combin coeffs generatingSet.
 \end{minted}
@@
   Definition ideal_module (x: M): Prop :=
-    exists (n: nat)(coeffs: t R n)(vectors: t M n),
+    exists (n: nat)(coeffs: t R n)(elts: t M n),
       Forall P coeffs /\
-      x =M= linear_combin Madd Mzero action coeffs vectors.
+      x =M= linear_combin Madd Mzero action coeffs elts.
 \end{minted}
@@
 Lemma module_fin_gen_ideal_module:
-  forall {n: nat}(basis: t M n),
-    finitely_generated Mequiv Madd Mzero action basis ->
-    forall {m: nat}(coeffs: t R m)(vectors: t M m),
+  forall {n: nat}(generatingSet: t M n),
+    finitely_generated Mequiv Madd Mzero action generatingSet ->
+    forall {m: nat}(coeffs: t R m)(elts: t M m),
       Forall P coeffs ->
       exists (coeffs': t R n),
-        linear_combin Madd Mzero action coeffs vectors =M=
-          linear_combin Madd Mzero action coeffs' basis /\
+        linear_combin Madd Mzero action coeffs elts =M=
+          linear_combin Madd Mzero action coeffs' generatingSet /\
         Forall P coeffs'.

### 2022-11-21 nakayama/paper.tex
Small edit to comment

@@
 
-\emily[inline]{Emily:  Reflecting, I think it would be very valuable to include the formal proof.
+\emily[inline]{Emily:  Reflecting, I think it would be valuable to include at least parts of the formal proof.
 Pieces would work, though it is short, and it could be ``broken up'' among the description of the informal argument.
-As is, our description of the proof focuses on the informal argument, which is not new/interesting.
+As is, our description of the proof focuses on the informal argument, which is not ``new''.
 }

### 2022-12-11 nakayama/paper.tex
First edits on Nakayama paper

@@
 associativity, and the distributive law governing the compatibility of addition
-and multiplication holds.  We require rings to contain a \emph{multiplicative identity},
-and $1 \in \mathbb{Z}$ is such an element since $n \in \mathbb{Z}$ one has
-$n \cdot 1 = 1 \cdot n = n$. 
-Even more, the integers form a
+and multiplication holds.  We require rings to contain a \emph{multiplicative
+identity}, and $1 \in \mathbb{Z}$ is such an element since $n \in \mathbb{Z}$
+one has $n \cdot 1 = 1 \cdot n = n$. Even more, the integers form a
 \emph{commutative ring} since $n \cdot m = m \cdot n$ for all integers $n$ and
@@
 
-A \emph{prime ideal} of a commutative ring is a proper ideal $I$ with the following property:  
-If the product $x \cdot y$ of ring elements $x$ and $y$ is in $I$, then $x \in I$ or $y \in I$.
-The naming convention is motivated by the ring of integers, where the prime ideals are precisely those 
-of the form $p\mathbb{Z}$, where $p$ is a prime number, along with the zero ideal.
+A \emph{prime ideal} of a commutative ring is a proper ideal $I$ with the
+following property:   If the product $x \cdot y$ of ring elements $x$ and $y$
+is in $I$, then $x \in I$ or $y \in I$. The naming convention is motivated by
+the ring of integers, where the prime ideals are precisely those  of the form
+$p\mathbb{Z}$, where $p$ is a prime number, along with the zero ideal.
 
@@
 containing $6 \mathbb{Z}$, and in general, the prime ideals in the ring of
-integers besides the zero ideal are  $p \mathbb{Z}$, where $p$
-a prime number. 
-It is not a coincidence that every maximal ideal of the ring of integers is also a prime 
-ideal; the analogous statement can be proved in arbitrary commutative rings.
+integers besides the zero ideal are  $p \mathbb{Z}$, where $p$ a prime number. 
+It is not a coincidence that every maximal ideal of the ring of integers is
+also a prime  ideal; the analogous statement can be proved in arbitrary
+commutative rings.
 
@@
 %While we found later on that we did not need quotients, 
-While in the end, our formal proof
-does not require calling upon 
- quotients of algebraic
-structures, quotient rings and quotient modules are fundamental to commutative
-algebra, and one can use them to construct alternate proofs of Nakayama's
-Lemma. It is worth pointing out that we have formalized quotients of algebraic
-objects in Coq using typeclasses, which appear to work rather nicely.
+While in the end, our formal proof does not require calling upon quotients of
+algebraic structures, quotient rings and quotient modules are fundamental to
+commutative algebra, and one can use them to construct alternate proofs of
+Nakayama's Lemma. It is worth pointing out that we have formalized quotients of
+algebraic objects in Coq using typeclasses, which appear to work rather nicely.
 
@@
 terms of an arbitrary equivalence relation, in our theory a quotient group is 
-simply defined as a group, but under an equivalence relation that is not the usual 
-equality. 
-Not much is lost due to Coq's rewrite tactics for setoids--types equipped with an equivalence relation---
-can still be called upon.
+simply defined as a group, but under an equivalence relation that is not the
+usual equality. Not much is lost due to Coq's rewrite tactics for
+setoids--types equipped with an equivalence relation---can still be called
+upon.
 
@@
 moved on to do the same for the notion of a maximal ideal, a proper ideal 
-that is maximal with respect to inclusion. Below is the definition in Coq, which
-uses \texttt{P} as the predicate for the ideal.
+that is maximal with respect to inclusion. Below is the definition in Coq,
+which uses \texttt{P} as the predicate for the ideal.
 
@@
 i.e., an element $x^{-1} \in R$ for which $x \cdot x^{-1}$ is the
-multiplicative identity $1 \in R$.  In fact, it $x$ is a unit, it has a unique  inverse.
+multiplicative identity $1 \in R$.  In fact, it $x$ is a unit, it has a unique 
+inverse.
 
@@
 
-    It is straightforward to verify that the increasing union of all $I_{k}$, $k \geq 1$, 
-    is by definition an ideal of $R$, and certainly
-    contains \(x\).  Hence by Zorn's lemma, since every ascending chain of ideals
-    containing $x$ with respect to inclusion has its union as an upper bound,
-    there exists a maximal ideal of \(R\) containing \(x\).
+    It is straightforward to verify that the increasing union of all $I_{k}$,
+    $k \geq 1$, is by definition an ideal of $R$, and certainly
+    contains \(x\).  Hence by Zorn's lemma, since every ascending chain of
+    ideals containing $x$ with respect to inclusion has its union as an upper
+    bound, there exists a maximal ideal of \(R\) containing \(x\).
 \end{quote}
 
-This argument has potentially infinitely many steps, and chose to avoid this
-issue by including an axiom that in any non-unit \(x\) of a ring is contained in some
-maximal ideal.
+This argument has potentially infinitely many steps. A proof with infinitely
+many steps is a problem in Coq. To see this from the above argument, suppose we
+wrote a proof tactic \mintinline{coq}{generate_larger_ideal} that allows us to
+go from one non-maximal ideal \(I_{k}\) which contains \(x\) to another ideal
+\(I_{k+1}\) which also contains \(x\). Provided our first ideal \(I_{1}\) is
+not maximal, our first invocation of \mintinline{coq}{generate_larger_ideal}
+will produce another ideal \(I_{2}\). Our new ideal \(I_{2}\) may also not be
+maximal, requiring that we invoke \mintinline{coq}{generate_larger_ideal}
+again. This can lead to an infinite number of calls to the tactic
+\mintinline{coq}{generate_larger_ideal} which will occupy any machine's
+processor(s) forever, and further, the infinite number of ideals in the proof
+state will fill any machine's memory. After we have overwhelmed any system with
+these infinite number of calls to a single proof tactic, we still have to
+invoke more tactics to finish the proof with an application of Zorn's lemma,
+which finally guarantees us a maximal ideal containing \(x\). To summarize, we
+are forced to run the following proof script which will never get past calling
+\mintinline{coq}{generate_larger_ideal} infinitely many times.
+\begin{minted}{coq}
+  repeat generate_larger_ideal. (* must be called infinitely often *)
+  zorns_lemma. (* called after the above non-terminating call finishes *)
+\end{minted}
+We chose to avoid this infinite proof script issue by including an axiom that
+any non-unit \(x\) of a ring must be contained in some maximal ideal.
 
@@
 
-We also used classical logic to prove that \(1 - x\) is a unit whenever \(x\) is
-an element of a local ring that is not a unit. The proof is completed by way of contradiction, and uses the rule that  
- \(\neg\neg P\rightarrow
-P\).
+We also used classical logic to prove that \(1 - x\) is a unit whenever \(x\)
+is an element of a local ring that is not a unit. The proof is completed by way
+of contradiction, and uses the rule that \(\neg\neg P\rightarrow P\).
 
-To start describing our proof, we formalize the statement of Nakayama's Lemma in Coq.
+To start describing our proof, we formalize the statement of Nakayama's Lemma
+in Coq.
 
@@
 \begin{minted}{coq}
+Context {P_ideal: Ideal Radd Rzero Rminus Rmul P}.
+Context {P_maxideal: maximal_ideal Requiv Radd Rzero Rminus Rmul P}.
+Context {R_local: local_ring Requiv Radd Rzero Rminus Rmul}.
+
+Let ideal_module_pred := ideal_module Mequiv Madd Mzero action P.
+
 Theorem nakayama:
@@
 
-To use as a building block in the formal proof of Nakayama's Lemma, we first formally stated and proved a lemma that gives a concrete description of the elements of the submodule $\mathfrak{m} M$  appearing in the statement of the the theorem.
-This lemma applies more generally, to any finitely generated module $M$ over a (not necessarily local) commutative ring, and any submodule of the form $IM$, for $I$ an arbitrary ideal. 
-By definition, $IM$ consists of scalar combinations of elements of $M$ with coefficients in $I$. 
-The lemma states that the elements from $M$ appearing in the expression can be chosen to be from any 
- fixed finite generating set for $M$. 
-In other words, given any generating set  $u_{1},\dots, u_{n} \in M$  of a  finitely generated $R$-module $M$, every element $x$ of $I M$ can be written as a scalar combination $a_1 \cdot u_1 + a_2  \cdot u_2 + \cdots + a_n  \cdot u_n$, where each $a_i \in I$.
+To use as a building block in the formal proof of Nakayama's Lemma, we first
+formally stated and proved a lemma that gives a concrete description of the
+elements of the submodule $\mathfrak{m} M$  appearing in the statement of the
+theorem. This lemma applies more generally, to any finitely generated module
+$M$ over a (not necessarily local) commutative ring, and any submodule of the
+form $I M$, for $I$ an arbitrary ideal. By definition, $IM$ consists of scalar
+combinations of elements of $M$ with coefficients in $I$. The lemma states that
+the elements from $M$ appearing in the expression can be chosen to be from any
+fixed finite generating set for $M$. In other words, given any generating set
+$u_{1},\dots, u_{n} \in M$  of a  finitely generated $R$-module $M$, every
+element $x$ of $I M$ can be written as a scalar combination $a_1 \cdot u_1 +
+a_2  \cdot u_2 + \cdots + a_n  \cdot u_n$, where each $a_i \in I$.
 
@@
 
-The proof follows from a straightforward argument based on definitions, by induction on the number of elements in a fixed generating set for $M$, which we informally describe:  By definition, $x \in I M$ can  be written, for some positive integer $k$ and elements $r_i \in R$ and $w_i \in M$,  $1 \leq i \leq k$, as   $x = r_1 \cdot w_1 + r_2 \cdot w_2 + \cdots + r_k \cdot w_k$.
-What's more, by definition of a finite generating set $u_{1},\dots, u_{n}$ for $M$,  each $w_i$ equals 
-$c_{i1} \cdot u_1 + c_{i2} \cdot u_2 + \cdots + c_{in} \cdot u_n$ for appropriate choices of $c_{ij} \in R$. 
-Hence, inductively applying associativity, 
+The proof follows from a straightforward argument based on definitions, by
+induction on the number of elements in a fixed generating set for $M$, which we
+informally describe: By definition, $x \in I M$ can  be written, for some
+positive integer $k$ and elements $r_i \in R$ and $w_i \in M$,
+$1 \leq i \leq k$, as $x = r_1 \cdot w_1 + r_2 \cdot w_2 + \cdots +
+r_k \cdot w_k$. What's more, by definition of a finite generating set $u_{1},
+\dots, u_{n}$ for $M$, each $w_i$ equals $c_{i1} \cdot u_1 + c_{i2} \cdot u_2 +
+\cdots + c_{in} \cdot u_n$ for appropriate choices of $c_{ij} \in R$. Hence,
+inductively applying associativity, 
 \begin{align*}
-  x = \sum_{i=1}^{k} r_i  \cdot  w_i  =  \sum_{i=1}^{k} r_i  \cdot  \left(  \sum_{j=1}^n c_{ij}  \cdot  u_j \right) 
-  =   \sum_{j=1}^n  \sum_{i=1}^{k} r_i   \cdot  (c_{ij}  \cdot  u_j ) 
-=  \sum_{j=1}^n \left( \sum_{i=1}^{k}  c_{ij}  \cdot   r_i \right)   \cdot  u_j.   
+  x = \sum_{i=1}^{k} r_i \cdot w_i
+    = \sum_{i=1}^{k} r_i \cdot \left(\sum_{j=1}^n c_{ij} \cdot  u_j\right)
+    = \sum_{j=1}^{n}\sum_{i=1}^{k} r_i \cdot (c_{ij} \cdot u_j) 
+    = \sum_{j=1}^{n}\left(\sum_{i=1}^{k} c_{ij} \cdot r_i\right) \cdot u_j.   
 \end{align*}
-By absorption in ideals, each  $c_{ij}  \cdot r_i$ is in $I$, and since ideals are closed under addition, we inductively conclude that 
-the coefficient $a_j := c_{1j} \cdot  r_1 +  c_{2j} \cdot  r_2 +  \cdots c_{kj}\cdot r_k$ of $u_j$ is also in $I$.
+By absorption in ideals, each  $c_{ij}  \cdot r_i$ is in $I$, and since ideals
+are closed under addition, we inductively conclude that the coefficient $a_j
+:= c_{1j} \cdot  r_1 +  c_{2j} \cdot  r_2 +  \cdots c_{kj}\cdot r_k$ of $u_j$
+is also in $I$.
 
-Now we move forward to outline the formal proof of Nakayama's lemma.
-We proceed by induction on the number of elements in a generating set for the
-$R$-module $M$. 
-The base case is the situation when \(M\) requires no generators, so 
-$M$ consists solely of the empty scalar combination, i.e., the empty sum, which, by convention, is the zero element.
-In other words, $M = 0$ by assumption, and this is also precisely the 
-conclusion of Nakayama's Lemma.  Hence the statement trivially, without using the hypothesis that $M = \mathfrak{m} M$.
+Now we move forward to outline the formal proof of Nakayama's lemma. We proceed
+by induction on the number of elements in a generating set for the $R$-module
+$M$. The base case is the situation when \(M\) requires no generators, so $M$
+consists solely of the empty scalar combination, i.e., the empty sum, which, by
+convention, is the zero element. In other words, $M = 0$ by assumption, and
+this is also precisely the conclusion of Nakayama's Lemma.  Hence the statement
+trivially, without using the hypothesis that $M = \mathfrak{m} M$.
 
@@
 
-Now, 
-fix an $R$-module $M$ generated by $u_1, \ldots, u_{n+1} \in M$. 
-By assumption, \(M = \mathfrak{m} M\), and in particular, 
-the generator $u_1$ is an element of the submodule $\mathfrak{m}M$.
-The lemma described above guarantees the existence of ring elements $a_1, \ldots, a_n \in \mathfrak{m}$
+Now, fix an $R$-module $M$ generated by $u_1, \ldots, u_{n+1} \in M$. By
+assumption, \(M = \mathfrak{m} M\), and in particular, the generator $u_1$ is
+an element of the submodule $\mathfrak{m} M$. The lemma described above
+guarantees the existence of ring elements $a_1, \ldots, a_n \in \mathfrak{m}$
 for which 
-\[u_{1} = a_{1} \cdot u_{1} + a_2 \cdot u_2 + \cdots + a_{n+1} \cdot u_{n+1}. \]
+\[u_{1} = a_{1} \cdot u_{1} + a_2 \cdot u_2 + \cdots + a_{n+1} \cdot u_{n+1}.\]
 
-Collecting the \(u_{1}\) terms
-on the left-hand side of the equation, applying the existence of additive inverses in $R$, and
- distributivity of scalar multiplication for modules, we see that
-\begin{equation} \label{equation1: e}
-(1 - a_{1}) \cdot u_{1} = a_{2} \cdot u_{2} + \cdots + a_{n+1} \cdot u_{n+1}\text{.}
+Collecting the \(u_{1}\) terms on the left-hand side of the equation, applying
+the existence of additive inverses in $R$, and distributivity of scalar
+multiplication for modules, we see that
+\begin{equation}\label{equation1: e}
+(1 - a_{1}) \cdot u_{1} =
+  a_{2} \cdot u_{2} + \cdots + a_{n+1} \cdot u_{n+1}\text{.}
 \end{equation}
+In Coq, this bit looks like the following code below.
+\begin{minted}[linenos,firstnumber=157,stepnumber=5]{coq}
+  assert ((Rone [+] Rminus x1) <.> u1 =M=
+  linear_combin Madd Mzero action coeffs' generatingSet').
+  { setoid_rewrite (module_distrib_Radd Radd Rmul Rone
+      Mequiv Madd Mzero Mminus action).
+    setoid_rewrite (module_Rone Radd Rmul Rone
+      Mequiv Madd Mzero Mminus action).
+    setoid_rewrite (module_minus_l Requiv Radd Rzero Rminus Rmul Rone
+      Mequiv Madd Mzero Mminus action).
+    symmetry.
+    apply (group_move_r Mequiv Madd Mzero Mminus).
+    symmetry.
+    assumption. }
+\end{minted}
 
-Since a proper ideal contains no units and $a_1$ is taken to be in $\mathfrak{m}$, it is not a unit.  
-Hence, by the formalized statement mentioned earlier, $1-a_1$ is a unit of $R$.    
-Let $b_{1} \in R$ denote its 
-multiplicative inverse, so that $b_1 \cdot  (1 - a_{1}) = 1$.
-Multiplying this element on the either side of \eqref{equation1: e}, we deduce the following.  
+Since a proper ideal contains no units and $a_1$ is taken to be in
+$\mathfrak{m}$, it is not a unit. Hence, by the formalized statement mentioned
+earlier, $1 - a_{1}$ is a unit of $R$. Let $b_{1} \in R$ denote its 
+multiplicative inverse, so that $b_1 \cdot  (1 - a_{1}) = 1$. Multiplying this
+element on the either side of \eqref{equation1: e}, we deduce the following.  
 \begin{align*}
-b_1 \cdot \left(  (1 - a_{1}) \cdot u_{1} \right)  & = b_1 \cdot  ( a_{2} \cdot u_{2} + \cdots + a_{n+1} \cdot u_{n+1} ) \\
-\left( b_1 \cdot  (1 - a_{1})\right) \cdot u_{1}   & = b_1 \cdot  ( a_{2} \cdot u_{2} ) + \cdots + b_1  \cdot   (a_{n+1} \cdot u_{n+1} )  \\
-u_1 = 1 \cdot u_{1}   & = ( b_1 \cdot  a_{2}  ) \cdot u_{2}  + \cdots + ( b_1  \cdot  a_{n+1} ) \cdot u_{n+1}  
+b_1 \cdot \left((1 - a_{1}) \cdot u_{1} \right)
+  & = b_1 \cdot (a_{2} \cdot u_{2} + \cdots + a_{n+1} \cdot u_{n+1}) \\
+\left( b_1 \cdot (1 - a_{1})\right) \cdot u_{1}
+  & = b_1 \cdot (a_{2} \cdot u_{2}) + \cdots + b_1 \cdot (a_{n+1} \cdot u_{n+1}) \\
+u_1 = 1 \cdot u_{1}
+  & = (b_1 \cdot  a_{2}) \cdot u_{2} + \cdots + (b_1  \cdot  a_{n+1}) \cdot u_{n+1}  
 \end{align*}
-In particular, the generator $u_1$ can be written as a scalar combination of the $n$ generators $u_2, \ldots, u_{n+1}$, and is superfluous.
-Hence $M$ can be generated by $n$ elements, and $M=0$ by the inductive hypothesis.
+\begin{minted}[linenos,firstnumber=181,stepnumber=5]{coq}
+  pose proof
+    (local_comm_ring_sub_1_nonunit Requiv Radd Rzero Rminus Rmul Rone
+      R_local x1 Hx1_nonunit) as H1mx1_unit.
+  (* u1 = (b1 coeffs') . generatingSet *)
+  inversion_clear H1mx1_unit as [b1 Hb1].
+  setoid_rewrite (commutative Requiv Rmul) in Hb1.
+  apply (module_op_l Requiv Mequiv action) with (r:=b1) in H.
+  setoid_rewrite <- (module_distrib_Rmul Radd Rmul Rone
+    Mequiv Madd Mzero Mminus action) in H.
+  setoid_rewrite Hb1 in H.
+  setoid_rewrite (module_Rone Radd Rmul Rone
+    Mequiv Madd Mzero Mminus action) in H.
+  setoid_rewrite <- (module_linear_combin_mul_l Requiv Radd Rmul Rone
+    Mequiv Madd Mzero Mminus action) in H.
+\end{minted}
+In particular, the generator $u_1$ can be written as a scalar combination of
+the $n$ generators $u_2, \ldots, u_{n+1}$, and is superfluous. Hence $M$ can be
+generated by $n$ elements, and $M=0$ by the inductive hypothesis.
 
-\emily[inline]{Emily:  Reflecting, I think it would be valuable to include at least parts of the formal proof.
-Pieces would work, though it is short, and it could be ``broken up'' among the description of the informal argument.
-As is, our description of the proof focuses on the informal argument, which is not ``new''.
-}
+\emily[inline]{Emily: Reflecting, I think it would be valuable to include at
+least parts of the formal proof.  Pieces would work, though it is short, and it
+could be ``broken up'' among the description of the informal argument.  As is,
+our description of the proof focuses on the informal argument, which is not
+``new''.}
 
-Showing that
-the inductive hypothesis holds in Coq is more work than in this informal
-proof, but this extra work is just a lot of bookkeeping.
+Showing that the inductive hypothesis holds in Coq is more work than in this
+informal proof, but this extra work is just a lot of bookkeeping.
+
+\section{Conclusion}
+TODO
 

### 2022-12-14 nakayama/paper.tex
Offering a few remarks on the proof code

@@
 \end{equation}
-In Coq, this bit looks like the following code below.
+In Coq, we worked backwards to establish this fact. The comments following
+each tactic offers a brief explanation of the effects on the goal.
 \begin{minted}[linenos,firstnumber=157,stepnumber=5]{coq}
-  assert ((Rone [+] Rminus x1) <.> u1 =M=
+  assert ((Rone [+] Rminus a1) <.> u1 =M= (* (1 - a1) u1 = ... *)
     linear_combin Madd Mzero action coeffs' generatingSet').
   { setoid_rewrite (module_distrib_Radd Radd Rmul Rone
-      Mequiv Madd Mzero Mminus action).
+      Mequiv Madd Mzero Mminus action). (* 1 u1 + (-a1) u1 = ... *)
     setoid_rewrite (module_Rone Radd Rmul Rone
-      Mequiv Madd Mzero Mminus action).
+      Mequiv Madd Mzero Mminus action). (* u1 + (-a1) u1 = ... *)
     setoid_rewrite (module_minus_l Requiv Radd Rzero Rminus Rmul Rone
-      Mequiv Madd Mzero Mminus action).
-    symmetry.
-    apply (group_move_r Mequiv Madd Mzero Mminus).
-    symmetry.
+      Mequiv Madd Mzero Mminus action). (* u1 - a1 u1 = ... *)
+    symmetry. (* ... = u1 - a1 u1 *)
+    apply (group_move_r Mequiv Madd Mzero Mminus). (* ... + a1 u1 = u1 *)
+    symmetry. (* u1 = ... + a1 u1 *)
     assumption. }
@@
     (local_comm_ring_sub_1_nonunit Requiv Radd Rzero Rminus Rmul Rone
-      R_local x1 Hx1_nonunit) as H1mx1_unit.
-  (* u1 = (b1 coeffs') . generatingSet *)
-  inversion_clear H1mx1_unit as [b1 Hb1].
-  setoid_rewrite (commutative Requiv Rmul) in Hb1.
+      R_local x1 Hx1_nonunit) as H1ma1_unit.
+  (* Getting to u1 = (b1 coeffs') . generatingSet *)
+  inversion_clear H1ma1_unit as [b1 Hb1]. (* 1 - a1 is a unit *)
+  setoid_rewrite (commutative Requiv Rmul) in Hb1. (* b1 (1 - a1) = 1 *)
+\end{minted}
+This bit of proof code has the effect of naming \(b_{1}\) as the inverse of the
+unit \(1 - a_{1}\) and storing in the hypothesis \texttt{Hb1} the equation
+\(b_{1} (1 - a_{1}) = 1\). The remainder of the code goes on to multiply on the
+left by \(b_{1}\) in the equation \texttt{H} in order to say that
+\(b_{1} ((1 - a_{1}) u1) = b_{1} (a_{2} u_{2} + \cdots + a_{n+1} u_{n+1})\).
+Going on to use the rules of module actions and hypothesis \texttt{Hb1}, we can
+simplify the left hand side of \texttt{H} to be just \(u_{1}\).
+\begin{minted}[linenos,firstnumber=last,stepnumber=5]{coq}
   apply (module_op_l Requiv Mequiv action) with (r:=b1) in H.
   setoid_rewrite <- (module_distrib_Rmul Radd Rmul Rone
-    Mequiv Madd Mzero Mminus action) in H.
-  setoid_rewrite Hb1 in H.
+    Mequiv Madd Mzero Mminus action) in H. (* H: (b1 (1 - a1)) u1 = ... *)
+  setoid_rewrite Hb1 in H. (* H: (1) u1 = ... *)
   setoid_rewrite (module_Rone Radd Rmul Rone
-    Mequiv Madd Mzero Mminus action) in H.
-  setoid_rewrite <- (module_linear_combin_mul_l Requiv Radd Rmul Rone
-    Mequiv Madd Mzero Mminus action) in H.
+    Mequiv Madd Mzero Mminus action) in H. (* H: u1 = ... *)
 \end{minted}

### 2023-01-03 nakayama/paper.tex
Exposition edits throughout

@@
 fixed integer $n>0$, fields---commutative rings in which every nonzero element
-has a multiplicative inverse---such as the rings of rational numbers, real
-numbers, and complex numbers, and rings of polynomials in a variable $x$ with
+has a multiplicative inverse---such as the rings of rational numbers $\mathbb{Q}$, real
+numbers $\mathbb{R}$, and complex numbers $\mathbb{C}$, and the rings
+ of polynomials in a variable $x$ with
 integer coefficients, or with coefficients in a field.
+
+A \emph{subgroup} of a group $G$ is a subset  $H$ of $G$ that is itself a 
+group when the binary operation of $G$ is restricted to $H$.
+Similarly, a \emph{subring} of a ring $R$
+is a subset $S$ of $R$ that forms a group when the operations on $R$ are 
+restricted to $S$, using the same multiplicative identity.  
+One has the sequence of subrings $\mathbb{Z} \subseteq \mathbb{Q} \subseteq \mathbb{R} \subseteq \mathbb{C}$.
 
@@
 an $F$-vector space, so the notion of a module over an arbitrary commutative
-ring extends that of a vector space over a field. Finitely generated vector
-spaces form the foundation for matrix algebra, and the extension of this notion
+ring extends that of a vector space over a field. 
+An $R$-\emph{submodule} $N$ of a module $M$ is simply a subgroup of $M$ that inherits 
+the scalar multiplication of $N$, i.e., $r \cdot w$ is an element of $N$ whenever $w \in N$.
+Therefore, returning to the case that $F$ is a field,
+the $F$-submodules of a vector space over $F$ are precisely its vector subspaces.
+
+Finitely generated vector spaces form the foundation for matrix algebra, and the extension of this notion
 to module theory is needed to state Nakayama's Lemma. We call an $R$-module
-$M$ \emph{finitely generated} if there exist a fixed finite number of elements
-$u_1, \ldots, u_n$ of $M$ with the following property:  Given any  $w \in M$,
+$M$ \emph{finitely generated} if there exist a fixed finite list of elements
+$u_1, \ldots, u_n$ of $M$ such that every element of $M$ is a scalar combination 
+of the $u_i$.  In other words, 
+given any  $w \in M$,
 there exist $r_1, \ldots, r_n \in R$ for which  
@@
 
-When $R = F$ is a field and $M = V$ is a finite-dimensional vector space over
-$F$, one can choose $u_1, \ldots, u_n$ to be a basis for $V$, i.e.,
+It is straightforward to see that a finitely generated module over a field is  
+simply a finite dimensional vector space.
+Moreover, if $V$ is a finite dimensional vector space over a field 
+$F$, one can choose the generators $u_1, \ldots, u_n$ to be a basis for $V$, so that  
 $n = \dim V$. In this case, the choice of scalar coefficients in the expression
@@
 
-In order to state Nakayama's Lemma, we first explain some notation:  If $I$ is
-an ideal of a commutative ring $R$ and $M$ is an $R$-module, then $IM$ is the
-set of elements of the form $a_1 u_1 + a_2 u_2 + \cdots + a_k u_k$, where, for
-some positive integer $k$, $a_1, \ldots, a_k \in I$ and
-$u_1, \ldots, u_k \in M$. Notice that due to the absorption property of ideals,
-$I M$ is an $R$-module contained in $M$.
+In order to informally state Nakayama's Lemma, we first explain some of notational 
+conventions.  In this dicussion, suppose that  $I$ is an ideal of a commutative ring $R$, 
+and that $M$ is an $R$-module. Then $IM$ denotes the set of all scalar combinations of 
+elements in $M$ with coefficients in $I$.  That is, $IM$ is the set of  elements of the form, 
+for some positive integer $k$,
+ \[a_1 u_1 + a_2 u_2 + \cdots + a_k u_k\] 
+where $a_1, \ldots, a_k \in I$ and
+$u_1, \ldots, u_k \in M$. Observe the absorption property of ideals implies that 
+$I M$ is an $R$-submodule of $M$.
 
-If an $R$-module $M$ consists of only one element, this element must be its
-additive identity $0$ as an abelian group under addition. The notation $M=0$
-means that we are in this situation.
+If an $R$-module $M$ consists of just one element, this element must be its
+additive identity $0$, by virtue of the fact that $M$ is an abelian group under addition. 
+The notation $M=0$ is used to indicate that we are in this situation.
 
@@
 
-When $R=F$ is a field, its unique maximal ideal is the zero ideal, and given
-any vector space $M=V$ over $F$, the only linear combination of vectors with
-coefficients in the zero ideal is the zero vector. Hence in this special case,
-the hypothesis that  $M = \mathfrak{m} M$ is equivalent to the conclusion that
-$M=0$. Hence Nakayama's Lemma describes one way that finitely generated modules
+When $R=F$ is a field, its unique maximal ideal is the zero ideal.  
+Given any vector space $M=V$ over $F$, the only linear combination of vectors with
+coefficients in the zero ideal is the zero vector. Hence in this case, regardless of the choice of 
+vector space, the hypothesis that  $M = \mathfrak{m} M$ is equivalent to the conclusion that
+$M=0$. 
+In particular, the hypothesis that $V$ is finitely generated, which is equivalent to the
+assumption that it is a finite-dimensional $F$-vector space, is not required in this setting. 
+Therefore, Nakayama's Lemma describes one way that finitely generated modules
 over commutative local rings are similar to vector spaces.
 
-In general, the quotient $R/\mathfrak{m}$ of a local ring modulo its maximal
-ideal $\mathfrak{m}$ is a field, and the quotient of a module $M$ modulo the
+The quotient $R/\mathfrak{m}$ of a commutative ring $R$ modulo any maximal ideal 
+$\mathfrak{m}$ is a field; in fact, this property characterizes maximal ideals. 
+Moreover, given an arbitrary $R$-module $M$, its quotient modulo the
 submodule $\mathfrak{m}M$ is an $R/\mathfrak{m}$-module, i.e.,
@@
 \section{Formalization}
-We start by describing our process of formalizing the required algebraic
+We start by describing our process of formalizing the necessary algebraic
 structures detailed in the previous section. Then, with that in hand, we move
@@
 
-Our foundation begins by defining a semigroup class, which declares a binary
+\paragraph{Semigroups.} Our foundation begins by defining a semigroup class, which declares a binary
 operation to be associative. From here, we build up through monoids, which
@@
 \end{minted}
-Lines such as  ``\verb|monoid_semigroup :> Semigroup equiv op;|'' simply coerce
+The lines such as  ``\verb|monoid_semigroup :> Semigroup equiv op;|'' simply coerce
 the monoid typeclass into a semigroup.
 
-%While we found later on that we did not need quotients, 
-While in the end, our formal proof does not require calling upon quotients of
-algebraic structures, quotient rings and quotient modules are fundamental to
-commutative algebra, and one can use them to construct alternate proofs of
-Nakayama's Lemma. It is worth pointing out that we have formalized quotients of
-algebraic objects in Coq using typeclasses, which appear to work rather nicely.
+\paragraph{Algebraic quotients.}
+While in the end, our formal proof does not call upon quotients of
+algebraic structures, alternative proofs of Nakamaya's Lemma take advantage of 
+ the structures quotient rings and quotient modules.  As algebraic 
+ quotient structures are also fundamental to commutative algebra,
+it is work pointing out that we have formalized quotients of groups, rings, and modules 
+  using typeclasses, which appear to work rather smoothly.
 
@@
 for which the set of equivalence classes inherit the same kind of algebraic
-structure. For example, consider the quotient of a group modulo a subgroup,
-i.e., a subset of elements of the group that it itself a group under the group
-operations. Under equivalence relation on the group, every element of the
-subgroup must be in the same equivalence class as the identity. With \texttt{P}
+structure. 
+As an example, consider the quotient of a group modulo a subgroup,
+i.e., a subset of elements of the group that it itself a group using the same operations. 
+Under this equivalence relation on the group, every element of the
+subgroup must be in the same equivalence class as the identity. 
+For instance, after taking the quotient of the ring of integers $\mathbb{Z}$ by the
+subgroup $n \mathbb{Z}$ consisting of all multiples of an integer $n$, one obtains the
+group of integers modulo $n$, often denoted $\mathbb{Z}/n\mathbb{Z}$.
+In general, with \texttt{P}
 the predicate for the subgroup, there are two ways to make an equivalence
@@
 
-When these two relations coincide, then we can prove that this common
-equivalence relation actually preserves the group structure. Subgroups which
-have this property are called \emph{normal subgroups}.
+When these two equivalence relations coincide, then we can prove that this common
+ relation actually preserves the group structure. Subgroups of a group that satisfy 
+this property are called \emph{normal subgroups}.
 
@@
 
-The importance of quotients in commutative algebra motivates our use of
-equivalence relations to define the components of a group structure. If one
-were to instead use the regular Leibniz equality, it would be difficult to
-identify a quotient group and another group. However, by  defining a group in
+The utility--and, as a consequence, the ubiquity--of quotients in commutative algebra 
+motivates our choice to use equivalence relations to define the components of a group structure. If one
+were to instead use the traditional Leibniz equality, it would be difficult to
+identify a quotient group with another group. However, by  defining a group in
 terms of an arbitrary equivalence relation, in our theory a quotient group is 
 simply defined as a group, but under an equivalence relation that is not the
-usual equality. Not much is lost due to Coq's rewrite tactics for
-setoids--types equipped with an equivalence relation---can still be called
+usual equality. Not much is lost in adopting this convention thanks to Coq's 
+rewrite tactics for setoids--types equipped with an equivalence relation---can 
+still be called
 upon.
 
+\paragraph{Rings and their ideals.}
 Moving onward, rings form the next step in our algebraic hierarchy; a ring has
@@
 under addition that satisfies the absorption property under multiplication,
-i.e., \(r a\) is in the ideal for every element \(a\) of the ideal, and every
+i.e., \(r a\) sits in the ideal whenever \(a\) of the ideal, regardless of the choice of 
 element \(r\) of the commutative ring. We also used this to formalize the
@@
 
-We then were able to take advantage of the definition of a maximal ideal
+\noindent Next, we were able to employ this definition of a maximal ideal
 to formally define a local
@@
 
-At this point we formalized the definition of a module over a commutative ring,
+\paragraph{Modules over rings.}
+At this point, we formalized the definition of a module over a commutative ring,
 the commutative-algebraic generalization of the notion of a vector space over a
 field. Nakayama's Lemma is a statement about finitely generated modules, and
-hence we must formalize the notion of a scalar combination of a finite
-collection of elements, $u_1, \ldots, u_n$, of an $R$-module $M$, i.e.,
+hence we formalized the notion of a scalar combination of a finite
+collection of elements, $u_1, \ldots, u_n$ a module $M$ over a commutative ring $R$, i.e.,
 expressions of the form $r_1 u_1 + r_1 u_2 + \cdots + r_n u_n$, where each
-$r_i \in R$.
+$r_i$ is an element of $R$.
 
@@
 
-Next, given an ideal \(I\) of a commutative ring $R$ and and an $R$-module
-\(M\),  we defined the submodule $IM$, the set consisting of all scalar
+Finally, we defined the submodule $IM$ of a module $M$ over a commutative ring $R$, 
+where $I$ is an arbitrary ideal of $R$.
+Recall that when $R$ is local and $I$ is its unique maximal ideal, this submodule 
+appears in the statement of Nakayama's Lemma. 
+In general, $IM$ is the set consisting of all scalar
 combinations of elements of \(M\) whose coefficients are in  \(I\). We
-represented this in Coq as a predicate over \(M\).
+represent this in Coq as a predicate over \(M\).
 
@@
 
-The use of  ``\verb|Forall P coeffs|'' ensures that every element of the
+\noindent The use of  ``\verb|Forall P coeffs|'' ensures that every element of the
 coefficient list \texttt{coeffs} satisfies the predicate \texttt{P}.
@@
 
-We formally proved that an ideal $I$ of a commutative ring $R$ that contains a
+We formally prove that an ideal $I$ of a commutative ring $R$ that contains a
 unit $x$, then $I$ must be the trivial ideal, i.e., the entire ring.  The
-informal logic is as follows:  By the absorption property, since $x \in I$, we
-have that $x \cdot x^{-1} = 1 \in I$.  Hence for every element $r$ of $R$,
+informal logic is as follows:  Due to the absorption property of $I$,  
+$x \cdot x^{-1} = 1 \in I$.  Hence for every element $r$ of $R$,
 $r = r \cdot 1$ is also in $I$, i.e., $I=R$.
@@
 Every non-unit element of a commutative ring is contained in some maximal
-ideal. This fact relies on the Axiom of Choice. The following standard informal
+ideal, a fact that relies on the Axiom of Choice.
+
+The following standard informal
 proof calls upon Zorn's lemma, which is equivalent to the Axiom of Choice, and
@@
 
-This argument has potentially infinitely many steps. A proof with infinitely
+The above argument has potentially infinitely many steps. A proof with infinitely
 many steps is a problem in Coq. To see this from the above argument, suppose we

### 2023-01-03 nakayama/paper.tex
Edits to description on Axiom of Choice

@@
 applications. Less frequently referred to as the \emph{Krull-Azumaya theorem}
-\footnote{Hideyuki Matsumura explains in his text \emph{Commutative Algebra}
+\footnote{Hideyuki Matsumura explains in his book \emph{Commutative Algebra}
   \cite{matsumura}: ``{This simple but important lemma is due to T.\ Nakayama,
@@
 Beyond formalizing the relevant structures from higher algebra, we also
-formally establish some basic theory. For instance, a \emph{unit} of a
-commutative ring $R$ is an element $x \in R$ with a multiplicative inverse,
-i.e., an element $x^{-1} \in R$ for which $x \cdot x^{-1}$ is the
-multiplicative identity $1 \in R$.  In fact, it $x$ is a unit, it has a unique 
-inverse.
+formally establish some basic theory from the field in Coq. For instance, 
+consider the notion of a \emph{unit} of a
+commutative ring $R$, which is an element $a \in R$ with a multiplicative inverse,
+i.e., there exists an element $a^{-1} \in R$ for which $x^{-1} \cdot x$ is the
+multiplicative identity $1 \in R$.  In fact, it $x$ is a unit, its inverse is unique.
 
-We formally prove that an ideal $I$ of a commutative ring $R$ that contains a
-unit $x$, then $I$ must be the trivial ideal, i.e., the entire ring.  The
-informal logic is as follows:  Due to the absorption property of $I$,  
-$x \cdot x^{-1} = 1 \in I$.  Hence for every element $r$ of $R$,
+\emily[inline]{Emily: I changed statement to \emph{if and only if} below; do we need to update formal proof?}
+Suppose that $I$ is an ideal of a commutative rings $R$.  
+We formally state prove the following lemma: If $I$ contains a
+unit $a$ if and only if $I$ is the trivial ideal, i.e., $I=R$. 
+The informal proof logic is as follows:  Due to the absorption property of $I$,  
+$a^{-1}  \cdot a= 1 \in I$.  Hence for every element $r$ of $R$,
 $r = r \cdot 1$ is also in $I$, i.e., $I=R$. 
+On the other hand, if $I = R$, then the multiplicative identity $1$ is a unit in $I$.
 
+\paragraph{Dealing with the Axiom of Choice.}
 Every non-unit element of a commutative ring is contained in some maximal
 ideal, a fact that relies on the Axiom of Choice. 
-
 The following standard informal
-proof calls upon Zorn's lemma, which is equivalent to the Axiom of Choice, and
-says that given a partially ordered set $S$, if every chain in $S$ has an upper
-bound, then $S$ must have at least one maximal element.
+proof calls upon Zorn's lemma, which is equivalent to the Axiom of Choice, and which 
+says that if every chain of elements from a partially ordered set  has an upper
+bound in the set, then the set must contain at least one maximal element.
 
 \begin{quote}
-    Set \(I_{1}\) to be the principal ideal generated by an element \(x\) of a
-    commutative ring $R$, i.e. the smallest ideal containing the element $x$,
-    which consists of all $R$-multiples of $x$.
+	Fix a non-unit $x$ in a commutative ring $R$, and  \(I_{1}\) to be the principal 
+	ideal generated by $x$, i.e., the smallest ideal containing the element $x$,
+    which consists of all $R$-multiples of it.  No element of $I_1$ is a unit, since if  
+    $y \in R$ were the multiplicative inverse of some $R$-multiple
+    $r \cdot x$, then $1 = y \cdot (r \cdot x) = (y\cdot r) \cdot x$, showing that $x^{-1} = y \cdot r$, 
+    which contradicts the assumption that $x$ is not a unit. Hence by the lemma described earlier in this section, 
+    $I_1$ is proper.
 
-    If \(I_{1}\) is not a maximal ideal, then there exists a strictly larger
+    If \(I_{1}\) is not a maximal ideal of $R$, then by definition there exists a strictly larger
     proper ideal \(I_{2}\) of $R$, i.e.,
-    $x\in I_{1}\subsetneq I_{2} \subsetneq R$. Moreover, if  \(I_{2}\) is not
+    $x \in I_{1}\subsetneq I_{2} \subsetneq R$. Likewise, if  \(I_{2}\) is again not
     maximal, then there exists a strictly larger proper ideal
-    $I_{3}$ containing $I_2$.
+    $I_{3}$, which, if not maximal, is strictly contained in another ideal, $I_4$, etc.
 
-    Continuing this process, if it terminates at some step, we have found a
-    maximal ideal, and if not, one obtains an infinite chain of ideals
-    containing \(x\).
-    \[x\in I_{1}\subsetneq I_{2}\subsetneq I_{3}\subsetneq\cdots\subsetneq R\]
+  Continuing in this way, if  this process terminates, we have successfully identified a
+    maximal ideal of $R$ that contains $x$, and if not, one obtains an infinite, strictly increasing chain of proper ideals containing $x$, 
+    \[I_{1}\subsetneq I_{2}\subsetneq I_{3}\subsetneq\cdots\subsetneq I_n \subsetneq \cdots. \]
+    It is straightforward to verify that an increasing union of ideals 
+    is, by definition, an ideal containing every ideal in the union.  Moreover, if each ideal in the union
+    contains an element $x$, then the union certainly 
+       contains \(x\) as well.
 
-    It is straightforward to verify that the increasing union of all $I_{k}$,
-    $k \geq 1$, is by definition an ideal of $R$, and certainly
-    contains \(x\).  Hence by Zorn's lemma, since every ascending chain of
-    ideals containing $x$ with respect to inclusion has its union as an upper
-    bound, there exists a maximal ideal of \(R\) containing \(x\).
+      Hence the set $S$ of all ideals of $R$, partially ordered by inclusion, 
+       satisfies the property that every chain in $S$ has an upper bound in $S$.
+    Therefore Zorn's lemma ensures the existence of a maximal ideal of \(R\) containing \(x\).
 \end{quote}

### 2023-01-03 nakayama/paper.tex
Broke section on algebraic structures and formal proof into two separate sections

@@
 
-\paragraph{Commutative rings.}
+\subsubsection{Commutative rings}
 In abstract algebra, the quintessential example of a commutative ring is the
@@
 
-\paragraph{Ideals of commutative rings.}
+\subsubsection{Ideals of commutative rings}
 The concept of an {ideal} of a ring can be thought of as an extension of the
@@
 
-\paragraph{Local rings.}
+\subsubsection{Local rings}
 A commutative ring is \emph{local} if it has exactly one maximal ideal. 
@@
 
-\paragraph{Modules over commutative rings.}
+\subsubsection{Modules over commutative rings}
 Let  $R$ be a commutative ring. 
@@
 
-\section{Formalization}
-We start by describing our process of formalizing the necessary algebraic
-structures detailed in the previous section. Then, with that in hand, we move
-on to the formal proof of Nakayama's Lemma.
+\section{Our Algebraic Hierarchy}
+In this section we describe our process of formalizing the necessary algebraic
+structures, detailed in the previous section, in Coq. Then, with these formal definitions 
+ in hand, we move
+on in the next section to detail our formal proof of Nakayama's Lemma.
 
-\subsection{Our Algebraic Hierarchy}
 \begin{figure}[t]
@@
 
-\paragraph{Semigroups.} Our foundation begins by defining a semigroup class, which declares a binary
+\subsection{Semigroups} Our foundation begins by defining a semigroup class, which declares a binary
 operation to be associative. From here, we build up through monoids, which
@@
 
-\paragraph{Algebraic quotients.}
+\subsection{Algebraic quotients}
 While in the end, our formal proof does not call upon quotients of
@@
 
-\paragraph{Rings and their ideals.}
+\subsection{Rings and their ideals}
 Moving onward, rings form the next step in our algebraic hierarchy; a ring has
@@
 %  combination in multiple ways, while bases are linearly independent.  I've
-%  proposed a rewrite of the blue paragraph right above it.  Drew, can you
+%  proposed a rewrite of the blue subsubsection right above it.  Drew, can you
 %  double check it for accuracy with respect to the code? 
@@
 
-\paragraph{Modules over rings.}
+\subsection{Modules over rings}
 At this point, we formalized the definition of a module over a commutative ring,
@@
 
-\subsection{Constructing the Formal Proof}
+\section{Constructing the Formal Proof}
 Beyond formalizing the relevant structures from higher algebra, we also
@@
 
-\paragraph{Dealing with the Axiom of Choice.}
+\subsection{Dealing with the Axiom of Choice}
 Every non-unit element of a commutative ring is contained in some maximal
@@
   Continuing in this way, if  this process terminates, we have successfully identified a
-    maximal ideal of $R$ that contains $x$, and if not, one obtains an infinite, strictly increasing chain of proper ideals containing $x$, 
+    maximal ideal of $R$ that contains $x$, and if not, one obtains an infinite, strictly increasing chain of proper ideals of $R$, each containing $x$, 
     \[I_{1}\subsetneq I_{2}\subsetneq I_{3}\subsetneq\cdots\subsetneq I_n \subsetneq \cdots. \]
@@
 
+\subsection{The Formal Statement of Nakayama's Lemma}
 To start describing our proof, we formalize the statement of Nakayama's Lemma
@@
 
-\emily[inline]{Emily: Reflecting, I think it would be valuable to include at
-least parts of the formal proof.  Pieces would work, though it is short, and it
-could be ``broken up'' among the description of the informal argument.  As is,
-our description of the proof focuses on the informal argument, which is not
-``new''.}
-
 Showing that the inductive hypothesis holds in Coq is more work than in this

### 2023-01-04 nakayama/paper.tex
Exposition updates, mostly on section on Axiom of Choice

@@
 	Emily E.\ Witt\thanks{Witt acknowledges support from NSF CAREER Award
-    DMS-1945611 and the 2022-23 Ruth I.\, Michler Memorial Prize from the
+    DMS-1945611, the Keeler Intra-University Professorship from the University of Kansas, and the 2022-23 Ruth I.\, Michler Memorial Prize from the
     Association for Women in Mathematics.} \\ {\ttfamily witt@ku.edu}
@@
 \noindent \textbf{Keywords:}
-Formalization of Mathematics,
-Formal Proof,
-Commutative Algebra,
-Commutative Ring,
-Local Ring,
-Ideal,
-Module over a Ring,
-Finitely Generated Module.
+formalization of mathematics,
+formal proof,
+commutative algebra,
+commutative ring,
+local ring,
+ideal,
+module over a ring,
+finitely generated module.
 
@@
 applications. Less frequently referred to as the \emph{Krull-Azumaya theorem}
-\footnote{Hideyuki Matsumura explains in his book \emph{Commutative Algebra}
+\footnote{Hideyuki Matsumura explains in his text \emph{Commutative Algebra}
   \cite{matsumura}: ``{This simple but important lemma is due to T.\ Nakayama,
@@
 
-\subsubsection{Commutative rings}
+\paragraph{Commutative rings}
 In abstract algebra, the quintessential example of a commutative ring is the
@@
 
-\subsubsection{Ideals of commutative rings}
+\paragraph{Ideals of commutative rings}
 The concept of an {ideal} of a ring can be thought of as an extension of the
@@
 
-\subsubsection{Local rings}
+\paragraph{Local rings}
 A commutative ring is \emph{local} if it has exactly one maximal ideal. 
@@
 
-\subsubsection{Modules over commutative rings}
+\paragraph{Modules over commutative rings}
 Let  $R$ be a commutative ring. 
@@
 \section{Constructing the Formal Proof}
+Not only to aid in the formalization of Nakayama's lemma, but also to
+
 Beyond formalizing the relevant structures from higher algebra, we also
@@
 
-\emily[inline]{Emily: I changed statement to \emph{if and only if} below; do we need to update formal proof?}
+\emily[inline]{Emily: Just changed statement to \emph{if and only if} below; we should check whether we should update its formal proof}
 Suppose that $I$ is an ideal of a commutative rings $R$.  
-We formally state prove the following lemma: If $I$ contains a
+We formally establish the following: If $I$ contains a
 unit $a$ if and only if $I$ is the trivial ideal, i.e., $I=R$. 
@@
     $r \cdot x$, then $1 = y \cdot (r \cdot x) = (y\cdot r) \cdot x$, showing that $x^{-1} = y \cdot r$, 
-    which contradicts the assumption that $x$ is not a unit. Hence by the lemma described earlier in this section, 
+    which contradicts the assumption that $x$ is not a unit. Hence by the statement described earlier in this section, 
     $I_1$ is proper.
 
-    If \(I_{1}\) is not a maximal ideal of $R$, then by definition there exists a strictly larger
-    proper ideal \(I_{2}\) of $R$, i.e.,
-    $x \in I_{1}\subsetneq I_{2} \subsetneq R$. Likewise, if  \(I_{2}\) is again not
-    maximal, then there exists a strictly larger proper ideal
-    $I_{3}$, which, if not maximal, is strictly contained in another ideal, $I_4$, etc.
+   Either $I_1$ is a maximal ideal of $R$, or it is strictly contained in a maximal ideal, or there exists 
+   an inifinite chain of strictly increasing
+   proper ideals of the form 
+    \begin{equation} \label{infinite-chain: e}
+    I_{1}\subsetneq I_{2}\subsetneq I_{3}\subsetneq\cdots\subsetneq I_n \subsetneq \cdots. 
+    \end{equation}  
+   Indeed, suppose that $I_1$ is not maximal, and   
+   assume that for some integer $n \geq 1$,  there exist proper, non-maximal ideals 
+   $I_k$ of $R$, $1 < k \leq n$, such that for all such $k$,  $I_{k-1}$ is strictly contained in $I_k$.  
+   Since $I_n$ is not maximal, there exists a proper ideal $I_{n+1}$ of $R$ such that $I_n \subsetneq I_{n+1}$.
+      Then either $I_{n+1}$ is maximal, or we have extended the chain by one additional link.
 
-  Continuing in this way, if  this process terminates, we have successfully identified a
-    maximal ideal of $R$ that contains $x$, and if not, one obtains an infinite, strictly increasing chain of proper ideals of $R$, each containing $x$, 
-    \[I_{1}\subsetneq I_{2}\subsetneq I_{3}\subsetneq\cdots\subsetneq I_n \subsetneq \cdots. \]
+%   
+%    If \(I_{1}\) is not a maximal ideal of $R$, then by definition there exists a strictly larger
+%    proper ideal \(I_{2}\) of $R$, i.e.,
+%    $x \in I_{1}\subsetneq I_{2} \subsetneq R$. Likewise, if  \(I_{2}\) is again not
+%    maximal, then there exists a strictly larger proper ideal
+%    $I_{3}$, which, if not maximal, is strictly contained in another ideal, $I_4$, etc.
+%
+
     It is straightforward to verify that an increasing union of ideals 
-    is, by definition, an ideal containing every ideal in the union.  Moreover, if each ideal in the union
-    contains an element $x$, then the union certainly 
-       contains \(x\) as well.
+    is, by definition, an ideal containing every ideal in the union.  
+Hence if, in this process, no maximal ideal is identified; i.e., we have ensured the existence of a chain of the form \eqref{infinite-chain: e},  then the increasing union of the $I_k$ is again an ideal, which contains $x$ since  $x \in I_1$.
 
-      Hence the set $S$ of all ideals of $R$, partially ordered by inclusion, 
-       satisfies the property that every chain in $S$ has an upper bound in $S$.
-    Therefore Zorn's lemma ensures the existence of a maximal ideal of \(R\) containing \(x\).
+%  Continuing in this way, if  this process terminates, we have successfully identified a
+%    maximal ideal of $R$ that contains $x$, and if not, one obtains an infinite, strictly increasing chain of proper ideals of $R$, each containing $x$, 
+%    \[I_{1}\subsetneq I_{2}\subsetneq I_{3}\subsetneq\cdots\subsetneq I_n \subsetneq \cdots. \]
+%    It is straightforward to verify that an increasing union of ideals 
+%    is, by definition, an ideal containing every ideal in the union.  Moreover, if each ideal in the union
+%    contains an element $x$, then the union certainly 
+%       contains \(x\) as well.
+
+      Hence the set $X$ of all proper ideals of $R$ containing $x$, partially ordered by inclusion, 
+       satisfies the property that every chain in $X$ has an upper bound in $X$.
+    Therefore, Zorn's lemma ensures the existence of a maximal element of $X$, i.e., a maximal ideal of \(R\) containing \(x\).
 \end{quote}
 
-The above argument has potentially infinitely many steps. A proof with infinitely
-many steps is a problem in Coq. To see this from the above argument, suppose we
-wrote a proof tactic \mintinline{coq}{generate_larger_ideal} that allows us to
-go from one non-maximal ideal \(I_{k}\) which contains \(x\) to another ideal
-\(I_{k+1}\) which also contains \(x\). Provided our first ideal \(I_{1}\) is
-not maximal, our first invocation of \mintinline{coq}{generate_larger_ideal}
-will produce another ideal \(I_{2}\). Our new ideal \(I_{2}\) may also not be
-maximal, requiring that we invoke \mintinline{coq}{generate_larger_ideal}
-again. This can lead to an infinite number of calls to the tactic
-\mintinline{coq}{generate_larger_ideal} which will occupy any machine's
-processor(s) forever, and further, the infinite number of ideals in the proof
-state will fill any machine's memory. After we have overwhelmed any system with
+The above argument has potentially infinitely many steps, posing a Coq implementation
+ problem. Indeed, suppose one were to write a proof tactic called \mintinline{coq}{generate_larger_ideal} 
+allowing one to move from a non-maximal, proper ideal \(I\) that contains a fixed non-unit 
+$x$ to a strictly larger ideal 
+\(J \), which is again proper, and also contains \(x\).
+
+After fixing a proper ideal $I_1$, provided that it is not maximal, 
+our first invocation of \mintinline{coq}{generate_larger_ideal}
+will produce another ideal, \(I_{2}\). It is possible that \(I_{2}\) is also non-maximal, 
+requiring that we invoke \mintinline{coq}{generate_larger_ideal}
+again, producing $I_3$, which again could be non-maximal, and so on, 
+which could lead to an infinite number of calls to the tactic
+\mintinline{coq}{generate_larger_ideal}
+Of course, this would occupy any machine's
+processor(s) forever, and further, the boundlessly increasing number of ideals in the proof
+state would fill any machine's memory.
+
+After we have overwhelmed any system with
 these infinite number of calls to a single proof tactic, we still have to
@@
 
-\subsection{The Formal Statement of Nakayama's Lemma}
-To start describing our proof, we formalize the statement of Nakayama's Lemma
-in Coq.
+\subsection{The Formal Statement}
+We now present our formal statement of Nakayama's Lemma
+in Coq, and describe a lemma called upon in our proof.
 
@@
 formally stated and proved a lemma that gives a concrete description of the
-elements of the submodule $\mathfrak{m} M$  appearing in the statement of the
-theorem. This lemma applies more generally, to any finitely generated module
+elements of the submodule $\mathfrak{m} M$  appearing in its statement. 
+This lemma applies more generally, to an arbitrary finitely generated module
 $M$ over a (not necessarily local) commutative ring, and any submodule of the
-form $I M$, for $I$ an arbitrary ideal. By definition, $IM$ consists of scalar
+form $I M$, for $I$ an arbitrary ideal.
+
+By definition, $IM$ consists of scalar
 combinations of elements of $M$ with coefficients in $I$. The lemma states that
-the elements from $M$ appearing in the expression can be chosen to be from any
+the elements from $M$ appearing in such an expression can be chosen to be from any
 fixed finite generating set for $M$. In other words, given any generating set
-$u_{1},\dots, u_{n} \in M$  of a  finitely generated $R$-module $M$, every
+$u_{1},\dots, u_{n} \in M$  for a  finitely generated $R$-module $M$, every
 element $x$ of $I M$ can be written as a scalar combination $a_1 \cdot u_1 +
@@
 
-The proof follows from a straightforward argument based on definitions, by
+This lemma's proof follows from a straightforward argument based on definitions, by
 induction on the number of elements in a fixed generating set for $M$, which we
@@
 
-Now we move forward to outline the formal proof of Nakayama's lemma. We proceed
-by induction on the number of elements in a generating set for the $R$-module
-$M$. The base case is the situation when \(M\) requires no generators, so $M$
+\subsection{The Formal Proof}
+We now outline the formal proof of Nakayama's lemma, and  proceed
+by induction on the number of elements in a fixed generating set for the finitely generated $R$-module
+$M$. The base case in this situation is when \(M\) requires no generators, so $M$
 consists solely of the empty scalar combination, i.e., the empty sum, which, by
 convention, is the zero element. In other words, $M = 0$ by assumption, and
-this is also precisely the conclusion of Nakayama's Lemma.  Hence the statement
+this is also precisely the conclusion of Nakayama's Lemma.  Hence the statement holds
 trivially, without using the hypothesis that $M = \mathfrak{m} M$.

### 2023-01-16 nakayama/paper.tex
Spelling corrections

@@
 In general, a commutative ring is a set $R$ with two binary operations, which
-we call \emph{addition} and \emph{mutiplication}, typically denoted $\cdot$ and
-$+$, respectively. As motivated by the properties of the ring of integers,
+we call \emph{addition} and \emph{multiplication}, typically denoted $\cdot$
+and $+$, respectively. As motivated by the properties of the ring of integers,
 addition, $R$ must be an abelian group, multiplication must be associative, $R$
@@
 In order to informally state Nakayama's Lemma, we first explain some of notational 
-conventions.  In this dicussion, suppose that  $I$ is an ideal of a commutative ring $R$, 
+conventions.  In this discussion, suppose that  $I$ is an ideal of a commutative ring $R$, 
 and that $M$ is an $R$-module. Then $IM$ denotes the set of all scalar combinations of 

### 2023-02-02 nakayama/paper.tex
Edited the section on the formal proof, minor edits throughout exposition on Coq, and added Conclusion

@@
 	Emily E.\ Witt\thanks{Witt acknowledges support from NSF CAREER Award
-    DMS-1945611, the Keeler Intra-University Professorship from the University of Kansas, and the 2022-23 Ruth I.\, Michler Memorial Prize from the
+    DMS-1945611, the Keeler Intra-University Professorship from the University of Kansas, and the Ruth I.\, Michler Memorial Prize from the
     Association for Women in Mathematics.} \\ {\ttfamily witt@ku.edu}
@@
 The theory, including the formalization of all algebraic structures, makes up
-approximately $100$ kB and 3300 lines of code.
+approximately $100$ kB, and 3300 lines of code.
 
@@
 \begin{figure}[t]
-  \caption{The hierarchy of our algebraic structures}
+  \caption{The hierarchy of our algebraic structures in Coq}
   \includegraphics[width=.4\textwidth]{algebraic-structures.pdf}
   \centering
+   \label{alg-heirarchy: F}
 \end{figure}
 
-\subsection{Semigroups} Our foundation begins by defining a semigroup class, which declares a binary
+\subsection{Semigroups} 
+Appearing at the top of \Cref{alg-heirarchy: F}, our
+ foundation begins by defining a semigroup class, which declares a binary
 operation to be associative. From here, we build up through monoids, which
 introduce identities, to groups, which introduce inverses. Note the double
-equals ``$==$'' appearing in these definitions is notation for an arbitrary
+equals, ``$==$'', appearing in these definitions is notation for an arbitrary
 equivalence relation over the group's carrier set, which acts as equality.
@@
 \end{minted}
-The lines such as  ``\verb|monoid_semigroup :> Semigroup equiv op;|'' simply coerce
-the monoid typeclass into a semigroup.
+The line  ``\verb|monoid_semigroup :> Semigroup equiv op;|'' simply coerces
+the monoid typeclass into a semigroup, and similar lines perform analogous functions.
 
-\subsection{Algebraic quotients}
+\subsection{Algebraic Quotients}
 While in the end, our formal proof does not call upon quotients of
@@
  quotient structures are also fundamental to commutative algebra,
-it is work pointing out that we have formalized quotients of groups, rings, and modules 
+it is worth pointing out that we have formalized quotients of groups, rings, and modules 
   using typeclasses, which appear to work rather smoothly.
@@
 
-The utility--and, as a consequence, the ubiquity--of quotients in commutative algebra 
+The utility--and, as a consequence, the ubiquity--of quotients in algebra 
 motivates our choice to use equivalence relations to define the components of a group structure. If one
@@
 simply defined as a group, but under an equivalence relation that is not the
-usual equality. Not much is lost in adopting this convention thanks to Coq's 
-rewrite tactics for setoids--types equipped with an equivalence relation---can 
-still be called
-upon.
+usual equality. Not much is lost in adopting this convention, thanks to Coq's 
+rewrite tactics for setoids, which are types equipped with an equivalence relation.
 
-\subsection{Rings and their ideals}
+\subsection{Rings and their Ideals}
 Moving onward, rings form the next step in our algebraic hierarchy; a ring has
@@
 which need not be commutative in general. In our formulation, rings must have a
-multiplicative identity. Next, we formalized the definition of a commutative
-ring, further requiring commutativity of multiplication. At this point, we
-formalized the notion of an ideal of a commutative ring, a subgroup of the ring
-under addition that satisfies the absorption property under multiplication,
-i.e., \(r a\) sits in the ideal whenever \(a\) of the ideal, regardless of the choice of 
-element \(r\) of the commutative ring. We also used this to formalize the
+multiplicative identity. Next, we formalize the definition of a commutative
+ring, further requiring commutativity of multiplication.
+
+At this point, we formalize several algebraic structures defined in terms of commutative rings.
+First is the definition of an ideal of a commutative ring, a subgroup of the ring
+under addition that satisfies the absorption property under multiplication, and with this, also the 
 notion of a quotient ring $R/I$, where $I$ is an ideal of a commutative ring
 $R$.
-
-Next, we formalized the definition of a  prime ideal, and then 
-moved on to do the same for the notion of a maximal ideal, a proper ideal 
-that is maximal with respect to inclusion. Below is the definition in Coq,
+We also formalize the definition of a  prime ideal, and that of a maximal ideal--a proper ideal that is maximal with respect to inclusion.
+ Below is the definition of latter in Coq,
 which uses \texttt{P} as the predicate for the ideal.
@@
 
-\noindent Next, we were able to employ this definition of a maximal ideal
-to formally define a local
+ Next, we employ the above definition to formally define a local
 ring, i.e., a commutative ring with a single maximal ideal.
@@
 
-\subsection{Modules over rings}
-At this point, we formalized the definition of a module over a commutative ring,
+\subsection{Modules over Rings}
+With the fundamental definitions for commutative rings and their ideals formalized, we move on 
+to build our formal module theory.  
+We start by formalizing the definition of a module over a commutative ring,
 the commutative-algebraic generalization of the notion of a vector space over a
@@
 length-parameterized lists; since we don't use the simpler kind of lists, there
-are no name collisions. In our code, \texttt{M} is the type of module elements,
-\texttt{R} is the type of ring elements, act as coefficients, and
+are no name collisions. In the code excerpted below, \texttt{M} is the type of module elements,
+\texttt{R} is the type of ring elements, acting as coefficients, and
 \texttt{t A n} is a list whose elements are of type \texttt{A} and whose length
@@
 
-Finally, we defined the submodule $IM$ of a module $M$ over a commutative ring $R$, 
+Finally, we define the submodule $IM$ of a module $M$ over a commutative ring $R$, 
 where $I$ is an arbitrary ideal of $R$.
@@
 
-\section{Constructing the Formal Proof}
-Not only to aid in the formalization of Nakayama's lemma, but also to
-
-Beyond formalizing the relevant structures from higher algebra, we also
-formally establish some basic theory from the field in Coq. For instance, 
+\section{Constructing the Formal Proof} \label{formal-proof: S}
+Not only to aid in the formal proof of Nakayama's lemma, but also to add to the body 
+of formalized theory in commutative algebra, along with our formal definitions of algebraic structures,
+we also  
+ establish some basic theory of these objects in Coq.
+ For instance, 
 consider the notion of a \emph{unit} of a
@@
 
-\emily[inline]{Emily: Just changed statement to \emph{if and only if} below; we should check whether we should update its formal proof}
-Suppose that $I$ is an ideal of a commutative rings $R$.  
-We formally establish the following: If $I$ contains a
-unit $a$ if and only if $I$ is the trivial ideal, i.e., $I=R$. 
+Suppose that $I$ is an ideal of a commutative ring $R$.   Then if $I$ is the trivial ideal, i.e., $I = R$, then it, of course, contains a unit, namely $1$. 
+We formally establish the converse of this statement: If $I$ contains a
+unit $a$, then $I=R$. 
 The informal proof logic is as follows:  Due to the absorption property of $I$,  
@@
 
+We also use classical logic to prove that \(1 - x\) is a unit whenever \(x\)
+is an element of a local ring that is not a unit. The proof is completed by way
+of contradiction, and uses the rule that \(\neg\neg P\rightarrow P\).
+
 \subsection{Dealing with the Axiom of Choice}
+
+\emily[inline]{Emily says:  There was an issue with our argument below, so I have updated it, and need to point to 
+quotients to deal with the fact that we want a maximal ideal \emph{that contains a fixed element}.
+}
+
 Every non-unit element of a commutative ring is contained in some maximal
 ideal, a fact that relies on the Axiom of Choice. 
-The following standard informal
-proof calls upon Zorn's lemma, which is equivalent to the Axiom of Choice, and which 
+This fact can be derived from from the weaker statement that every commutative ring contains a maximal ideal:
+Indeed, assume this, and fix a non-unit $x$ of a commutative ring $R$.  Then the quotient $R/\langle x \rangle$ of $R$ modulo 
+the principal ideal generated by $x$ is a commutative ring, and so contains a maximal ideal, which corresponds precisely to a 
+maximal ideal of $R$ containing $x$ by   
+the lattice isomorphism theorem for rings.
+
+The following standard informal proof of the fact that every commutative rings contains a maximal ideal calls upon Zorn's lemma, 
+which is equivalent to the Axiom of Choice (assuming Zermelo-Fraenkel Set Theory), and which 
 says that if every chain of elements from a partially ordered set  has an upper
@@
 \begin{quote}
-	Fix a non-unit $x$ in a commutative ring $R$, and  \(I_{1}\) to be the principal 
-	ideal generated by $x$, i.e., the smallest ideal containing the element $x$,
-    which consists of all $R$-multiples of it.  No element of $I_1$ is a unit, since if  
-    $y \in R$ were the multiplicative inverse of some $R$-multiple
-    $r \cdot x$, then $1 = y \cdot (r \cdot x) = (y\cdot r) \cdot x$, showing that $x^{-1} = y \cdot r$, 
-    which contradicts the assumption that $x$ is not a unit. Hence by the statement described earlier in this section, 
-    $I_1$ is proper.
+Fix a commutative ring $R$.  Since $1 \neq 0$ in $R$, the zero ideal is proper.  
+If the zero ideal is maximal, then we have identified a maximal ideal of $R$. 
+If not, then there must exist a proper ideal 
+$I_1$ of $R$ containing more than just the element $0$.
 
-   Either $I_1$ is a maximal ideal of $R$, or it is strictly contained in a maximal ideal, or there exists 
-   an inifinite chain of strictly increasing
-   proper ideals of the form 
+If $I_1$ is maximal, then we have found a maximal ideal, but if not, then there exists a proper ideal 
+$I_2$ of $R$ that strictly contains $I_1$.  
+Likewise, if $I_2$ is maximal, we are done, and if not, there exists a proper ideal $I_3$ such that $I_3 \supsetneq I_2$.
+Continuing this pattern, we either identify a maximal ideal of $R$, or we construct an infinite chain of proper ideals of $R$:
     \begin{equation} \label{infinite-chain: e}
@@
     \end{equation}
-   Indeed, suppose that $I_1$ is not maximal, and   
-   assume that for some integer $n \geq 1$,  there exist proper, non-maximal ideals 
-   $I_k$ of $R$, $1 < k \leq n$, such that for all such $k$,  $I_{k-1}$ is strictly contained in $I_k$.  
+
+       More precisely, assume by induction that  there exist proper, non-maximal ideals 
+   $I_k$ of $R$, $1 < k \leq n$, such that each $I_{k-1}$ is strictly contained in $I_k$.  
    Since $I_n$ is not maximal, there exists a proper ideal $I_{n+1}$ of $R$ such that $I_n \subsetneq I_{n+1}$.
@@
 
-%   
-%    If \(I_{1}\) is not a maximal ideal of $R$, then by definition there exists a strictly larger
-%    proper ideal \(I_{2}\) of $R$, i.e.,
-%    $x \in I_{1}\subsetneq I_{2} \subsetneq R$. Likewise, if  \(I_{2}\) is again not
-%    maximal, then there exists a strictly larger proper ideal
-%    $I_{3}$, which, if not maximal, is strictly contained in another ideal, $I_4$, etc.
-%
+It is straightforward to verify, by definition, 
+         that an increasing union of ideals 
+    is again an ideal.
+Hence if, in this process, no maximal ideal is identified, i.e., we have ensured the existence of a chain of the form \eqref{infinite-chain: e},  then the increasing union of the $I_k$ is again an ideal.
 
-    It is straightforward to verify that an increasing union of ideals 
-    is, by definition, an ideal containing every ideal in the union.  
-Hence if, in this process, no maximal ideal is identified; i.e., we have ensured the existence of a chain of the form \eqref{infinite-chain: e},  then the increasing union of the $I_k$ is again an ideal, which contains $x$ since  $x \in I_1$.
-
-%  Continuing in this way, if  this process terminates, we have successfully identified a
-%    maximal ideal of $R$ that contains $x$, and if not, one obtains an infinite, strictly increasing chain of proper ideals of $R$, each containing $x$, 
-%    \[I_{1}\subsetneq I_{2}\subsetneq I_{3}\subsetneq\cdots\subsetneq I_n \subsetneq \cdots. \]
-%    It is straightforward to verify that an increasing union of ideals 
-%    is, by definition, an ideal containing every ideal in the union.  Moreover, if each ideal in the union
-%    contains an element $x$, then the union certainly 
-%       contains \(x\) as well.
-
-      Hence the set $X$ of all proper ideals of $R$ containing $x$, partially ordered by inclusion, 
-       satisfies the property that every chain in $X$ has an upper bound in $X$.
-    Therefore, Zorn's lemma ensures the existence of a maximal element of $X$, i.e., a maximal ideal of \(R\) containing \(x\).
+Let $X$ denote the set of all proper ideals of $R$, partially ordered by inclusion.
+We have shown that every chain in $X$ has an upper bound in $X$, so  Zorn's lemma ensures the existence of a maximal element of $X$, i.e., a maximal ideal of \(R\). 
 \end{quote}
 
-The above argument has potentially infinitely many steps, posing a Coq implementation
- problem. Indeed, suppose one were to write a proof tactic called \mintinline{coq}{generate_larger_ideal} 
-allowing one to move from a non-maximal, proper ideal \(I\) that contains a fixed non-unit 
+This argument potentially requires infinitely many steps, posing an implementation
+ problem. Indeed, suppose one were to write a Coq proof tactic called \mintinline{coq}{generate_larger_ideal}
+ that allows one to move from a non-maximal, proper ideal \(I\) that contains a fixed non-unit 
 $x$ to a strictly larger ideal 
@@
 
-After we have overwhelmed any system with
-these infinite number of calls to a single proof tactic, we still have to
+Even if it were possible not to overwhelm a system with
+these infinitely many calls to a single proof tactic, one would still have to
 invoke more tactics to finish the proof with an application of Zorn's lemma,
@@
 \end{minted}
-We chose to avoid this infinite proof script issue by including an axiom that
+
+We choose to avoid this infinite proof script issue by including an axiom that
 any non-unit \(x\) of a ring must be contained in some maximal ideal.
@@
 
-We also used classical logic to prove that \(1 - x\) is a unit whenever \(x\)
-is an element of a local ring that is not a unit. The proof is completed by way
-of contradiction, and uses the rule that \(\neg\neg P\rightarrow P\).
-
-\subsection{The Formal Statement}
+\subsection{The Formal Statement} \label{formal-statement: SS}
 We now present our formal statement of Nakayama's Lemma
@@
 
-To use as a building block in the formal proof of Nakayama's Lemma, we first
-formally stated and proved a lemma that gives a concrete description of the
+To use as a building block in the formal proof of Nakayama's Lemma, we 
+formally state and prove a lemma that gives a concrete description of the
 elements of the submodule $\mathfrak{m} M$  appearing in its statement. 
@@
 \end{align*}
-By absorption in ideals, each  $c_{ij}  \cdot r_i$ is in $I$, and since ideals
+By the absorption property of ideals, each  $c_{ij}  \cdot r_i$ is in $I$, and since ideals
 are closed under addition, we inductively conclude that the coefficient $a_j
@@
 \subsection{The Formal Proof}
-We now outline the formal proof of Nakayama's lemma, and  proceed
-by induction on the number of elements in a fixed generating set for the finitely generated $R$-module
+We now outline our formal proof of Nakayama's lemma, and  proceed
+by way of induction on the number of elements in a fixed generating set for the finitely generated $R$-module
 $M$. The base case in this situation is when \(M\) requires no generators, so $M$
@@
 assumption, \(M = \mathfrak{m} M\), and in particular, the generator $u_1$ is
-an element of the submodule $\mathfrak{m} M$. The lemma described above
+an element of the submodule $\mathfrak{m} M$. The lemma described in \Cref{formal-statement: SS}
 guarantees the existence of ring elements $a_1, \ldots, a_n \in \mathfrak{m}$
@@
 \[u_{1} = a_{1} \cdot u_{1} + a_2 \cdot u_2 + \cdots + a_{n+1} \cdot u_{n+1}.\]
-
-Collecting the \(u_{1}\) terms on the left-hand side of the equation, applying
+Collecting the \(u_{1}\) terms on the left-hand side of the equation, calling on 
 the existence of additive inverses in $R$, and distributivity of scalar
@@
 \end{equation}
-In Coq, we worked backwards to establish this fact. The comments following
-each tactic offers a brief explanation of the effects on the goal.
+
+In Coq, we work backward to establish \eqref{equation1: e}. The comment following
+each tactic appearing in the code below offers a brief indication of its effects on the goal.
 \begin{minted}[linenos,firstnumber=157,stepnumber=5]{coq}
@@
 $\mathfrak{m}$, it is not a unit. Hence, by the formalized statement mentioned
-earlier, $1 - a_{1}$ is a unit of $R$. Let $b_{1} \in R$ denote its 
+early in \Cref{formal-proof: S}, $1 - a_{1}$ is a unit of $R$. Let $b_{1} \in R$ denote its 
 multiplicative inverse, so that $b_1 \cdot  (1 - a_{1}) = 1$. Multiplying this
 element on the either side of \eqref{equation1: e}, we deduce the following.  
-\begin{align*}
+\begin{align}
+\label{simplify-line-1}
 b_1 \cdot \left((1 - a_{1}) \cdot u_{1} \right)
   & = b_1 \cdot (a_{2} \cdot u_{2} + \cdots + a_{n+1} \cdot u_{n+1}) \\ 
+\label{simplify-line-2}
 \left( b_1 \cdot (1 - a_{1})\right) \cdot u_{1}
   & = b_1 \cdot (a_{2} \cdot u_{2}) + \cdots + b_1 \cdot (a_{n+1} \cdot u_{n+1}) \\ 
+   \label{simplify-line-3}
 u_1 = 1 \cdot u_{1}
   & = (b_1 \cdot  a_{2}) \cdot u_{2} + \cdots + (b_1  \cdot  a_{n+1}) \cdot u_{n+1} 
-\end{align*}
+\end{align}
 \begin{minted}[linenos,firstnumber=181,stepnumber=5]{coq}
@@
 \end{minted}
-This bit of proof code has the effect of naming \(b_{1}\) as the inverse of the
-unit \(1 - a_{1}\) and storing in the hypothesis \texttt{Hb1} the equation
-\(b_{1} (1 - a_{1}) = 1\). The remainder of the code goes on to multiply on the
-left by \(b_{1}\) in the equation \texttt{H} in order to say that
-\(b_{1} ((1 - a_{1}) u1) = b_{1} (a_{2} u_{2} + \cdots + a_{n+1} u_{n+1})\).
-Going on to use the rules of module actions and hypothesis \texttt{Hb1}, we can
-simplify the left hand side of \texttt{H} to be just \(u_{1}\).
+
+This block of code has the effect of naming \(b_{1}\) as the inverse of the
+unit \(1 - a_{1}\), and storing in the hypothesis \texttt{Hb1} the equation
+\(b_{1} \cdot (1 - a_{1}) = 1\). The remainder of the code goes on to multiply on the
+left by \(b_{1}\) in the equation \texttt{H} in order to establish  \eqref{simplify-line-1}.
+Going on and applying the axioms of a module over a commutative ring, along with hypothesis \texttt{Hb1}, we can
+simplify the left hand side of \texttt{H} to be just \(u_{1}\), as in \eqref{simplify-line-3}.
 \begin{minted}[linenos,firstnumber=last,stepnumber=5]{coq}
@@
 generated by $n$ elements, and $M=0$ by the inductive hypothesis. 
-
-Showing that the inductive hypothesis holds in Coq is more work than in this
-informal proof, but this extra work is just a lot of bookkeeping.
+Though showing that the inductive hypothesis holds is more technical in Coq than in this
+informal proof, the extra steps are essentially bookkeeping.
 
 \section{Conclusion}
-TODO
+Our work here is evidence that Coq is amendable to the 
+formalization of abstract algebraic notions from commutative algebra, which are often non-discrete, and their theory. 
+There are several natural directions in which to move from here, a first  step being to further develop the formal theory of quotient rings, and to formalize the isomorphism theorems for rings.
+
+Our current body of work can be extended to include further essential concepts from commutative algebra, e.g., 
+ module homomorphisms; direct sums and free modules; tensor products of modules and exact sequences; projective, injective, and flat modules; direct and inverse limits of modules; and/or graded rings and modules.
+In this process, building formal proofs of other fundamental theorems involving these notions will likely be valuable in  
+effectively designing their formal definitions, as we noticed in building our algebraic heirarchy for Nakayama's Lemma.
+
+Finally, integrating within the formalized commutative algebra theory some of the computational algebra that has been formally developed, such as that regarding Gr\"obner bases \cite{buchberger,persson2001integrated}, could also be a fruitful direction to pursue.
 

### 2023-02-24 nakayama/images/algebraic-structures.tex
Converted to use Springer Nature document class

@@
        minimum height = .4cm,
- %      fill = gray!30
- %      fill = cyan!40
- %      fill = blue!50!white!80
     },
@@
     }
-%    bad/.style = {
-%       shape=rectangle, %rounded corners,
-%       align=center,
-%       minimum width = .4cm,
-%       minimum height = .4cm,
-%       fill = red!70
-%    }
 }

### 2023-02-24 nakayama/paper.tex
Converted to use Springer Nature document class

@@
 \RequirePackage[l2tabu,orthodox]{nag}
-\documentclass{article}
-\usepackage{amsthm}
-\usepackage{amssymb}
-\usepackage{mathtools}
+\RequirePackage{tikz}
+\documentclass[referee,sn-mathphys]{sn-jnl}
+% \usepackage{amsthm}
+% \usepackage{amssymb}
+% \usepackage{mathtools}
 \usepackage{minted}
+% \usepackage{amsmath}
+% \usepackage{amsfonts}
+% \usepackage{color}
+% \usepackage{mathrsfs}
+% \usepackage[mathcal]{euscript}
+% \usepackage{enumitem}
+% \usepackage{float}
+% \usepackage[center]{caption}
+% \usepackage{graphicx}
+\usepackage{cleveref}
 
-\input{preamble.tex}
+\jyear{2021}
+
+% TikZ libraries and settings
+\usetikzlibrary{positioning}
+\tikzset{
+  node/.style = {
+    shape=rectangle, %rounded corners,
+    align=center,
+    minimum width = .4cm,
+    minimum height = .4cm,
+  },
+  Snode/.style = {
+    shape=rectangle, %rounded corners,
+    align=center,
+    minimum width = .4cm,
+    minimum height = .4cm,
+    fill = green!60!blue!70
+  }
+}
+
+% Clever references
+\crefname{equation}{Eq.}{Eqs.}
+\crefname{theorem}{Theorem}{Theorems}
+\crefname{lemma}{Lemma}{Lemmata}
+\crefname{corollary}{Corollary}{Corollaries}
+\crefname{proposition}{Proposition}{Propositions}
+\crefname{definition}{Definition}{Definitions}
+\crefname{rem}{Remark}{Remarks}
+\crefname{example}{Example}{Examples}
+\crefname{conventions}{Conventions}{Conventions}
+\crefname{setup}{Setup}{Setup}
+\crefname{question}{Question}{Question}
+\crefname{figure}{Figure}{Figures}
+
+%THEOREM ENVIRONMENTS
+\newtheorem{theorem}{Theorem}[section]
+\newtheorem{lemma}[theorem]{Lemma}
+\newtheorem{corollary}[theorem]{Corollary}
+\newtheorem{proposition}[theorem]{Proposition}
+
+\newtheorem*{nak*}{Nakayama's Lemma}
+
+%DEFINITION STYLE ENVIRONMENTS
+\theoremstyle{definition}
+\newtheorem{definition}[theorem]{Definition}
+\newtheorem{definition-theorem}[theorem]{Definition/Theorem}
+\newtheorem{setup}[theorem]{Setup}
+\newtheorem{notation}[theorem]{Notation}
+\newtheorem{conventions}[theorem]{Conventions}
+\newtheorem{example}[theorem]{Example}
+
+%REMARK STYLE ENVIRONMENTS 
+\theoremstyle{remark}
+\newtheorem{remark}[theorem]{Remark}
+\newtheorem{convention}{Convention}
+
+\numberwithin{equation}{section}
+\numberwithin{figure}{subsection}
+
+%%%%%%%%
+% \mathchardef\ordinarycolon\mathcode`\:
+% \mathcode`\:=\string"8000
+% \begingroup \catcode`\:=\active
+%   \gdef:{\mathrel{\mathop\ordinarycolon}}
+% \endgroup
 
 \begin{document}
-\title{ 
+\title[Formalizing Commutative Algebra in Coq]{ 
 Formalizing Commutative Algebra in Coq: \\
@@
 
-\date{}
+\author[1]{\fnm{Andrew} \sur{Cousino}}\email{acousino@ku.edu}
+\author[1]{\fnm{Emily E.\ Witt}}\email{witt@ku.edu}
+\author[1]{\fnm{Perry} \sur{Alexander}}\email{palexand@ku.edu}
+\affil[1]{\orgdiv{Institute for Information Sciences},
+  \orgname{University of Kansas},
+  \orgaddress{\city{Lawrence}, \postcode{66045}, \state{Kansas},
+    \country{United States of America}}}
 
-\author{ 
-	Andrew Cousino \\ {\ttfamily acousino@ku.edu}
-	\and 
-	Emily E.\ Witt\thanks{Witt acknowledges support from NSF CAREER Award
-    DMS-1945611, the Keeler Intra-University Professorship from the University of Kansas, and the Ruth I.\, Michler Memorial Prize from the
-    Association for Women in Mathematics.} \\ {\ttfamily witt@ku.edu}
-  \and 
-	Perry Alexander \\ {\ttfamily palexand@ku.edu}
-}
-
-\maketitle
-
-\vspace{-1cm}
-
-{\large
-\begin{center}
-	Institute for Information Sciences \\
-	The University of Kansas \\
-	Lawrence, KS 66045
-\end{center}
-}
-
-\todo[inline]{To do:  Add to/alter author list, funding acknowledgments, title,
-  and/or abstract as needed}
-
-\begin{abstract}
+\abstract{
   We describe our formal proof of Nakayama's Lemma, a fundamental theorem in
@@
   explain our process of formalizing these structures.
-\end{abstract}
+}
 
-\noindent \textbf{Keywords:}
-formalization of mathematics,
-formal proof,
-commutative algebra,
-commutative ring,
-local ring,
-ideal,
-module over a ring,
-finitely generated module.
+\keywords{formalization of mathematics, formal proof, commutative algebra,
+  commutative ring, local ring, ideal, module over a ring,
+  finitely generated module}
+
+\maketitle
 
@@
 (e.g., see  \cite{grobner-bases-cryptography}). A implementation of
-Buchberger's algorithm \cite{buchberger} for determining Gr\"obner bases of
+Buchberger's algorithm \cite{buchberger} for determining Gr\"{o}bner bases of
 ideals in polynomial rings has been proved correct within the proof assistant
@@
 \cite{mathcomp}, we start from scratch.
-\todo{To do: Verify whether MathComp only formalized finite algebraic
-  structures. Drew is about as certain as he can be that this is the case.}
 The theory, including the formalization of all algebraic structures, makes up
@@
   \caption{The hierarchy of our algebraic structures in Coq}
-  \includegraphics[width=.4\textwidth]{algebraic-structures.pdf}
+  \resizebox{0.5\textwidth}{0.4\textwidth}{
+    \begin{tikzpicture}[->,>=stealth,shorten >=1pt,auto,node distance=1cm,semithick]
+      \node[Snode] (Semigroup) {Semigroup};
+      \node[Snode] (Monoid) [below = of Semigroup]{Monoid};
+      \node[Snode] (Group) [below =of Monoid] {Group};
+      \node[Snode] (AbelianGroup) [below =of Group] {AbelianGroup};
+      \node[Snode] (Subgroup) [left =1.3cm of AbelianGroup] {Subgroup};
+
+      \node[Snode] (Ring) [below = of AbelianGroup] {Ring};
+      \node[Snode] (CommutativeRing) [below =of Ring] {CommRing};
+      \node[Snode] (Module) [right = 1.3cm of CommutativeRing] {Module};
+      \node[Snode] (Submodule) [left = 1.0 of CommutativeRing] {Submodule};
+      \node[Snode] (Ideal) [left =1.0 of Submodule] {Ideal};
+      \path (Semigroup) edge (Monoid)
+        (Monoid) edge (Group)
+        (Group) edge (AbelianGroup)
+        (Group) edge (Subgroup)
+        (Subgroup) edge (Ideal)
+        (AbelianGroup) edge (Ring)
+        (AbelianGroup) edge (Module)
+        (Ring) edge (CommutativeRing)
+        (Subgroup) edge (Submodule);
+    \end{tikzpicture}
+  }
   \centering
@@
 
-%\emily[inline]{Emily:  Unfortunately, I think we need to update naming
-%  conventions since in mathematics, ``vector'' is reserved for an element of a
-%  vector space over a field, rather than an element of an arbitrary module.  So
-%  this could cause confusion.  Similar with ``basis,'' which is especially
-%  tricking since two different generating sets of a finitely generated module
-%  can have different sizes, but all bases of a vector space have the same
-%  cardinality, and an element of a module can typically be written as a scalar
-%  combination in multiple ways, while bases are linearly independent.  I've
-%  proposed a rewrite of the blue subsubsection right above it.  Drew, can you
-%  double check it for accuracy with respect to the code? 
-%}
-%\emily[inline]{We'll also need to update the code.  I think {\ttfamily vectors}
-%  should be something like {\ttfamily scalar-combinations}, and
-%  {\ttfamily basis} something like {\ttfamily generating-set}. 
-%}
-
 \subsection{Modules over Rings}
@@
 \begin{minted}{coq}
-  Definition finitely_generated {n: nat}(generatingSet: t M n) :=
+  Definition finitely_generated {n: nat}(genSet: t M n) :=
     forall (elt: M),
       exists (coeffs: t R n),
-        elt =M= linear_combin coeffs generatingSet.
+        elt =M= linear_combin coeffs genSet.
 \end{minted}
@@
 \subsection{Dealing with the Axiom of Choice}
-
-\emily[inline]{Emily says:  There was an issue with our argument below, so I have updated it, and need to point to 
-quotients to deal with the fact that we want a maximal ideal \emph{that contains a fixed element}.
-}
 
@@
 \begin{minted}{coq}
-  repeat generate_larger_ideal. (* must be called infinitely often *)
-  zorns_lemma. (* called after the above non-terminating call finishes *)
+  (* must be called infinitely often *)
+  repeat generate_larger_ideal.
+  (* called after the above non-terminating call finishes *)
+  zorns_lemma.
 \end{minted}
@@
     ~ is_unit equiv mul one x ->
-    exists (P: Carrier -> Prop)(P_proper: Proper (equiv ==> iff) P)
+    exists (P: Carrier -> Prop)
+      (P_proper: Proper (equiv ==> iff) P)
     	(P_ideal: Ideal add zero minus mul P),
@@
 Context {P_ideal: Ideal Radd Rzero Rminus Rmul P}.
-Context {P_maxideal: maximal_ideal Requiv Radd Rzero Rminus Rmul P}.
+Context {P_maxideal: maximal_ideal Requiv Radd ... Rmul P}.
 Context {R_local: local_ring Requiv Radd Rzero Rminus Rmul}.
@@
 Lemma module_fin_gen_ideal_module:
-  forall {n: nat}(generatingSet: t M n),
-    finitely_generated Mequiv Madd Mzero action generatingSet ->
+  forall {n: nat}(genSet: t M n),
+    finitely_generated Mequiv Madd Mzero action genSet ->
     forall {m: nat}(coeffs: t R m)(elts: t M m),
@@
         linear_combin Madd Mzero action coeffs elts =M=
-          linear_combin Madd Mzero action coeffs' generatingSet /\
+          linear_combin Madd Mzero action coeffs' genSet /\
         Forall P coeffs'.
@@
 \begin{align*}
-  x = \sum_{i=1}^{k} r_i \cdot w_i
-    = \sum_{i=1}^{k} r_i \cdot \left(\sum_{j=1}^n c_{ij} \cdot  u_j\right)
-    = \sum_{j=1}^{n}\sum_{i=1}^{k} r_i \cdot (c_{ij} \cdot u_j) 
+  x & = \sum_{i=1}^{k} r_i \cdot w_i
+    = \sum_{i=1}^{k} r_i \cdot \left(\sum_{j=1}^n c_{ij} \cdot  u_j\right) \\
+    & = \sum_{j=1}^{n}\sum_{i=1}^{k} r_i \cdot (c_{ij} \cdot u_j) 
     = \sum_{j=1}^{n}\left(\sum_{i=1}^{k} c_{ij} \cdot r_i\right) \cdot u_j.   
@@
 \begin{minted}[linenos,firstnumber=157,stepnumber=5]{coq}
-  assert ((Rone [+] Rminus a1) <.> u1 =M= (* (1 - a1) u1 = ... *)
+  (* (1 - a1) u1 = ... *)
+  assert ((Rone [+] Rminus a1) <.> u1 =M=
     linear_combin Madd Mzero action coeffs' generatingSet').
-  { setoid_rewrite (module_distrib_Radd Radd Rmul Rone
-      Mequiv Madd Mzero Mminus action). (* 1 u1 + (-a1) u1 = ... *)
+  { (* 1 u1 + (-a1) u1 = ... *)
+    setoid_rewrite (module_distrib_Radd Radd Rmul Rone
+      Mequiv Madd Mzero Mminus action).
+    (* u1 + (-a1) u1 = ... *)
     setoid_rewrite (module_Rone Radd Rmul Rone
-      Mequiv Madd Mzero Mminus action). (* u1 + (-a1) u1 = ... *)
-    setoid_rewrite (module_minus_l Requiv Radd Rzero Rminus Rmul Rone
-      Mequiv Madd Mzero Mminus action). (* u1 - a1 u1 = ... *)
+      Mequiv Madd Mzero Mminus action).
+    (* u1 - a1 u1 = ... *)
+    setoid_rewrite (module_minus_l Requiv Radd ... Rone
+      Mequiv Madd Mzero Mminus action).
     symmetry. (* ... = u1 - a1 u1 *)
-    apply (group_move_r Mequiv Madd Mzero Mminus). (* ... + a1 u1 = u1 *)
-    symmetry. (* u1 = ... + a1 u1 *)
+    (* ... + a1 u1 = u1 *)
+    apply (group_move_r Mequiv Madd Mzero Mminus).
+    (* u1 = ... + a1 u1 *)
+    symmetry.
     assumption. }
@@
   pose proof
-    (local_comm_ring_sub_1_nonunit Requiv Radd Rzero Rminus Rmul Rone
+    (local_comm_ring_sub_1_nonunit Requiv Radd ... Rone
       R_local x1 Hx1_nonunit) as H1ma1_unit.
-  (* Getting to u1 = (b1 coeffs') . generatingSet *)
-  inversion_clear H1ma1_unit as [b1 Hb1]. (* 1 - a1 is a unit *)
-  setoid_rewrite (commutative Requiv Rmul) in Hb1. (* b1 (1 - a1) = 1 *)
+  (* Getting to u1 = (b1 coeffs') . genSet *)
+  (* 1 - a1 is a unit *)
+  inversion_clear H1ma1_unit as [b1 Hb1].
+  (* b1 (1 - a1) = 1 *)
+  setoid_rewrite (commutative Requiv Rmul) in Hb1.
 \end{minted}
@@
   apply (module_op_l Requiv Mequiv action) with (r:=b1) in H.
+  (* H: (b1 (1 - a1)) u1 = ... *)
   setoid_rewrite <- (module_distrib_Rmul Radd Rmul Rone
-    Mequiv Madd Mzero Mminus action) in H. (* H: (b1 (1 - a1)) u1 = ... *)
-  setoid_rewrite Hb1 in H. (* H: (1) u1 = ... *)
+    Mequiv Madd Mzero Mminus action) in H.
+  (* H: (1) u1 = ... *)
+  setoid_rewrite Hb1 in H.
+  (* H: u1 = ... *)
   setoid_rewrite (module_Rone Radd Rmul Rone
-    Mequiv Madd Mzero Mminus action) in H. (* H: u1 = ... *)
+    Mequiv Madd Mzero Mminus action) in H.
 \end{minted}
@@
 
-\bibliographystyle{plain}
+\backmatter
+\bmhead{Acknowledgments}
+This work is funded in part by the NSA Science of Security initiative contract
+\#H98230-18-D-0009 and Defense Advanced Research Project Agency contract
+\#HR0011-18-9-0001 and Honeywell FMT Purchase Order \#N000422909. The views and
+conclusions contained in this document are those of the authors and should not
+be interpreted as representing the official policies, either expressed or
+implied, of the United States Government.
+
+Witt acknowledges support from NSF CAREER Award DMS-1945611, the Keeler
+Intra-University Professorship from the University of Kansas, and the Ruth I.\,
+Michler Memorial Prize from the Association for Women in Mathematics.
 \bibliography{references}

### 2023-02-25 nakayama/paper.tex
Moved GitHub link to abstract

@@
 Formalizing Commutative Algebra in Coq: \\
-Nakayama's Lemma\thanks{Source code for this work is available on the following
-site: \url{https://github.com/ku-sldg/algebra}}
+Nakayama's Lemma
 }
@@
   commutative rings, ideals of these rings, and modules over them, and we also
-  explain our process of formalizing these structures.
+  explain our process of formalizing these structures. Source code for this
+  work is available on the following site:
+  \url{https://github.com/ku-sldg/algebra}.
 }
